### 2013-07-19 abstract.tex
Initial commit.

% This is abstract.tex

The abstract should be a brief summary of your results that grabs the
reader's attention.  It is the first thing the reader will see, and you
must convince the reader that the rest of your paper is worthwhile.  In
the best of all possible worlds, \LaTeX\ will take care of all the
formatting for you.  Let $v = (v_0, v_1, \ldots, v_n)$.  If your
abstract contains nothing but words, no one would know that you're using
\LaTeX!

### 2013-07-19 appa.tex
Initial commit.

% This is appa.tex
%
% This file is for appendices.  If you don't have any appendices, delete
% the percent sign from the beginning of the next line.
%\endinput

\appendix

% Add additional appendices by replicating the line below.

\section{Title of Appendix}

Appendices may appear after the paper proper.  Appendices may hold
extra information that would interrupt the flow of the paper and that
is not absolutely necessary for the reader to appreciate the work.
For example, a large number of related figures or a mathematical
derivation could go nicely in an appendix.

### 2013-07-19 paper.tex
Initial commit.

% This is paper.tex

\section{Introduction}
We study a class of maps between Bott-Samelson bimodules.  These maps are represented by certain types of diagrams, as described in section \ref{sec:prelim_map}.  The maps are composed by juxtaposition.

Given a sequence of consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libednisky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.  Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.  We describe the relationship between the final result of such a composition and the two binary strings being composed.

Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:prelim_probstate}.  
% TODO change this
We then do a bunch of nonsense.

\section{Preliminaries}
\label{sec:prelim}
% \subsection{Coxeter Rings, and the Bott-Samelson Bimodules}
Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be unit vectors normal to these planes.  We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.  If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a. \]  In particular, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.  Furthermore, we see that there exist fixed constants $x$ and $y$ such that
\begin{align*}
	s(\alpha_t) &= \alpha_t + x \alpha_s \\
	t(\alpha_s) &= \alpha_s + y \alpha_t
\end{align*}
Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.

Let $R^s$ be the subring of $R$ which is invariant under $s$.  Define $R^t$ similarly.  Then a \emph{Bott-Samelson bimodule} is a bimodule of the form
\[ R \otimes_{R^{i_1}} R \otimes_{R^{i_2}} R \otimes_{R^{i_3}} \dots \otimes_{R^{i_n}} R \]
where each $R^i$ is either $R^s$ or $R^t$.   Elements of such a bimodule will be written in the form $f_0 \mid f_1 \mid \dots \mid f_n$, where $f_i \in R$.

We will consider maps between these bimodules that preserve left and right actions; that is, we consider the maps $\sigma$ such that
\begin{equation}
	\sigma(rx) = r\sigma(x) \quad\text{and}\quad \sigma(xr) = \sigma(x)r \quad\text{for every $r \in R$ and $x \in \text{Dom } \sigma$}.
	\label{eq:respect}
\end{equation}
These maps can be represented using diagrammatics, as below.

\subsection{Diagrammatics of Maps}
\label{sec:prelim_map}
\newcommand{\DD}{\mathcal D}
Certain maps between Bott-Samleson bimodules can be described in terms of diagrams.  We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.  A reader who is not interested in this context can simply accept on faith the relations specified in section \ref{sec:prelim_genrel}.

Consider a category $\DD$ whose elements are linear combinations $\sum c_i \square$ of the diagrams described below.  The coefficients $c_i$ belong to the ring $\ZZ[x,y]$.

The diagrams may be described as planar graphs, not necessarily connected, drawn in a rectangle, with the following properties.
\begin{enumerate}[(i)]
	\ii Vertices may lie on the upper or lower boundary, but not on the left or right boundary.
	\ii Each vertex has degree $1$ or $3$.
	\ii Each connected component is colored either blue or red.
\end{enumerate}
The vertices on the boundary are by convention not explicitly shown, but are nonetheless labelled $s$ or $t$ for blue or red, respectively.

\begin{figure}[ht]
	\centering
	\begin{asy}
	size(6cm);
	real xmax=7;
	real ymax=5;
	draw( (xmax,ymax)--(xmax,-ymax)--(-xmax,-ymax)--(-xmax,ymax)--cycle );
	pair apex = (0,2);
	path arc = (5,-5)..(2,0)..apex..(-2,0)..(-5,-5);
	draw(arc, blue);
	dot(apex, blue);
	draw(apex--(0,ymax), blue);
	draw(-apex--(0,-ymax), red + dashed + 0.6);
	dot(-apex, red);
	label("$s$", (0,ymax), dir(90));
	label("$t$", (0,-ymax), dir(270));
	label("$s$", (-5,-ymax), dir(270));
	label("$s$", (5,-ymax), dir(270));
	\end{asy}
	\caption{An example of a possible diagram.}
	\label{fig:example_diagram}
\end{figure}

The elements of $\DD$ by simply adding corresponding coefficients.  Multiplication is defined as follows: the product of two diagrams is the composition of the diagrams if the labels coincide, and is $0$ otherwise.

In \cite{basispf}, Khovanova and Elias show that all such maps can be expressed as a linear combination of these diagrams.

\subsection{Algebraic Context}
The maps are conventionally read from bottom to top.  The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take.  For example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.  An unlabelled domain corresponds to $R$.

Let us hasten to introduce one final definition.
\begin{definition*}
	The \emph{Demazure operator} $\partial_s$ is given by $f \mapsto \frac{f - sf}{\alpha_s}$.
\end{definition*}

With this, we can now describe the ``primitive'' maps for blue lines in table \ref{tab:prim_maps}.  The corresponding equations hold for red in $t$.

\begin{table}[ht]
	\[
	\begin{array}{rll}
		\text{Map} & \text{Modules} & \text{Description} \\[1em]
		\barbell{half_top} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
		\barbell{half_bot} & R \to R \ttimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
		\barbell{tri_down} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
		\barbell{tri_up} & R \stimes R \stimes R \to R \stimes R & 1 \mid g \mid 1 \mapsto \partial_s(g) \mid 1 \\[1em]
		\barbell{id} & R \stimes R \to R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \\[1em]
	\end{array}
	\]
	\caption{Describing the maps.}
	\label{tab:prim_maps}
\end{table}

Note that the descriptions are sufficient to determine outputs for all values because these morphisms respect left and right actions, as prescribed in \eqref{eq:respect}.

Maps are composed by juxtaposition, and disjoint portions of the diagrams act independently.  Therefore, by a combination of these structures, we can generate arbitrarily complicated maps.  For example, the map in figure \ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d. \]

Henceforth we will make the convenient abbreviation of $\barbell{tri_up_contract_before}$ as $\barbell{tri_up_contract_after}$.  It will also be understood that edges need not be straight lines, but any topologically equivalent deformation shall represent the same graph.  With this understanding, any of the graphs described in the previous section can be viewed as compositions of the primitive structures we describe here.

Subsequently, for any polynomial $f \in R$ we will abuse notation and refer to the map $x \mapsto fx$ by simply $f$.  In particular, one can easily verify that $\barbell{barbell_blue}$ represents $\alpha_s$.  Note that this is \emph{not} in general the same as $x \mapsto xf$ because $x$ may belong to some bimodule rather than to $R$.  Phrased diagrammatically, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \barbell{barbell_blue}\barbell{alpha_blue} = \alpha_s$, for instance.

\subsection{Operations for Diagrammatics}
\label{sec:prelim_genrel}
From the algebraic context given above, one can derive the following relationships, which are here encoded completely graphically.  These rules are sufficient to compute the maps we are interested in.

\setcounter{op}{-1}
\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  \end{op}
\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$ and the similar equation for red.  \end{op}
\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$ and the similar equation for red.  \end{op}
\begin{op}[The Needle] We have $\barbell{needle} = 0$.  Similarly, the red needle yields zero.  \end{op}
\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well. In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.  \end{remark*}
\begin{op}[Barbell-Forcing Rules]
	We have the following three equalities:
	\begin{enumerate}[(a)]
		\ii $\barbell{barbell_blue}\barbell{alpha_blue} + \barbell{alpha_blue} \barbell{barbell_blue} = 2 \barbell{break_blue}$, and the similar equation for red.
		\ii $\barbell{alpha_red}\barbell{barbell_blue} = -x\barbell{break_red} + \barbell{barbell_blue}\barbell{alpha_red} + x \barbell{barbell_red}\barbell{alpha_blue}$.
		\ii $\barbell{alpha_blue}\barbell{barbell_red} = -y\barbell{break_blue} + \barbell{barbell_red}\barbell{alpha_blue} + y \barbell{barbell_blue}\barbell{alpha_red}$.
	\end{enumerate}
\end{op}

Furthermore, one can again verify that $\barbell{barbell_blue}$, when on the far left, is simply $\alpha_s$.

\subsection{Libedinsky's Light Leaves}
\label{sec:prelim_lightleave}
\begin{figure}[ht]
	\centering
	\begin{asy}
	size(10cm);
	real h = 0.7;
	pen s = blue, t = dashed + red + 0.6;
	int n = 14;
	draw(currentpicture, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
	draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
	draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
	draw(currentpicture, (4,0)--(4,h/2)..((4+8)/2.0,h*4)..(8,h/2)--(8,0), t);
	draw(currentpicture, (8,0)--(8,h/2)..((8+9)/2.0,h*1)..(9,h/2)--(9,0), t);
	draw(currentpicture, (11,0)--(11,h/2)..((11+13)/2.0,h*2)..(13,h/2)--(13,0), t);
	draw(currentpicture, (1,0)--(1,h), t);dot(currentpicture, (1,h), red);
	draw(currentpicture, (7,0)--(7,h), s);dot(currentpicture, (7,h), s);
	draw(currentpicture, (12,0)--(12,h), s);dot(currentpicture, (12,h), s);
	draw(currentpicture,(9,0)--(9,5*h), t);
	draw(currentpicture,(10,0)--(10,5*h), s);
	dot(currentpicture, (2, h/2), blue);
	dot(currentpicture, (8, h/2), red);
	dot(currentpicture, (9, h/2), red);
	label(currentpicture, "1", (0,-1.5h), dir(90));
	label(currentpicture, "s", (0,-0.8*h), dir(90));
	label(currentpicture, "0", (1,-1.5h), dir(90));
	label(currentpicture, "t", (1,-0.8*h), dir(90));
	label(currentpicture, "0", (2,-1.5h), dir(90));
	label(currentpicture, "s", (2,-0.8*h), dir(90));
	label(currentpicture, "1", (3,-1.5h), dir(90));
	label(currentpicture, "s", (3,-0.8*h), dir(90));
	label(currentpicture, "1", (4,-1.5h), dir(90));
	label(currentpicture, "t", (4,-0.8*h), dir(90));
	label(currentpicture, "1", (5,-1.5h), dir(90));
	label(currentpicture, "s", (5,-0.8*h), dir(90));
	label(currentpicture, "1", (6,-1.5h), dir(90));
	label(currentpicture, "s", (6,-0.8*h), dir(90));
	label(currentpicture, "0", (7,-1.5h), dir(90));
	label(currentpicture, "s", (7,-0.8*h), dir(90));
	label(currentpicture, "0", (8,-1.5h), dir(90));
	label(currentpicture, "t", (8,-0.8*h), dir(90));
	label(currentpicture, "0", (9,-1.5h), dir(90));
	label(currentpicture, "t", (9,-0.8*h), dir(90));
	label(currentpicture, "1", (10,-1.5h), dir(90));
	label(currentpicture, "s", (10,-0.8*h), dir(90));
	label(currentpicture, "1", (11,-1.5h), dir(90));
	label(currentpicture, "t", (11,-0.8*h), dir(90));
	label(currentpicture, "0", (12,-1.5h), dir(90));
	label(currentpicture, "s", (12,-0.8*h), dir(90));
	label(currentpicture, "1", (13,-1.5h), dir(90));
	label(currentpicture, "t", (13,-0.8*h), dir(90));
	\end{asy}
	\caption{An example of light leaves.}
	\label{fig:lightleaf_example}
\end{figure}

Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any any binary string $\ul b$ of length $n$, we can construct a diagram based on a series of rules.

Each bit of $\ul b$ is read from left to right in order and designated either up or down.  We say that a bit $x$ is an \emph{open neighbor} of $y$ if $x$ is marked up, $x$ and $y$ have the same color, and there are no other bits marked up between $x$ and $y$.
\begin{itemize}
	\ii If the bit is a $1$:
	\begin{itemize}
		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, and mark both bits as down.
		\ii Otherwise, designate the current bit as up.
	\end{itemize}
	\ii If the bit is $0$:
	\begin{itemize}
		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, mark the previous bit as down, and the current bit as up.
		\ii Otherwise, create a ``stub'', i.e. a single vertex of degree one, and mark the current bit as down.
	\end{itemize}
\end{itemize}
Finally, join any bits which are up at the end of the process to the opposite end.  An example of such a light leaf is shown in figure \ref{fig:lightleaf_example}.

These light leaves are interesting because, in the seventh chapter of \cite{span}, it is shown that these light leaves for a ``basis'' in the sense that all maps may be expressed using those generated by light leaves (modulo lower terms).

\subsection{Problem Statement}
\label{sec:prelim_probstate}
Recall that maps are multiplied by simply placing them on top of each other.  The operations are then applied to simplify the product.

\begin{figure}[ht]
	\centering
	\begin{asy}
	size(4cm);
	real h = 0.7;
	pen s = blue, t = red + dashed + 0.6;
	pen dot_s = blue, dot_t = red;
	int n = 7;

	picture one;
	draw(one, (0,0)--(0,h/2)..((0+3)/2.0,h*3)..(3,h/2)--(3,0), s);
	draw(one, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), t);
	draw(one, (1,0)--(1,h), t);
	dot(one, (1,h), dot_t);
	draw(one, (2,0)--(2,h), t);
	dot(one, (2,h), dot_t);
	draw(one, (5,0)--(5,h), s);
	dot(one, (5,h), dot_s);
	draw(one,(6,0)--(6,4*h), t);
	dot(one, (6, h/2), dot_t);

	picture two;
	draw(two, (0,0)--(0,h/2)..((0+3)/2.0,h*3)..(3,h/2)--(3,0), s);
	draw(two, (1,0)--(1,h), t);
	dot(two, (1,h), dot_t);
	draw(two, (2,0)--(2,h), t);
	dot(two, (2,h), dot_t);
	draw(two, (4,0)--(4,h), t);
	dot(two, (4,h), dot_t);
	draw(two, (5,0)--(5,h), s);
	dot(two, (5,h), dot_s);
	draw(two,(6,0)--(6,4*h), t);

	add(one); add(reflect((0,0),(1,0))*two);
	draw((-1,0)--(7,0));
	\end{asy}
	\caption{An example of composing two maps, 1001100 and 1001001.}
\end{figure}

\begin{definition*}
	A map is \emph{idempotent} if multiplying it with itself returns the original graph.
\end{definition*}
Colloquially, $m^2=m$ if and only if $m$ is idempotent.

Fix an $\ul r$.  If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.  This motivates us to construct potential idempotents by taking two light leaves whose top sequences are identical, and composing $A$ upside-down with $B$.  If $AB=1$, then this will yield an idempotent.

This motivates the main objective of study.
\begin{ques*}
	For a fixed $\ul r$ and two binary sequences $\ul a$ and $\ul b$ with the same top, can one determine their product based on $\ul a$ and $\ul b$?
\end{ques*}

In this question, we will consider only maps with the same top, and we will also work \emph{modulo lower terms}.  This means that any map which has a component that touches either the top or bottom boundary exactly once will be treated as zero.  In that case, using the operations described in section \ref{sec:prelim_genrel}, we can reduce every map to simply multiplying by a polynomial on the left.  The goal is to then compute these polynomials using some combinatorial formula.

\section{Notations}
For each positive integer $n$, let us define for convenience the strings
\[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
and
\[
	\AA_n \defeq
	\begin{cases}
		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
	\end{cases}.
\]
By the way, let $\BB_n$ denote the set of binary strings of length $n$.

Consider a string $\ul r$ of letters $s$ and $t$.  Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the appropriate map formed by a single application of the light leaves.  
Additionally, let $\Top_{\ul r} \ul b$ denote the top of the map $\MM_{\ul r}(\ul b)$.

Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.  Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on

If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.

Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.

\section{One-Color Case: Characterizing $\MM_{\SS_n}(\ul a, \ul b)$}
In this section we provide a complete characterization for the $\MM_{\SS_n}(\ul a, \ul b)$.  The proof is effectively trivial, but requires some rather irritating details and definitions in order to be clear.

First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
\begin{definition*}
	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
\end{definition*}
\begin{proposition}
	For any $\ul b$ of length $n$, \[
		\Top_{\SS_n} \ul b =
		\begin{cases}
			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
		\end{cases}.
		\]
\end{proposition}
\begin{proof}
	Left as exercise. (It should take about a minute.)
\end{proof}

Subsequently, we make the following definition.
\begin{definition*}
	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
	\[
		\ul b^\ast [i] = 
		\begin{cases}
			1 & \text{if } b[1] + b[2] + \dots + b[i] = equiv 1 \pmod{2} \\
			0 & \text{otherwise}
		\end{cases}.
	\]
\end{definition*}
This lets us state our main result for this section.
\begin{theorem}
	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
	\[
		\MM_{\SS_n} \left( \ul a, \ul b \right)
		=
		\begin{cases}
			0 & \text{if } \exists 1 \le i \le n-1: \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
		\end{cases}.
	\]
\end{theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
size(7cm);
real h = 0.7;
pen s = blue, t = red + dashed + 0.6;
pen dot_s = blue, dot_t = red;
int n = 8;
draw(currentpicture, (0,0)--(0,h/2)..\left( 0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
draw(currentpicture, (1,0)--(1,h/2)..\left( 1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
draw(currentpicture, (2,0)--(2,h/2)..\left( 2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
draw(currentpicture, (5,0)--(5,h/2)..\left( 5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
draw(currentpicture, (4,0)--(4,h), s);
dot(currentpicture, (4,h), dot_s);
draw(currentpicture, (7,0)--(7,h), s);
dot(currentpicture, (7,h), dot_s);
dot(currentpicture, (1, h/2), dot_s);
dot(currentpicture, (2, h/2), dot_s);
label(currentpicture, "1", (0,-1.5h), dir(90));
label(currentpicture, "s", (0,-0.8*h), dir(90));
label(currentpicture, "0", (1,-1.5h), dir(90));
label(currentpicture, "s", (1,-0.8*h), dir(90));
label(currentpicture, "0", (2,-1.5h), dir(90));
label(currentpicture, "s", (2,-0.8*h), dir(90));
label(currentpicture, "1", (3,-1.5h), dir(90));
label(currentpicture, "s", (3,-0.8*h), dir(90));
label(currentpicture, "0", (4,-1.5h), dir(90));
label(currentpicture, "s", (4,-0.8*h), dir(90));
label(currentpicture, "1", (5,-1.5h), dir(90));
label(currentpicture, "s", (5,-0.8*h), dir(90));
label(currentpicture, "1", (6,-1.5h), dir(90));
label(currentpicture, "s", (6,-0.8*h), dir(90));
label(currentpicture, "0", (7,-1.5h), dir(90));
label(currentpicture, "s", (7,-0.8*h), dir(90));
	\end{asy}
	\caption{It looks hard until you actually draw it.  Then you LOL.}
\end{figure}
\begin{proof}
	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.

	Number the ``vertices'' on the bottom boundary of from $1$ to $n$, from left to right.

	For a map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the points on the bottom boundary it touches.  Note that the antennae always form a contiguous sequence of integers, by construction.

	Now, we observe that for each $1 \le i \le n-1$, we have that $\ul a^\ast[i] = 1$ if and only if $i$ and $i+1$ are both antennae of some component.

	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$.  Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel each $k$ times} if they have $k$ antennae in common.  Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because there can be no other structures inside these faces.  Furthermore, it is easy to see that any faces must be formed in this manner.

	On the other hand, suppose this product is nonzero, and consider a component from the top with $k$ antennae.  Each of its antennae then feels a distinct component.  Hence, it unites $k$ different components into one.

	The formula then follows directly from counting the number of connected components, because each component can be contracted into a single $\alpha_s$ term (a barbell), and there are no other structures possible.
\end{proof}

\section{Main Result}
\label{sec:mainresult}
%I wish I had one.

\section{Conclusion}
% The conclusion should be a brief summary of what you have done.  You wish to leave the reader with a clear impression of your ideas and what you have accomplished.  This section is typically extremely short and in the past tense.

\section{Acknowledgments} 
I offer my sincerest gratitude\footnote{That sounded horribly fake, but really, I mean it.  You guys are the best.  Thank you for a great project.} to my mentor Mr. Francisco Unda for daily mentorship, and Dr. Benjamin Elias for providing the project and for often meeting with me personally to discuss it.
I further wish to thank the MIT Math Department, and in particular the head mentor Dr. Tanya Khovanova, for organizing the Math RSI, providing individual discussion with each student outside of the mentorship, as well as organizing additional meetings and lectures.
I also wish to thank my tutor Mr. Antoni Rangachev for his invaluable advice in preparing both this paper and my final presentation.
Finally, I would like to thank the Center for Excellence in Education and the Research Science Institute for generously providing the facilities for the research.

### 2013-07-19 summary.tex
Initial commit.

% This is summary.tex

The non-technical summary is like an abstract, but without any technical
terminology. So instead of $v = (v_0, v_1, \ldots, v_n)$, you might say
something along the lines of ``pick a point in high-dimensional space.''
Don't worry about this section yet; you'll receive more guidance
later on, when you're near the end of your mentorship.

### 2013-07-19 paper.tex
omnomnom

@@
 Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:prelim_probstate}.
+
 % TODO change this
@@
 \[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
-and
+and the ``alternating'' string
 \[
@@
 \begin{proof}
-	Left as exercise. (It should take about a minute.)
+	Straightforward induction on $n$.  
 \end{proof}
@@
 		\begin{cases}
-			1 & \text{if } b[1] + b[2] + \dots + b[i] = equiv 1 \pmod{2} \\
+			1 & \text{if } b[1] + b[2] + \dots + b[i] \equiv 1 \pmod{2} \\
 			0 & \text{otherwise}
@@
 		int n = 8;
-draw(currentpicture, (0,0)--(0,h/2)..\left( 0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
-draw(currentpicture, (1,0)--(1,h/2)..\left( 1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
-draw(currentpicture, (2,0)--(2,h/2)..\left( 2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
-draw(currentpicture, (5,0)--(5,h/2)..\left( 5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
+		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
+		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
+		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
+		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
 		draw(currentpicture, (4,0)--(4,h), s);
@@
 	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$.
-Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel each $k$ times} if they have $k$ antennae in common.
-Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because there can be no other structures inside these faces.
+Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel} each other $k$ times if they have $k$ antennae in common.
+Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because the two antenna combine to form an empty face.
 Furthermore, it is easy to see that any faces must be formed in this manner.
+In combination with the claim above, this implies the first case of the theorem.
 
@@
 
-\section{Main Result}
-\label{sec:mainresult}
-%I wish I had one.
+\section{The Caterpillar Theorem}
+\label{sec:caterpillar}
+We turn our attention to the case of $\ul r = \AA_n$.  Let us make a few definitions before proceeding.
+
+Consider a composition of two maps $\MM_{\AA_n}( \ul a, \ul b)$ and the associated diagram $D$.  Let us make a few convenient definitions for the graphical structures.
+\begin{definition*}
+	A \emph{pocket} is a face, and its \emph{contents} are the connected components inside that face.
+\end{definition*}
+\begin{definition*}
+	A \emph{fence} is a contiguous path which runs from the top of the boundary to the bottom of the boundary (i.e.
+paths between the labelled vertices).
+The diagram is divided by these fences into \emph{pastures}, which will be numbered from left to right as $0$, $1$, \dots, $M$.
+\end{definition*}
 

### 2013-07-19 paper.tex
Slides.

@@
 
-\section{Notations}
+\section{Definitions and Notations}
+\subsection{Notations for Strings}
 For each positive integer $n$, let us define for convenience the strings
@@
 
-Consider a string $\ul r$ of letters $s$ and $t$.  Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the appropriate map formed by a single application of the light leaves.  
-Additionally, let $\Top_{\ul r} \ul b$ denote the top of the map $\MM_{\ul r}(\ul b)$.
+Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.
+
+\subsection{Definitions for Maps and Diagram}
+Consider a string $\ul r$ of letters $s$ and $t$.  Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the appropriate map (or its associated diagram;
+we will refer to maps and their associated diagrams interchangably) formed by a single application of the light leaves.
+We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.
+Additionally, let $\Top_{\ul r} \ul b$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.
 
 Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.
-Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on
-
+(Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on.)  Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.
 If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.
 
-Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.
+Recall that the light leaves are based off a sequence of vertices at the bottom boundary of a half-map.
+We will call those vertices, whether on the bottom boundary of a half-map or the center of a full-map, the \emph{anchors} for that map, and the associated sequence of letters the \emph{base}.
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(4cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 5;
+
+		picture one;
+		draw(one, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+		draw(one, (1,0)--(1,h), t);
+		dot(one, (1,h), dot_t);
+		draw(one, (3,0)--(3,h), t);
+		dot(one, (3,h), dot_t);
+		draw(one, (4,0)--(4,h), s);
+		dot(one, (4,h), dot_s);
+
+		picture two;
+		draw(two, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
+		draw(two, (0,0)--(0,h/2)..((0+4)/2.0,h*4)..(4,h/2)--(4,0), s);
+		draw(two, (2,0)--(2,h), s);
+		dot(two, (2,h), dot_s);
+
+		add(one); add(reflect((0,0),(1,0))*two);
+		draw((-1,0)--(5,0));
+	\end{asy}
+	\caption{A full-map with base $ststs$, hence with five anchors.  The top is $\varnothing$.}
+\end{figure}
+
+\subsection{Nomenclature for Certain Structures in Diagrams}
+Let us make a few convenient definitions.
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(5cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 10;
+
+		picture one;
+		draw(one, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), s);
+		draw(one, (3,0)--(3,h/2)..((3+7)/2.0,h*4)..(7,h/2)--(7,0), t);
+		draw(one, (2,0)--(2,h/2)..((2+8)/2.0,h*6)..(8,h/2)--(8,0), s);
+		draw(one, (1,0)--(1,h/2)..((1+9)/2.0,h*8)..(9,h/2)--(9,0), t);
+		draw(one, (5,0)--(5,h), t);
+		dot(one, (5,h), dot_t);
+		draw(one,(0,0)--(0,9*h), s);
+
+		picture two;
+		draw(two, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+		draw(two, (1,0)--(1,h/2)..((1+5)/2.0,h*4)..(5,h/2)--(5,0), t);
+		draw(two, (0,0)--(0,h/2)..((0+6)/2.0,h*6)..(6,h/2)--(6,0), s);
+		draw(two, (3,0)--(3,h), t);
+		dot(two, (3,h), dot_t);
+		draw(two, (7,0)--(7,h), t);
+		dot(two, (7,h), dot_t);
+		draw(two, (9,0)--(9,h), t);
+		dot(two, (9,h), dot_t);
+		draw(two,(8,0)--(8,7*h), s);
+
+		add(one); add(reflect((0,0),(1,0))*two);
+		draw((-1,0)--(10,0));
+	\end{asy}
+	\caption{Two blue barbells with a very twisted fence, which creates two pastures.}
+\end{figure}
+
+\begin{definition*}
+	A connected component which (i) is a tree, and (ii) does not touch the top or bottom boundaries is called a \emph{barbell}.
+\end{definition*}
+Notice that, by homotopy, every blue barbell is simply $\barbell{barbell_blue}$, which evaluates as $\alpha_s$.  Similarly, every red barbell is simply $\barbell{barbell_red} = \alpha_t$.
+
+\begin{definition*}
+	A \emph{fence} is a contiguous path which runs from the top of the boundary to the bottom of the boundary (i.e.
+paths between the labelled vertices).
+The diagram is divided by these fences into \emph{pastures}, which will be numbered from left to right as $0$, $1$, \dots, $k$, where $k$ is the number of fences.
+\end{definition*}
+
+We remind the reader that we are working modulo lower terms; any map which contains a ``half fence'' (i.e. a connected component which touches a boundary exactly once) is not considered.
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(4cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 4;
+
+		picture one;
+		draw(one, (0,0)--(0,h/2)..((0+3)/2.0,h*3)..(3,h/2)--(3,0), s);
+		draw(one, (1,0)--(1,h), t);
+		dot(one, (1,h), dot_t);
+		draw(one, (2,0)--(2,h), t);
+		dot(one, (2,h), dot_t);
+
+		picture two;
+		draw(two, (0,0)--(0,h/2)..((0+3)/2.0,h*3)..(3,h/2)--(3,0), s);
+		draw(two, (1,0)--(1,h), t);
+		dot(two, (1,h), dot_t);
+		draw(two, (2,0)--(2,h), t);
+		dot(two, (2,h), dot_t);
+
+		add(one); add(reflect((0,0),(1,0))*two);
+		draw((-1,0)--(4,0));
+	\end{asy}
+	\caption{A blue bubble with two barbells inside it.}
+\end{figure}
+
+\begin{definition*}
+	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its contents.  It may be connected to a fence, in which case we call it \emph{attached}.
+\end{definition*}
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(6cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 7;
+
+		picture one;
+		draw(one, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+		draw(one, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+		draw(one, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), s);
+		draw(one, (1,0)--(1,h), t);
+		dot(one, (1,h), dot_t);
+		draw(one, (3,0)--(3,h), t);
+		dot(one, (3,h), dot_t);
+		draw(one, (5,0)--(5,h), t);
+		dot(one, (5,h), dot_t);
+		dot(one, (2, h/2), dot_s);
+		dot(one, (4, h/2), dot_s);
+
+		picture two;
+		draw(two, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+		draw(two, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+		draw(two, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), s);
+		draw(two, (1,0)--(1,h), t);
+		dot(two, (1,h), dot_t);
+		draw(two, (3,0)--(3,h), t);
+		dot(two, (3,h), dot_t);
+		draw(two, (5,0)--(5,h), t);
+		dot(two, (5,h), dot_t);
+		dot(two, (2, h/2), dot_s);
+		dot(two, (4, h/2), dot_s);
+
+		add(one); add(reflect((0,0),(1,0))*two);
+		draw((-1,0)--(7,0));
+	\end{asy}
+	\caption{A caterpillar made of three bubbles}
+\end{figure}
+
+\begin{definition*}
+	A \emph{caterpillar} is any connected collection of bubbles.
+\end{definition*}
 
@@
 
-	Number the ``vertices'' on the bottom boundary of from $1$ to $n$, from left to right.
+	Number the anchors $1$, $2$, $\dots$ from left to right.
 
-	For a map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the points on the bottom boundary it touches.
-Note that the antennae always form a contiguous sequence of integers, by construction.
+	For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.  Note that the antennae always form a single contiguous sequence of anchors.
 
@@
 
-	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$.
+	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$ to obtain a full-map.
 Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel} each other $k$ times if they have $k$ antennae in common.
-Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because the two antenna combine to form an empty face.
-Furthermore, it is easy to see that any faces must be formed in this manner.
+Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because the two antenna combine to form an empty bubble.
+Furthermore, it is easy to see that any bubbles must be formed in this manner.
 In combination with the claim above, this implies the first case of the theorem.
@@
 
-	The formula then follows directly from counting the number of connected components, because each component can be contracted into a single $\alpha_s$ term (a barbell), and there are no other structures possible.
+	The formula then follows directly from counting the number of connected components, because each component can be contracted into a single barbell, since any acyclic connected component is merely a tree.
 \end{proof}
@@
 \label{sec:caterpillar}
-We turn our attention to the case of $\ul r = \AA_n$.  Let us make a few definitions before proceeding.
-
-Consider a composition of two maps $\MM_{\AA_n}( \ul a, \ul b)$ and the associated diagram $D$.  Let us make a few convenient definitions for the graphical structures.
-\begin{definition*}
-	A \emph{pocket} is a face, and its \emph{contents} are the connected components inside that face.
-\end{definition*}
-\begin{definition*}
-	A \emph{fence} is a contiguous path which runs from the top of the boundary to the bottom of the boundary (i.e.
-paths between the labelled vertices).
-The diagram is divided by these fences into \emph{pastures}, which will be numbered from left to right as $0$, $1$, \dots, $M$.
-\end{definition*}
+We now turn our attention to the case of $\ul r = \AA_n$.
 

### 2013-07-20 paper.tex
Very extended introduction.

@@
 
-\section{Preliminaries}
+\section{Preliminaries and Definitions}
+\subsection{An Extended Introduction}
 \label{sec:prelim}
@@
 
-\subsection{Diagrammatics of Maps}
+\subsubsection{Diagrammatics of Maps}
 \label{sec:prelim_map}
@@
 
-\subsection{Algebraic Context}
+\subsubsection{Algebraic Context}
 The maps are conventionally read from bottom to top.
@@
 
-Subsequently, for any polynomial $f \in R$ we will abuse notation and refer to the map $x \mapsto fx$ by simply $f$.
+% Subsequently, for any polynomial $f \in R$ we will abuse notation and refer to the map $x \mapsto fx$ by simply $f$.
 In particular, one can easily verify that $\barbell{barbell_blue}$ represents $\alpha_s$.
@@
 
-\subsection{Operations for Diagrammatics}
+\subsubsection{Operations for Diagrammatics}
 \label{sec:prelim_genrel}
@@
 
-\subsection{Libedinsky's Light Leaves}
+\subsubsection{Libedinsky's Light Leaves}
 \label{sec:prelim_lightleave}
@@
 
-\subsection{Problem Statement}
+\subsubsection{Problem Statement}
 \label{sec:prelim_probstate}
@@
 
-In this question, we will consider only maps with the same top, and we will also work \emph{modulo lower terms}.
+Further details on the evaluation of these maps are detailed in section \ref{sec:explain_poly_eval}, but before that we need to introduce certain definitions for clarity.
+
+% In this question, we will consider only maps with the same top, and we will also work \emph{modulo lower terms}.
 This means that any map which has a component that touches either the top or bottom boundary exactly once will be treated as zero.
@@
 
-\section{Definitions and Notations}
-\subsection{Notations for Strings}
+\subsection{Definitions and Notations}
+\subsubsection{Notations for Strings}
 For each positive integer $n$, let us define for convenience the strings
@@
 \]
-By the way, let $\BB_n$ denote the set of binary strings of length $n$.
+Let $\BB_n$ denote the set of binary strings of length $n$.
 
@@
 
-\subsection{Definitions for Maps and Diagram}
+\subsubsection{Definitions for Maps and Diagram}
 Consider a string $\ul r$ of letters $s$ and $t$.  Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the appropriate map (or its associated diagram;
@@
 Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.
-(Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on.)  Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.
+% (Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on.)
+Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.
 If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.
@@
 
-\subsection{Nomenclature for Certain Structures in Diagrams}
+% We will now abuse notation further and refer even to components by polynomials, when the map is left alone.
+For example, $\barbell{alpha_blue}\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}$ might be referred interchangeably with $\barbell{alpha_blue} \alpha_s^2 \alpha_t$.
+Note that, even though we may write $\barbell{alpha_blue} = 1$, we still have $\barbell{alpha_blue} \alpha_s^2\alpha_t \neq \alpha_s^2\alpha_t$, because we strictly require left multiplication as the accepted convention.
+
+\subsubsection{Nomenclature for Certain Structures in Diagrams}
 Let us make a few convenient definitions.
@@
 \begin{definition*}
-	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its contents.  It may be connected to a fence, in which case we call it \emph{attached}.
+	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its \emph{contents}.  
 \end{definition*}
@@
 \end{definition*}
+
+\subsection{Representations of Maps as Polynomials}
+% TODO actually do this
 
@@
 	\end{asy}
-	\caption{It looks hard until you actually draw it.  Then you LOL.}
+	\caption{A half-map with base $\SS_8$.}
 \end{figure}
@@
 
-\section{The Caterpillar Theorem}
+\section{Constraints on the Diagrammatics in the Alternating Case}
 \label{sec:caterpillar}
 We now turn our attention to the case of $\ul r = \AA_n$.
+
+In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
+\begin{lemma}[Bubble Lemma]
+	Consider a bubble in a full-diagram with base $\AA_n$.  The contents of the bubble are either a barbell or a caterpillar.
+\end{lemma}
+\begin{corollary}[Caterpillar Corollary]
+	A caterpillar in a full-diagram with base $\AA_n$ evaluates as 
+\end{corollary}<++>
 

### 2013-07-20 paper.tex
2nd milestone.

@@
 
-% TODO change this
-We then do a bunch of nonsense.
+TODO: Add road map once I figure out what results I actually have
 
 \section{Preliminaries and Definitions}
+NOTE: If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dotted for readability.
+
 \subsection{An Extended Introduction}
@@
 
-Furthermore, one can again verify that $\barbell{barbell_blue}$, when on the far left, is simply $\alpha_s$.
+% Furthermore, one can again verify that $\barbell{barbell_blue}$, when on the far left, is simply $\alpha_s$.
 
@@
 
-Further details on the evaluation of these maps are detailed in section \ref{sec:explain_poly_eval}, but before that we need to introduce certain definitions for clarity.
+Further details on the evaluation of these maps are detailed in section \ref{sec:prelim_explain_poly_eval}, but before that we need to introduce certain definitions for clarity.
 
@@
 \end{definition*}
+\begin{definition*}
+	A component is called \emph{attached} if it is connected to a fence.  Otherwise, it is \emph{free}.  By convention, any attached components belong to the pasture to the left of the associated fence.
+\end{definition*}
 
-We remind the reader that we are working modulo lower terms; any map which contains a ``half fence'' (i.e. a connected component which touches a boundary exactly once) is not considered.
+% We remind the reader that we are working modulo lower terms; any map which contains a ``half fence'' (i.e. a connected component which touches a boundary exactly once) is not considered.
 
@@
 \begin{definition*}
-	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its \emph{contents}.  
+	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its \emph{contents}.  The color of the bubble is the color of the edges which form the bounded face.
 \end{definition*}
@@
 \begin{definition*}
-	A \emph{caterpillar} is any connected collection of bubbles.
+	A \emph{caterpillar} is any connected component for which each edge belongs to some bubble (in the caterpillar).  The \emph{size} of the caterpillar is the number of bubbles it is composed of.
 \end{definition*}
 
+Notice that every free component can be expressed as a collection of caterpillars joined by edges.
+Furthermore, every attached component can be described as a free component attached by edges to a fence.
+
 \subsection{Representations of Maps as Polynomials}
-% TODO actually do this
+\label{sec:prelim_explain_poly_eval}
 
-\section{One-Color Case: Characterizing $\MM_{\SS_n}(\ul a, \ul b)$}
+In order to study these maps as algebraic structures, we wish to consider full-maps as polynomials in $\RR[x,y][\alpha_s,\alpha_t]$.  Hence, we establish the following conventions:
+\begin{enumerate}
+	\ii The map $x \mapsto fx$ will be abbreviated as $f$ from this point forward.  
+	\par Note that, in particular, $\barbell{barbell_blue} = \alpha_s$.
+Furthermore, one can check that, say, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.
+	Please note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \alpha_s$.
+	\ii We will work \emph{modulo lower terms}.
+That is, any map which contains a connected component that touches any boundary only once (total) is considered zero.
+So, for example, $\barbell{break_blue} = 0$.
+\end{enumerate}
+Henceforth, we will refer to diagrams and their associated polynomials interchangeably.
+
+One can verify that, using the barbell-forcing rules, we can recursively move all barbells to the right, and any ``broken'' walls are reduced to zero, or are contracted.
+Hence, any full-diagram can be reduced to linear combinations of maps of the form $x \mapsto \alpha_s^m \alpha_t^n x$.
+In other words, every full diagram can be represented as a polynomial in $\RR[x,y][\alpha_s,\alpha_t]$.
+
+In fact, we can even show that, with this new convention, that the following identity holds for every $f$:
+\begin{equation}
+	\barbell{alpha_blue} f = \partial_s(f) \barbell{break_blue} + s(f) \barbell{alpha_blue}
+	\label{eq:barbell_break}
+\end{equation}
+where $\partial_s$ is the Demazure operator defined in section \ref{sec:prelim_genrel}.
+
+The problem statement then becomes to compute the polynomial $\MM_{\ul r}(\ul a, \ul b)$ with a formula in terms of $\ul r$, $\ul a$, $\ul b$.
+
+\section{A Complete Characterization of the One-Color Case}
 In this section we provide a complete characterization for the $\MM_{\SS_n}(\ul a, \ul b)$.
@@
 
-\section{Constraints on the Diagrammatics in the Alternating Case}
-\label{sec:caterpillar}
+\section{Constraints in the Alternating Case}
 We now turn our attention to the case of $\ul r = \AA_n$.
@@
 \begin{corollary}[Caterpillar Corollary]
-	A caterpillar in a full-diagram with base $\AA_n$ evaluates as 
-\end{corollary}<++>
+	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
+\end{corollary}
+\begin{theorem}[Pasture Theorem]
+	Consider a full-diagram with $N+1$ pastures with base $\AA_n$, numbered $0$, $1$, \dots, $N$, where $N \ge 1$.  Then
+	\begin{enumerate}[(i)]
+		\ii Pastures $1$ to $N-1$ contain no free components and at most one attached component.
+		\ii Pasture $N$ contains at most one free component, either a caterpillar or a barbell.
+	\end{enumerate}
+\end{theorem}
+
+TODO: Work out details of the proofs.
+
+\section{A Recursion for the Alternating Case}
 

### 2013-07-22 paper.tex
Meeting Tanya in 20 minutes oops.

@@
 \section{Preliminaries and Definitions}
-NOTE: If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dotted for readability.
+NOTE: If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.
 
@@
 \]
-Let $\BB_n$ denote the set of binary strings of length $n$.
+Similarly, let $\AA_n'$ denote $AA_n$, except with the roles of $s$ and $t$ switched.  Note that $\AA_0 = \AA_0' = \varnothing$.
+
+In general, a string of $s$'s and $t$'s will be referred to as an \emph{expression}.
+In the case where there are no consecutive identical characters (e.g.
+$\AA_n$), we will refer to them as \emph{reduced expressions}.
+
+Next, let $\BB_n$ denote the set of binary strings of length $n$.
 
@@
 Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.
-% (Recall that we are abusing notation in such products, and will simply refer to the map $g \mapsto fg$ as $f$ from this point on.)
 Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.
@@
 We will call those vertices, whether on the bottom boundary of a half-map or the center of a full-map, the \emph{anchors} for that map, and the associated sequence of letters the \emph{base}.
+Furthermore, the line on which the anchors lie will be called the \emph{anchorline}.
 
@@
 \begin{definition*}
-	A \emph{bubble} is a bounded face alongside with any components contained within it, which are its \emph{contents}.  The color of the bubble is the color of the edges which form the bounded face.
+	A \emph{bubble} is a bounded face alongside with any components contained within it.  The \emph{color} of the bubble is the color of the edges which form the bounded face.  
+\end{definition*}
+\begin{definition*}
+	We say that the bubble $B$ \emph{holds} a component $c$ if $c$ is inside $B$, but there is no other bubble $B'$ inside $B$ which contains $c$.  
 \end{definition*}
@@
 \begin{definition*}
-	A \emph{caterpillar} is any connected component for which each edge belongs to some bubble (in the caterpillar).  The \emph{size} of the caterpillar is the number of bubbles it is composed of.
+	A \emph{caterpillar} consists of a free component and the contents of any bubbles it contains.  A caterpillar \emph{holds} a component if some bubble of the caterpillar holds it.
 \end{definition*}
-
-Notice that every free component can be expressed as a collection of caterpillars joined by edges.
-Furthermore, every attached component can be described as a free component attached by edges to a fence.
+\begin{remark*}
+	Notice that any barbell or bubble is a special case of a caterpillar.
+\end{remark*}
 
@@
 
-One can verify that, using the barbell-forcing rules, we can recursively move all barbells to the right, and any ``broken'' walls are reduced to zero, or are contracted.
+One can verify that, using the barbell-forcing rules, we can recursively move all barbells to the left, and any ``broken'' walls are reduced to zero, or are contracted.
 Hence, any full-diagram can be reduced to linear combinations of maps of the form $x \mapsto \alpha_s^m \alpha_t^n x$.
@@
 In this section we provide a complete characterization for the $\MM_{\SS_n}(\ul a, \ul b)$.
-The proof is effectively trivial, but requires some rather irritating details and definitions in order to be clear.
+% The proof is effectively trivial, but requires some rather irritating details and definitions in order to be clear.
 
@@
 
+\section{Counting Maps}
+TODO: Write up / prove the formula for number of maps from $A$ to $B$.
+
+For each expression $\ul T$ and $\ul r$, we give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r}(\ul b) = \ul T$.
+One can check that, by construction, $\Top(\ul b)$ is always a reduced expression.
+
+\begin{definition*}
+	Let $R(\ul r)$ denote the $\ul r$ with any consecutive blocks of $s$'s replaced by a single $s$, and similarly for $t$.
+\end{definition*}
+For example, $R(sststttts) = ststs$.
+
+\begin{theorem}
+	Let $\ul r$ be an expression of length $t$, and suppose $R(\ul r) = \AA_n$.
+	\begin{enumerate}
+		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{t-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r}(\ul b)$.
+		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{t-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r}(\ul b)$.
+	\end{enumerate}
+\end{theorem}
+
+TODO: Add proof.
+
 \section{Constraints in the Alternating Case}
@@
 In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
-\begin{lemma}[Bubble Lemma]
-	Consider a bubble in a full-diagram with base $\AA_n$.  The contents of the bubble are either a barbell or a caterpillar.
-\end{lemma}
-\begin{corollary}[Caterpillar Corollary]
+\begin{theorem}[Bubble Theorem]
+	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar.
+	\label{thm:bubble}
+\end{theorem}
+\begin{theorem}[Caterpillar Theorem]
 	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
-\end{corollary}
+	\label{thm:caterpillar}
+\end{theorem}
 \begin{theorem}[Pasture Theorem]
-	Consider a full-diagram with $N+1$ pastures with base $\AA_n$, numbered $0$, $1$, \dots, $N$, where $N \ge 1$.  Then
+	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
 	\begin{enumerate}[(i)]
-		\ii Pastures $1$ to $N-1$ contain no free components and at most one attached component.
-		\ii Pasture $N$ contains at most one free component, either a caterpillar or a barbell.
+		\ii Pastures $1$ through $N-1$ contain either nothing or a free component.
+		\ii Pasture $N$ contains nothing if $T[N] \neq \AA_n[n]$, and contains a single caterpillar otherwise.
 	\end{enumerate}
+	\label{thm:pasture}
 \end{theorem}
 
-TODO: Work out details of the proofs.
+\subsection{Proof of the Bubble Theorem}
+% We prove theorem \ref{thm:bubble}.
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(5cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 8;
+
+		picture one;
+		draw(one, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
+		draw(one, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), t);
+		draw(one, (0,0)--(0,h/2)..((0+7)/2.0,h*7)..(7,h/2)--(7,0), s);
+		draw(one, (2,0)--(2,h), s);
+		dot(one, (2,h), dot_s);
+		draw(one, (5,0)--(5,h), s);
+		dot(one, (5,h), dot_s);
+
+		picture two;
+		draw(two, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
+		draw(two, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), t);
+		draw(two, (0,0)--(0,h/2)..((0+7)/2.0,h*7)..(7,h/2)--(7,0), s);
+		draw(two, (2,0)--(2,h), s);
+		dot(two, (2,h), dot_s);
+		draw(two, (5,0)--(5,h), s);
+		dot(two, (5,h), dot_s);
+
+		add(one); add(reflect((0,0),(1,0))*two);
+		draw((-1,0)--(8,0));
+	\end{asy}
+	\caption{The bubble theorem is not true for non-alternating sequences.}
+\end{figure}
+Consider a bubble $B$ and assume without loss of generality that it is blue.
+First, we verify that $B$ is nonempty.
+Take any pair of blue anchors on the boundary of $B$.
+Then there must be a red point between these two anchors, and it follows that there exists a component of red color inside the bubble, and hence at least one caterpillar.
+
+Now we verify that there is at most one caterpillar.  Clearly any caterpillars held in the bubble must be red.  Now assume on the contrary that there are at least two caterpillars.
+
+TODO: Finish this.  
+% We claim there exists a blue anchor which is not contained inside any bubble.
+%Consider the portion of the anchorline which is in the on or inside $B$, and view it as a collection of intervals in $\RR$.
+Let us call this set $S \subset \RR$.
+For every red bubble, color red the portion of $S$ which is contained inside it or on the boundary, and call this collection $R \subset S$.
+Two bubbles are connected if the portion of $S$ they mark touches, even at an endpoint\footnote{But the converse is not true}.
+Since there are at least two caterpillars, there must thus be two intervals in $R$, generated by bubbles from different caterpillars, with no red color between them.
+(Otherwise, all the red bubbles are connected and are hence part of a single caterpillar.) Since the endpoints of all intervals in $R$ are red anchors, we obtain a blue anchor that is not contained in any red bubble.
+
+% Because the caterpillars are disjoint and not contained in each other, it is possible to draw a path in the plane such that each caterpillar is on one side of this path.
+
+\subsection{Proof of the Caterpillar Theorem}
+We will now derive the Caterpillar Theorem as a consequence of the Bubble Theorem.
+
+First, a few definitions for this section only.
+\begin{definition*}
+	Consider a caterpillar $C$ in a full-diagram with base $\AA_n$.
+Define the \emph{nesting level} of the caterpillar as the largest integer $n$ for which there exists caterpillars $C = C_0$, $C_1$, $C_2$, $\dots$, $C_n$ such that $C_i$ holds $C_{i+1}$ for each $i=0,1,\dots,n-1$.
+Define the \emph{size} of the caterpillar to be the number of bubbles it contains.
+\end{definition*}
+
+\begin{proof}[Proof of Theorem \ref{thm:caterpillar}]
+	The proof is by double induction.  First we will consider caterpillars with nesting level $0$.
+
+	We perform induction on the size of the caterpillar. 
+	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
+	This is the base step.
+	For the inductive step, consider an arbitrary bubble.
+Inside it is exactly one caterpillar, say $c$, by the Bubble Theorem.
+Because the caterpillar has nesting level $0$, that caterpillar is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
+	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms; one of them is zero because it creates a new empty bubble, and one of them is one of $\left\{ x,y \right\}$ times the same diagram with the cycle cut open and the contents removed.
+The inductive hypothesis now applies directly, and this completes the induction.
+
+	Now suppose a caterpillar has nesting level $k \ge 1$.
+We simply apply the exact same induction on the size as before.
+The only modification is that, instead of a barbell, we have a caterpillar with nesting level strictly less than $k$.
+However, these caterpillars all evaluate as a polynomial again of the form $x^my^n \alpha_s$ or $x^my^n\alpha_t$, by the outer inductive hypothesis.
+So applying equation \eqref{eq:barbell_break} in the same manner completes this induction as well.
+\end{proof}
+
+\subsection{Proof of the Pasture Theorem}
+TODO
 
 \section{A Recursion for the Alternating Case}
+In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM(\ul a, \ul b)$.
+
+TODO: Write this section.
 

### 2013-07-22 paper.tex
Implemented a bunch of Tanya's suggestions.

@@
 
-Given a sequence of consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libednisky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.
+Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libednisky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.
 Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.
@@
 
-\subsection{An Extended Introduction}
+\subsection{An Extended Background}
 \label{sec:prelim}
@@
 Let $R^s$ be the subring of $R$ which is invariant under $s$.  Define $R^t$ similarly.  Then a \emph{Bott-Samelson bimodule} is a bimodule of the form
-\[ R \otimes_{R^{i_1}} R \otimes_{R^{i_2}} R \otimes_{R^{i_3}} \dots \otimes_{R^{i_n}} R \]
-where each $R^i$ is either $R^s$ or $R^t$.   Elements of such a bimodule will be written in the form $f_0 \mid f_1 \mid \dots \mid f_n$, where $f_i \in R$.
+\[ R \otimes_{R^{i_1}} R \otimes_{R^{i_2}} R \otimes_{R^{i_3}} \dots \otimes_{R^{i_n}} R, \]
+where each $i_j$ is either $s$ or $t$.   Elements of such a bimodule will be written in the form $f_0 \mid f_1 \mid \dots \mid f_n$, where $f_i \in R$.
 
@@
 
-The elements of $\DD$ by simply adding corresponding coefficients.
-Multiplication is defined as follows: the product of two diagrams is the composition of the diagrams if the labels coincide, and is $0$ otherwise.
+An example of such a diagram is shown in figure \ref{fig:example_diagram}.
 
-In \cite{basispf}, Khovanova and Elias show that all such maps can be expressed as a linear combination of these diagrams.
+The elements of $\DD$ can be added by simply adding corresponding coefficients.
+Multiplication is defined as follows: the product of two diagrams is the composition of the diagrams if the labels on the bottom of the first coincide with those on the top of the second.
+Otherwise, the product is $0$.
+
+In \cite{basispf}, Khovanov and Elias show that all such maps can be expressed as a linear combination of these diagrams.
 
@@
 
-With this, we can now describe the ``primitive'' maps for blue lines in table \ref{tab:prim_maps}.  The corresponding equations hold for red in $t$.
+With this, we can now describe the ``primitive'' maps for blue lines in Table~\ref{tab:prim_maps}.  The corresponding equations hold for red in $t$.
 
@@
 
-Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any any binary string $\ul b$ of length $n$, we can construct a diagram based on a series of rules.
+Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any binary string $\ul b$ of length $n$, we can construct a diagram based on a series of rules.
 
@@
 \label{sec:prelim_probstate}
-Recall that maps are multiplied by simply placing them on top of each other.  The operations are then applied to simplify the product.
+Recall that maps are multiplied by simply placing them on top of each other.  The operations are then applied to simplify the product.  An example is shown in figure \ref{fig:example_compose}.
 
@@
 	\caption{An example of composing two maps, 1001100 and 1001001.}
+	\label{fig:example_compose}
 \end{figure}
@@
 \]
-Similarly, let $\AA_n'$ denote $AA_n$, except with the roles of $s$ and $t$ switched.  Note that $\AA_0 = \AA_0' = \varnothing$.
+Similarly, let $\AA_n'$ denote $\AA_n$, except with the roles of $s$ and $t$ switched.  Note that $\AA_0 = \AA_0' = \varnothing$.
 
@@
 Furthermore, the line on which the anchors lie will be called the \emph{anchorline}.
+
+An example of a full-map with base $\AA_5$ is given in figure \ref{fig:example_full_map}.
 
@@
 	\caption{A full-map with base $ststs$, hence with five anchors.  The top is $\varnothing$.}
+	\label{fig:example_full_map}
 \end{figure}
@@
 	\caption{Two blue barbells with a very twisted fence, which creates two pastures.}
+	\label{fig:def_barbell_fence}
 \end{figure}
@@
 \end{definition*}
-Notice that, by homotopy, every blue barbell is simply $\barbell{barbell_blue}$, which evaluates as $\alpha_s$.  Similarly, every red barbell is simply $\barbell{barbell_red} = \alpha_t$.
+Notice that, by homotopy, every blue barbell is simply $\barbell{barbell_blue}$, which we will see later evaluates as $\alpha_s$.
+Similarly, every red barbell is simply $\barbell{barbell_red} = \alpha_t$.
 
@@
 \end{definition*}
+An example of a fence complete with two barbells is given in figure \ref{fig:def_barbell_fence}.
+
+Next, we name some recurrent characters in our work.
 
@@
 	\caption{A blue bubble with two barbells inside it.}
+	\label{fig:def_bubble}
 \end{figure}
@@
 \end{definition*}
+
+An example of a bubble is given in figure~\ref{fig:def_bubble}.
 
@@
 	\caption{A caterpillar made of three bubbles}
+	\label{fig:def_caterpillar}
 \end{figure}
@@
 \end{definition*}
-\begin{remark*}
-	Notice that any barbell or bubble is a special case of a caterpillar.
-\end{remark*}
+An example of a caterpillar is given in figure~\ref{fig:def_caterpillar}.  Notice that any barbell or bubble is a special case of a caterpillar.
 
@@
 		\begin{cases}
-			0 & \text{if } \exists 1 \le i \le n-1: \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
+			0 & \text{if }\ \exists 1 \le i \le n-1:\ \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
 			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
@@
 	\caption{A half-map with base $\SS_8$.}
+	\label{fig:pf_trivial_theorem_example}
 \end{figure}
@@
 	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.
+See figure \ref{fig:pf_trivial_theorem_example} for a example of such a map.
 
@@
 \section{Counting Maps}
-TODO: Write up / prove the formula for number of maps from $A$ to $B$.
-
 For each expression $\ul T$ and $\ul r$, we give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r}(\ul b) = \ul T$.
@@
 \begin{theorem}
-	Let $\ul r$ be an expression of length $t$, and suppose $R(\ul r) = \AA_n$.
+	Let $\ul r$ be an expression of length $\ell$, and suppose $R(\ul r) = \AA_n$.
 	\begin{enumerate}
-		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{t-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r}(\ul b)$.
-		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{t-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r}(\ul b)$.
+		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r}(\ul b)$.
+		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r}(\ul b)$.
 	\end{enumerate}
 \end{theorem}
-
-TODO: Add proof.
 
@@
 \subsection{Proof of the Bubble Theorem}
-% We prove theorem \ref{thm:bubble}.
 
-\begin{figure}[ht]
-	\centering
-	\begin{asy}
-		size(5cm);
-		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
-		int n = 8;
-
-		picture one;
-		draw(one, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
-		draw(one, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), t);
-		draw(one, (0,0)--(0,h/2)..((0+7)/2.0,h*7)..(7,h/2)--(7,0), s);
-		draw(one, (2,0)--(2,h), s);
-		dot(one, (2,h), dot_s);
-		draw(one, (5,0)--(5,h), s);
-		dot(one, (5,h), dot_s);
-
-		picture two;
-		draw(two, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
-		draw(two, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), t);
-		draw(two, (0,0)--(0,h/2)..((0+7)/2.0,h*7)..(7,h/2)--(7,0), s);
-		draw(two, (2,0)--(2,h), s);
-		dot(two, (2,h), dot_s);
-		draw(two, (5,0)--(5,h), s);
-		dot(two, (5,h), dot_s);
-
-		add(one); add(reflect((0,0),(1,0))*two);
-		draw((-1,0)--(8,0));
-	\end{asy}
-	\caption{The bubble theorem is not true for non-alternating sequences.}
-\end{figure}
 Consider a bubble $B$ and assume without loss of generality that it is blue.
@@
 TODO: Finish this.
-% We claim there exists a blue anchor which is not contained inside any bubble.
-%Consider the portion of the anchorline which is in the on or inside $B$, and view it as a collection of intervals in $\RR$.
-Let us call this set $S \subset \RR$.
-For every red bubble, color red the portion of $S$ which is contained inside it or on the boundary, and call this collection $R \subset S$.
-Two bubbles are connected if the portion of $S$ they mark touches, even at an endpoint\footnote{But the converse is not true}.
-Since there are at least two caterpillars, there must thus be two intervals in $R$, generated by bubbles from different caterpillars, with no red color between them.
-(Otherwise, all the red bubbles are connected and are hence part of a single caterpillar.) Since the endpoints of all intervals in $R$ are red anchors, we obtain a blue anchor that is not contained in any red bubble.
-
-% Because the caterpillars are disjoint and not contained in each other, it is possible to draw a path in the plane such that each caterpillar is on one side of this path.
 
@@
 Inside it is exactly one caterpillar, say $c$, by the Bubble Theorem.
-Because the caterpillar has nesting level $0$, that caterpillar is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
-	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms; one of them is zero because it creates a new empty bubble, and one of them is one of $\left\{ x,y \right\}$ times the same diagram with the cycle cut open and the contents removed.
-The inductive hypothesis now applies directly, and this completes the induction.
+Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
+	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms.
+One of them is zero because it creates a new empty bubble.
+The other the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.
+The inductive hypothesis now applies directly, and this completes the first induction.
 
 	Now suppose a caterpillar has nesting level $k \ge 1$.
-We simply apply the exact same induction on the size as before.
+We simply apply the exact same induction on size as before.
 The only modification is that, instead of a barbell, we have a caterpillar with nesting level strictly less than $k$.

### 2013-07-23 paper.tex
how do you sleep with the light on like that

@@
 \section{Counting Maps}
-For each expression $\ul T$ and $\ul r$, we give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r}(\ul b) = \ul T$.
-One can check that, by construction, $\Top(\ul b)$ is always a reduced expression.
+We give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r} \ul b = \ul T$ for each expression $\ul T$ and $\ul r$.
+One can check that, by construction, $\Top \ul b$ is always a reduced expression.
 
@@
 	\begin{enumerate}
-		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r}(\ul b)$.
-		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r}(\ul b)$.
+		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r} \ul b$.
+		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r} \ul b$.
 	\end{enumerate}
+	\label{thm:count_maps}
 \end{theorem}
+Of course, if $\ul r$ begins with the character $t$, then one can simply reverse the roles of $s$ and $t$ in the above theorem to obtain an analogous formula.
+
+The main idea of the proof is to reduce the problem to the case when $\ell = n$, and then apply induction on $n$.  We fill in the details below.
+
+\begin{proof}[Proof of Theorem \ref{thm:count_maps}]
+	First we will resolve the case where $\ul r = \AA_n$.  This follows basically immediately by induction on $n$.  
+\end{proof}
 
@@
 \section{A Recursion for the Alternating Case}
-In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM(\ul a, \ul b)$.
-
-TODO: Write this section.
+In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
 
@@
 \section{Acknowledgments} 
-I offer my sincerest gratitude\footnote{That sounded horribly fake, but really, I mean it.
-You guys are the best.
-Thank you for a great project.} to my mentor Mr.
-Francisco Unda for daily mentorship, and Dr.
-Benjamin Elias for providing the project and for often meeting with me personally to discuss it.
-I further wish to thank the MIT Math Department, and in particular the head mentor Dr.
-Tanya Khovanova, for organizing the Math RSI, providing individual discussion with each student outside of the mentorship, as well as organizing additional meetings and lectures.
+I offer my sincerest gratitude to my mentor Mr. Francisco Unda for daily mentorship, and Dr. Benjamin Elias for providing the project and for often meeting with me personally to discuss it.
+That sounded horribly fake, but really, I mean it.  You guys are the best.  Thank you for a great project.
+
+I further wish to thank the MIT Math Department, and in particular the head mentor Dr. Tanya Khovanova, for organizing the Math RSI and providing individual discussion with me.
 I also wish to thank my tutor Mr. Antoni Rangachev for his invaluable advice in preparing both this paper and my final presentation.

### 2013-07-23 paper.tex
proved bubble thm

@@
 
-Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libednisky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.
+Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.
 Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.
@@
 \begin{theorem}[Bubble Theorem]
-	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar.
+	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
 	\label{thm:bubble}
@@
 \subsection{Proof of the Bubble Theorem}
+We begin with a proof of the bubble theorem, which is the crux result of the alternating case.  Indeed, both of the subsequent theorems are fairly straightforward consequences of this theorem.
 
-Consider a bubble $B$ and assume without loss of generality that it is blue.
-First, we verify that $B$ is nonempty.
-Take any pair of blue anchors on the boundary of $B$.
-Then there must be a red point between these two anchors, and it follows that there exists a component of red color inside the bubble, and hence at least one caterpillar.
+It's interesting to note that the Bubble Theorem is intuitively very natural.  The main difficulty is finding a clean way to handle the special cases generated by the convoluted geometry.
 
-Now we verify that there is at most one caterpillar.  Clearly any caterpillars held in the bubble must be red.  Now assume on the contrary that there are at least two caterpillars.
+\begin{proof}[Proof of Theorem \ref{thm:bubble}]
+	Take a bubble $B$ and assume without loss of generality that it is blue.
+It is easy to see, by considering two anchors on the boundary of blue, that there is some red anchor inside $B$.
+This implies that $B$ has at least one red caterpillar.
 
-TODO: Finish this.
+	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.
+Then let $S$ be the set of anchors contained on the boundary of any caterpillars held inside $B$ (in a sense, on the ``outermost'' level).
+
+	Define a pair of red anchors $u, v \in S$ to be \emph{quasi-connected} if one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect any boundaries of $B$, and furthermore, there is no other pair of red anchors both between $u$ and $v$, inclusive, with this property.
+
+	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a single arc}.
+To prove this, take such a quasi-connected pair $u$ and $v$.
+Now we'll focus only on the half-map in which the prescribed arc is drawn.
+We thus may state that an arc \emph{shields} any anchors between its endpoints.
+
+	\begin{figure}[ht]
+		\centering
+		\begin{asy}
+			size(6cm);
+			pen s = blue, t = red + dashed + 0.6;
+			pen dot_s = blue, dot_t = red;
+			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
+			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
+			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
+			draw((1,0)..(3,2)..(5,0), t); // red covering arc
+			draw((2,0)..(3,1)..(4,0), s); // blue covering arc again
+			label("$u$", (3,0), dir(-90));
+			label("$v$", (5,0), dir(-90));
+		\end{asy}
+		\hspace{2em}
+		\begin{asy}
+			size(6cm);
+			pen s = blue, t = red + dashed + 0.6;
+			pen dot_s = blue, dot_t = red;
+			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
+			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
+			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
+			draw((1,0)..(4,2)..(7,0), t); // red covering arc
+			draw((2,0)..(4,1)..(6,0), s); // blue covering arc
+			label("$u$", (3,0), dir(-90));
+			label("$v$", (5,0), dir(-90));
+		\end{asy}
+		\caption{Proving the bubble theorem with quasi-connected vertices.}
+		\label{fig:pf_bubble}
+	\end{figure}
+	Because the string is alternating, there exists a blue anchor between $u$ and $v$, say $x$.
+Furthermore, there must be some blue arc (of $B$) shielding $u$ and $v$.
+By the light-leave construction, there must be some red arc $A$ covering $x$.
+If this arc joins $u$ and $v$, then we are done.
+Otherwise, it must completely cover either $u$ or $v$ (by quasi-connectedness).
+Now we have two cases,
+	\begin{itemize}
+		\ii If the arc covers exactly one of $u$ or $v$, say $u$, then there must be a blue arc shielding $u$ from $A$.
+But then this contradicts the quasi-connectedness, because now it is not possible to join $u$ and $v$ by an arc on this half-map.
+This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
+		\ii If the arc covers both $u$ and $v$, then there must be a blue arc which shields both $u$ and $v$, which is itself shielded by $A$.
+Then we can repeat the same procedure with this new blue arc.
+This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
+	\end{itemize}
+	Therefore any pair of quasi-connected anchors must be connected by an arc.
+However, it is evident that this implies there is a path of arcs joining any pair of red anchors.
+Therefore all red anchors in $S$ must be connected.
+So there is a single caterpillar, as desired.
+\end{proof}
 
@@
 \subsection{Proof of the Pasture Theorem}
-TODO
 

### 2013-07-24 appa.tex
Meeting Tanya in 20 minutes oops.
Before meeting Ben.

@@
 % the percent sign from the beginning of the next line.
-%\endinput
+\endinput
 
@@
 
-\section{Title of Appendix}
-
-Appendices may appear after the paper proper.  Appendices may hold
-extra information that would interrupt the flow of the paper and that
-is not absolutely necessary for the reader to appreciate the work.
-For example, a large number of related figures or a mathematical
-derivation could go nicely in an appendix.
+\section{Casework for Theorem \ref{thm:count_maps}}
+\label{appa:count_maps}
+Compute like hell.

### 2013-07-24 paper.tex
Before meeting Ben.

@@
 \section{Preliminaries and Definitions}
-NOTE: If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.
+\textbf{Note:} If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.
 
@@
 		\]
+	\label{prop:s_top}
 \end{proposition}
@@
 		\begin{cases}
-			1 & \text{if } b[1] + b[2] + \dots + b[i] \equiv 1 \pmod{2} \\
+			1 & \text{if } \ul b[1] + \ul b[2] + \dots + \ul b[i] \equiv 1 \pmod{2} \\
 			0 & \text{otherwise}
@@
 	\]
+	\label{thm:s_eval}
 \end{theorem}
@@
 
-	Number the anchors $1$, $2$, $\dots$ from left to right.
+	Number the anchors $1$, $2$, \dots from left to right.
 
-	For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.  Note that the antennae always form a single contiguous sequence of anchors.
+	For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.
+Note that the antennae of a component always form a single contiguous sequence of anchors.
 
-	Now, we observe that for each $1 \le i \le n-1$, we have that $\ul a^\ast[i] = 1$ if and only if $i$ and $i+1$ are both antennae of some component.
+	The key observation is that for $1 \le i \le n-1$, we have that $\ul b^\ast[i] = 1$ if and only if $i$ and $i+1$ are both antennae of some component in $\MM(\ul b)$.  This follows by construction.
 
@@
 \begin{definition*}
-	Let $R(\ul r)$ denote the $\ul r$ with any consecutive blocks of $s$'s replaced by a single $s$, and similarly for $t$.
+	Let $R(\ul r)$ denote $\ul r$ with any consecutive blocks of $s$'s replaced by a single $s$, and similarly for $t$.
 \end{definition*}
@@
 	Let $\ul r$ be an expression of length $\ell$, and suppose $R(\ul r) = \AA_n$.
-	\begin{enumerate}
+	\begin{enumerate}[(i)]
 		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r} \ul b$.
@@
 \begin{proof}[Proof of Theorem \ref{thm:count_maps}]
-	First we will resolve the case where $\ul r = \AA_n$.  This follows basically immediately by induction on $n$.  
+	First we will resolve the case where $\ul r = \AA_n$, so that $\ell = n$ and $2^{\ell-n} = 1$.
+This follows by induction on $n$.
+The main idea is that, for the binary strings of length $n$, we consider those that end with $1$ and those that end with $0$.
+Those that end with a $0$ have the same top when the trailing $0$ is deleted, whilst those with end bit $1$ have a top which differs by one character if the trailing $1$ is deleted.
+We simply check that in all eight cases, the binomial coefficients add up to give the new binomial coefficients (via Pascal's identity).
+The computation is left to a reader.
+
+	To complete the theorem, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there a $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
+(This follows from Proposition \ref{prop:s_top}.)  This reduces to the previous case $\ul r = \AA_n$, but with some extra factors of $2$; aggregating all of them yields the factor of $2^{\ell-n}$, as desired.
 \end{proof}
@@
 		\ii Pastures $1$ through $N-1$ contain either nothing or a free component.
-		\ii Pasture $N$ contains nothing if $T[N] \neq \AA_n[n]$, and contains a single caterpillar otherwise.
+		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.
 	\end{enumerate}
@@
 	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.
-Then let $S$ be the set of anchors contained on the boundary of any caterpillars held inside $B$ (in a sense, on the ``outermost'' level).
 
-	Define a pair of red anchors $u, v \in S$ to be \emph{quasi-connected} if one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect any boundaries of $B$, and furthermore, there is no other pair of red anchors both between $u$ and $v$, inclusive, with this property.
+	Define a pair of red anchors $u, v$, with $u$ to the left of $v$, to be \emph{quasi-connected} if (i) one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect blue lines, and (ii) there is no red anchor $w$ strictly between $u$ and $v$ for which one can draw a similar arc on the same half-map joining $w$ and $v$.
 
@@
 Now we'll focus only on the half-map in which the prescribed arc is drawn.
-We thus may state that an arc \emph{shields} any anchors between its endpoints.
+We thus may state that an arc \emph{shields} any anchors which lie between its endpoints.
 
@@
 	\end{figure}
-	Because the string is alternating, there exists a blue anchor between $u$ and $v$, say $x$.
-Furthermore, there must be some blue arc (of $B$) shielding $u$ and $v$.
+	Because the string is alternating, we can take a blue anchor $x$ immediately to the left of $v$.
+Now, there must be some blue arc shielding $u$ and $v$ (since $u,v$ are inside a blue bubble).
 By the light-leave construction, there must be some red arc $A$ covering $x$.
 If this arc joins $u$ and $v$, then we are done.
-Otherwise, it must completely cover either $u$ or $v$ (by quasi-connectedness).
-Now we have two cases,
+	Otherwise, if it has endpoint $v$ then it must completely cover $u$ by condition (ii) of quasi-connectedness; if not, then it must completely cover $v$.  This leads us to two cases.
 	\begin{itemize}
@@
 Then we can repeat the same procedure with this new blue arc.
-This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
+This case is illustrated by the right half of figure \ref{fig:pf_bubble}.
 	\end{itemize}
 	Therefore any pair of quasi-connected anchors must be connected by an arc.
-However, it is evident that this implies there is a path of arcs joining any pair of red anchors.
-Therefore all red anchors in $S$ must be connected.
+However, one can verify that the red anchors in $B$ but not in any other blue bubble are ``connected'' under quasi-connectedness.\footnote{That is, one can follow a sequence of red anchors, each consecutive pair quasi-connected, from any red anchor to any other red anchor.}  Therefore all such red anchors must be connected.
 So there is a single caterpillar, as desired.
@@
 One of them is zero because it creates a new empty bubble.
-The other the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.
+The other is the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.
 The inductive hypothesis now applies directly, and this completes the first induction.
@@
 \subsection{Proof of the Pasture Theorem}
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(11cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 6;
+
+		picture before;
+		draw(before, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
+		draw(before, (2,0)--(2,h), s);
+		dot(before, (2,h), dot_s);
+		draw(before, (5,0)--(5,h), t);
+		dot(before, (5,h), dot_t);
+		draw(before,(0,0)--(0,3*h), s);
+		draw(before,(3,0)--(3,3*h), t);
+		draw(before,(4,0)--(4,3*h), s);
+		dot(before, (3, h/2), dot_t);
+
+		add(before); add(reflect((0,0),(1,0))*before);
+		draw((-1,0)--(6,0));
+
+		picture after;
+		draw(after, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
+		draw(after, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), s);
+		draw(after, (3,0)--(3,h/2)..((3+7)/2.0,h*4)..(7,h/2)--(7,0), t);
+		draw(after, (0,0)--(0,h/2)..((0+8)/2.0,h*5.5)..(8,h/2)--(8,0), s);
+		draw(after, (2,0)--(2,h), s);
+		dot(after, (2,h), dot_s);
+		draw(after, (5,0)--(5,h), t);
+		dot(after, (5,h), dot_t);
+		dot(after, (3, h/2), dot_t);
+
+		add(shift((9,0)) * after);
+		add(shift((9,0)) * reflect((0,0),(1,0))*after);
+		draw((8,0)--(18,0));
+
+		label("$\to$", (7,0));
+	\end{asy}
+	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Theorem from the Bubble Theorem.}
+	\label{fig:pf_pasture}
+\end{figure}
+The bubble theorem and the pasture theorem are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Theorem follows from the Bubble Theorem.
+\begin{proof}[Proof of Theorem \ref{thm:pasture}]
+	Again, let $T$ denote the top, with length $N$.
+In the first case, suppose $T[N] \neq \AA_n[n]$; that is, the last characters of $T$ and $\AA_n$ differ.
+Then it must be the case that the rightmost anchor is not part of a fence.
+	Now suppose the map arose from $\MM_{\AA_n}(\ul a, \ul b)$.
+Let $\ul a'$ be the string formed by appending $N$ $1$'s to $\ul a$, and define $\ul b'$ similarly.
+Now consider the map \[ \MM_{\AA_{n+N}} \left( \ul a', \ul b' \right).
+\]  See figure \ref{fig:pf_pasture} for an example.
+
+	It is easy to verify that the top of this new map is zero.
+Now what we have done is enclose the contents of each pasture into bubbles.
+The Bubble Theorem tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.
+This implies the Pasture Theorem in the first case.
+
+	The case where $T[N] = \AA_n[n]$ is similar.
+We simply append a zero followed by $N$ $1$'s and repeat the same procedure.
+The only difference is that the innermost barbell was generated by the $0$ we appended, and thus was not part of the original diagram.
+\end{proof}
 
@@
 In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
+TODO: Write this.
 

### 2013-07-25 abstract.tex
blargh

@@
 
-The abstract should be a brief summary of your results that grabs the
-reader's attention.  It is the first thing the reader will see, and you
-must convince the reader that the rest of your paper is worthwhile.  In
-the best of all possible worlds, \LaTeX\ will take care of all the
-formatting for you.  Let $v = (v_0, v_1, \ldots, v_n)$.  If your
-abstract contains nothing but words, no one would know that you're using
-\LaTeX!
+This paper considers left/right action-preserving morphisms between Bott-Samelson bimodules from a combinatorial perspective; specifically, using a diagrammatic representation.
+We examine the maps formed by a basis known as Libedinsky's light leaves, which constructs a map based on a sequence of letters $\underline r$ (composed of $s$ and $t$) and a binary string $\underline b$.
+The eventual goal is to find a formula for the composition of two such maps based on their binary strings $\underline b$.
+The paper provides a complete formula for the case $\underline r = sss\dots$, and shows that the possible structures of maps when $\underline r = ststs\dots$ are extremely limited.
+We additionally provide a formula for the number of maps between two arbitrary Bott-Samelson bimodules.

### 2013-07-25 paper.tex
Fixed a very embarrassing typo.
blargh

@@
 \section{Introduction}
+\textbf{Note:} If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.
+
 We study a class of maps between Bott-Samelson bimodules.
@@
 The maps are composed by juxtaposition.
+
+TODO: Expand on history, motivation, importance, etc. (meeting Ben on Monday)
 
@@
 
-Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:prelim_probstate}.
-
-TODO: Add road map once I figure out what results I actually have
+Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:probstate}.
+The results begin by solving the special case of one color completely in section \ref{sec:res_onecolor}.
+In section \ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.
+The most interesting results are in sections \ref{sec:res_altcase} and \ref{sec:res_altrecurse}, where we investigate the case where the given string is $ststst\cdots$.
+In particular, we show that the possible resulting structures is extremely limited, and provide a recursion based on these restrictions for special cases.
 
 \section{Preliminaries and Definitions}
-\textbf{Note:} If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.
+\label{sec:prelim}
+In section \ref{sec:prelim_background}, we provide the background behind the Bott-Samelson bimodules, and the correspondence between these maps and certain diagrams.
+We then introduce Libedinsky's light leaves, a basis by which maps can be constructed using binary strings.
 
+In section \ref{sec:prelim_def_notation}, we introduce several definitions which we use throughout the paper.
+Next, in section \ref{sec:prelim_explain_poly_eval}, we describe how these maps can be represent as polynomials.
+The actual problem statement is then deferred to \ref{sec:probstate}.
 \subsection{An Extended Background}
-\label{sec:prelim}
+\label{sec:prelim_background}
 % \subsection{Coxeter Rings, and the Bott-Samelson Bimodules}
-Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be unit vectors normal to these planes.
+Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be arbitrary vectors normal to these planes.
 We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.
-If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a.
-\]  In particular, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.
-Furthermore, we see that there exist fixed constants $x$ and $y$ such that
+In other words, $W$ is the infinite dihedral group with the presentation \[ W = \left<s,t \mid s^2=t^2=1\right>.
+\] If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected over a hyperplane normal to any $a \in V$ via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a.
+\]
+In particular, if $W$ acts on $V$ by this reflection, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.
+Furthermore, using the above, we see that there exist fixed constants $x$ and $y$ such that
 \begin{align*}
@@
 \end{align*}
+Explicitly, $x = \frac{-2(\alpha_s,\alpha_t)}{(\alpha_s, \alpha_s)}$ and $y = \frac{-2(\alpha_t,\alpha_s)}{(\alpha_t,\alpha_t)}$.
+Note that $x=y$ if $\left\lvert \alpha_s \right\rvert = \left\lvert \alpha_t \right\rvert$.
+
 Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.
@@
 \begin{equation}
-	\sigma(rx) = r\sigma(x) \quad\text{and}\quad \sigma(xr) = \sigma(x)r \quad\text{for every $r \in R$ and $x \in \text{Dom } \sigma$}.
+	\sigma(rx) = r\sigma(x) \quad\text{and}\quad \sigma(xr) = \sigma(x)r \quad\text{for every $r \in R$ and $x \in \text{Domain } \sigma$}.
 	\label{eq:respect}
@@
 \newcommand{\DD}{\mathcal D}
-Certain maps between Bott-Samleson bimodules can be described in terms of diagrams.
+Certain maps between Bott-Samelson bimodules can be described in terms of diagrams.
 We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.
@@
 The maps are conventionally read from bottom to top.
-The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take.
-For example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.
+The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take -- for example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.
 An unlabelled domain corresponds to $R$.
@@
 \begin{definition*}
-	The \emph{Demazure operator} $\partial_s$ is given by $f \mapsto \frac{f - sf}{\alpha_s}$.
+	The \emph{Demazure operator} $\partial_s: R \to R$ is given by $\partial_s(f) = \frac{f - sf}{\alpha_s}$.
 \end{definition*}
 
-With this, we can now describe the ``primitive'' maps for blue lines in Table~\ref{tab:prim_maps}.  The corresponding equations hold for red in $t$.
+With this, we can now describe the meanings of each type of vertex (for blue lines) in Table~\ref{tab:prim_maps}.  The corresponding equations hold for red in $t$.
 
@@
 		\barbell{half_top} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
-		\barbell{half_bot} & R \to R \ttimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
+		\barbell{half_bot} & R \to R \stimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
 		\barbell{tri_down} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
@@
 
-Henceforth we will make the convenient abbreviation of $\barbell{tri_up_contract_before}$ as $\barbell{tri_up_contract_after}$.
+Henceforth, we will make the convenient abbreviation of $\barbell{tri_up_contract_before}$ as $\barbell{tri_up_contract_after}$.
 It will also be understood that edges need not be straight lines, but any topologically equivalent deformation shall represent the same graph.
@@
 \end{itemize}
-Finally, join any bits which are up at the end of the process to the opposite end.  An example of such a light leaf is shown in figure \ref{fig:lightleaf_example}.
+Finally, join any bits which are up at the end of the process to the opposite end.
+A map which arises in such a manner is called a \emph{light leaf}.
+An example of such a light leaf is shown in figure \ref{fig:lightleaf_example}.
 
-These light leaves are interesting because, in the seventh chapter of \cite{span}, it is shown that these light leaves for a ``basis'' in the sense that all maps may be expressed using those generated by light leaves (modulo lower terms).
+These light leaves are interesting because, in the seventh chapter of \cite{span}, it is shown that these light leaves form a ``basis'' in the sense that all maps may be expressed by compositions of these light leaves.
 
-\subsubsection{Problem Statement}
-\label{sec:prelim_probstate}
-Recall that maps are multiplied by simply placing them on top of each other.  The operations are then applied to simplify the product.  An example is shown in figure \ref{fig:example_compose}.
+\subsection{Definitions and Notations}
+\label{sec:prelim_def_notation}
+\subsubsection{Notations for Strings}
+For each positive integer $n$, let us define for convenience the strings
+\[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
+and the ``alternating'' string
+\[
+	\AA_n \defeq
+	\begin{cases}
+		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
+		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
+	\end{cases}.
+\]
+Similarly, let $\AA_n'$ denote $\AA_n$, except with the roles of $s$ and $t$ switched.  Note that $\AA_0 = \AA_0' = \varnothing$.
+
+In general, a string of $s$'s and $t$'s will be referred to as an \emph{expression}.
+In the case where there are no consecutive identical characters (e.g.
+$\AA_n$), we will refer to them as \emph{reduced expressions}.
+
+Next, let $\BB_n$ denote the set of binary strings of length $n$.
+
+Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.
+
+\subsubsection{Definitions for Maps and Diagram}
+Consider a string $\ul r$ of letters $s$ and $t$.
+Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangably) formed by the light leaves.
+We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.
+Additionally, let $\Top_{\ul r} \ul b$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.
 
@@
 	\end{asy}
-	\caption{An example of composing two maps, 1001100 and 1001001.}
+	\caption{An example of composing two maps, $\MM_{sttstst}(1001100)$ and $\MM_{sttstst}(1001001)$.}
 	\label{fig:example_compose}
@@
 
-\begin{definition*}
-	A map is \emph{idempotent} if multiplying it with itself returns the original graph.
-\end{definition*}
-Colloquially, $m^2=m$ if and only if $m$ is idempotent.
+Two maps $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ with identical tops may be composed by juxtaposing $\MM_{\ul r}(\ul a)$ with a flipped copy of $\MM_{\ul r}(\ul b)$; an example of such a composition is given in Figure~\ref{fig:example_compose}.
+We will denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
+% Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.
 
-Fix an $\ul r$.
-If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.
-This motivates us to construct potential idempotents by taking two light leaves whose top sequences are identical, and composing $A$ upside-down with $B$.
-If $AB=1$, then this will yield an idempotent.
-
-This motivates the main objective of study.
-\begin{ques*}
-	For a fixed $\ul r$ and two binary sequences $\ul a$ and $\ul b$ with the same top, can one determine their product based on $\ul a$ and $\ul b$?
-\end{ques*}
-
-Further details on the evaluation of these maps are detailed in section \ref{sec:prelim_explain_poly_eval}, but before that we need to introduce certain definitions for clarity.
-
-% In this question, we will consider only maps with the same top, and we will also work \emph{modulo lower terms}.
-This means that any map which has a component that touches either the top or bottom boundary exactly once will be treated as zero.
-In that case, using the operations described in section \ref{sec:prelim_genrel}, we can reduce every map to simply multiplying by a polynomial on the left.
-The goal is to then compute these polynomials using some combinatorial formula.
-
-\subsection{Definitions and Notations}
-\subsubsection{Notations for Strings}
-For each positive integer $n$, let us define for convenience the strings
-\[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
-and the ``alternating'' string
-\[
-	\AA_n \defeq
-	\begin{cases}
-		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
-		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
-	\end{cases}.
-\]
-Similarly, let $\AA_n'$ denote $\AA_n$, except with the roles of $s$ and $t$ switched.  Note that $\AA_0 = \AA_0' = \varnothing$.
-
-In general, a string of $s$'s and $t$'s will be referred to as an \emph{expression}.
-In the case where there are no consecutive identical characters (e.g.
-$\AA_n$), we will refer to them as \emph{reduced expressions}.
-
-Next, let $\BB_n$ denote the set of binary strings of length $n$.
-
-Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.
-
-\subsubsection{Definitions for Maps and Diagram}
-Consider a string $\ul r$ of letters $s$ and $t$.  Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the appropriate map (or its associated diagram;
-we will refer to maps and their associated diagrams interchangably) formed by a single application of the light leaves.
-We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.
-Additionally, let $\Top_{\ul r} \ul b$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.
-
-Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.
 Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.
@@
 One can verify that, using the barbell-forcing rules, we can recursively move all barbells to the left, and any ``broken'' walls are reduced to zero, or are contracted.
-Hence, any full-diagram can be reduced to linear combinations of maps of the form $x \mapsto \alpha_s^m \alpha_t^n x$.
+Hence, any full-diagram can be reduced to linear combinations of maps of the form $f \mapsto \alpha_s^m \alpha_t^n f$.
 In other words, every full diagram can be represented as a polynomial in $\RR[x,y][\alpha_s,\alpha_t]$.
@@
 
-The problem statement then becomes to compute the polynomial $\MM_{\ul r}(\ul a, \ul b)$ with a formula in terms of $\ul r$, $\ul a$, $\ul b$.
+\subsection{Quantum Numbers}
+A particularly nice sequence of polynomials involved can be defined recursively.  They are termed \emph{two-color quantum numbers}.
+\begin{definition*}[Quantum Numbers]
+	For each integer $n \ge 0$, define two polynomials $[n]_x, [n]_y \in \ZZ[x,y]$ recursively by $[0]_x = [0]_y = 0$, $[1]_x = [1]_y = 1$, $[2]_x = x$, $[2]_y = 2$, and
+	\begin{align*}
+		[2]_x[n]_y = [n+1]_x - [n-1]_x \\
+		[2]_y[n]_x = [n+1]_y - [n-1]_y
+	\end{align*}
+	Finally, $[-n]_x = -[n]_x$ and $[-n]_y = -[n]_y$ for each $n \ge 0$.
+\end{definition*}
+The quantities $[n]_x$ and $[n]_y$ are closely related.  In particular, $[2k+1]_x = [2k+1]_y$ and $[2]_x[2k]_y = [2]_y[2k]_x$ for all integers $k$.
+
+The quantum numbers are relevant to the problem because of the identity
+\begin{equation}
+	s([n]_x\alpha_s + [n-1]_y\alpha_t) = [n]_x\alpha_s + [n+1]_y\alpha_t
+	\label{eq:quantum}
+\end{equation}
+and its analogous form for $t$.
+One can verify \eqref{eq:quantum} immediately follows from definitions.
+This allows us to recursively compute the polynomial which results from pushing a barbell through multiple alternating fences.
+For example, $ststst(\alpha_s) = ststst([1]_x\alpha_s + [0]_y\alpha_t) = [7]_x\alpha_s + [6]_y\alpha_t$.
+
+\section{Problem Statement}
+\label{sec:probstate}
+
+The motivation for this problem arises from the following definition.
+\begin{definition*}
+	A map is \emph{idempotent} if multiplying it with itself returns the original graph.
+\end{definition*}
+Colloquially, $m^2=m$ if and only if $m$ is idempotent.
+
+Fix an $\ul r$.
+If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.
+This motivates us to construct potential idempotents by taking two light leaves whose top sequences are identical, and composing $A$ upside-down with $B$.
+If $AB=1$, then this will yield an idempotent.
+
+This motivates the main objective of study.
+\begin{ques*}
+	For a fixed $\ul r$ and two binary sequences $\ul a$ and $\ul b$ with $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, find a formula for $\MM_{\ul r}(\ul a, \ul b)$ in terms of $\ul r$, $\ul a$, and $\ul b$.
+\end{ques*}
+Here, we are interested in computing the polynomial which corresponds to this map.
 
 \section{A Complete Characterization of the One-Color Case}
+\label{sec:res_onecolor}
 In this section we provide a complete characterization for the $\MM_{\SS_n}(\ul a, \ul b)$.
@@
 	On the other hand, suppose this product is nonzero, and consider a component from the top with $k$ antennae.
-Each of its antennae then feels a distinct component.
-Hence, it unites $k$ different components into one.
-
-	The formula then follows directly from counting the number of connected components, because each component can be contracted into a single barbell, since any acyclic connected component is merely a tree.
+We claim that there are $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees; this would complete the proof, because each tree contracts to a barbell.
+Notice that $\pi_1(\ul a^\ast) + \pi_1(\ul b^\ast)$ counts the number of edges between adjacent anchors ($i$ and $i+1$).
+Because there are no cycles, deleting one of these edges increases the number of connected components by exactly one (since all the connected components are trees).
+If we delete all such edges, then we obtain $n$ barbells.
+Therefore there must have been $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees to begin with, as desired.
 \end{proof}
@@
 \section{Counting Maps}
+\label{sec:res_count_maps}
 We give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r} \ul b = \ul T$ for each expression $\ul T$ and $\ul r$.
@@
 
-\begin{theorem}
+\begin{proposition}
 	Let $\ul r$ be an expression of length $\ell$, and suppose $R(\ul r) = \AA_n$.
@@
 	\label{thm:count_maps}
-\end{theorem}
+\end{proposition}
 Of course, if $\ul r$ begins with the character $t$, then one can simply reverse the roles of $s$ and $t$ in the above theorem to obtain an analogous formula.
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:count_maps}]
+\begin{proof}[Proof of Proposition \ref{thm:count_maps}]
 	First we will resolve the case where $\ul r = \AA_n$, so that $\ell = n$ and $2^{\ell-n} = 1$.
@@
 
-	To complete the theorem, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there a $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
+	To finish to all cases, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there a $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
 (This follows from Proposition \ref{prop:s_top}.)  This reduces to the previous case $\ul r = \AA_n$, but with some extra factors of $2$; aggregating all of them yields the factor of $2^{\ell-n}$, as desired.
@@
 \section{Constraints in the Alternating Case}
+\label{sec:res_altcase}
 We now turn our attention to the case of $\ul r = \AA_n$.
@@
 	\begin{enumerate}[(i)]
-		\ii Pastures $1$ through $N-1$ contain either nothing or a free component.
+		\ii Pastures $1$ through $N-1$ contain either nothing or a attached component.
 		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.
@@
 \section{A Recursion for the Alternating Case}
+\label{sec:res_altrecurse}
 In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
-TODO: Write this.
+
+\begin{proposition}
+	BLAH
+	\label{thm:recurse}
+\end{proposition}
 
@@
 \section{Acknowledgments} 
-I offer my sincerest gratitude to my mentor Mr. Francisco Unda for daily mentorship, and Dr. Benjamin Elias for providing the project and for often meeting with me personally to discuss it.
-That sounded horribly fake, but really, I mean it.  You guys are the best.  Thank you for a great project.
+I wish to thank the MIT Math Department for organizing the Math RSI, and in particular the head mentor Dr. Tanya Khovanova (MIT) for providing individual discussion with me.
+I also wish to thank my tutor Mr. Antoni Rangachev (Northeaster University) for his invaluable advice in preparing both this paper and my final presentation.
+I would also like to thank the Center for Excellence in Education and the Research Science Institute, as well as the Massachusetts Institute of Technology, for generously providing the facilities for the research.
 
-I further wish to thank the MIT Math Department, and in particular the head mentor Dr. Tanya Khovanova, for organizing the Math RSI and providing individual discussion with me.
-I also wish to thank my tutor Mr. Antoni Rangachev for his invaluable advice in preparing both this paper and my final presentation.
-Finally, I would like to thank the Center for Excellence in Education and the Research Science Institute for generously providing the facilities for the research.
+Finally, I offer my sincerest gratitude to my mentor Mr.
+Francisco Unda (MIT) for daily mentorship, and Professor Benjamin Elias (MIT), for providing the project and for often meeting with me personally to discuss it.
+That sounded horribly fake, but I really mean it.  You guys are the best.  Thank you for a great project.

### 2013-07-25 summary.tex
blargh

@@
 
-The non-technical summary is like an abstract, but without any technical
-terminology. So instead of $v = (v_0, v_1, \ldots, v_n)$, you might say
-something along the lines of ``pick a point in high-dimensional space.''
-Don't worry about this section yet; you'll receive more guidance
-later on, when you're near the end of your mentorship.
+We consider maps between structures called Bott-Samelson bimodules, and study these maps using special diagrams.
+We want to find a formula for the product of two such maps.
+This paper gives a formula for the uniform case, and provides restrictions on the possible products for an ``alternating'' case.
+We also count the number of maps between any two given Bott-Samelson bimodules.

### 2013-07-26 paper.tex
Fixed obvious typos.

@@
 
-\subsection{Quantum Numbers}
+\subsubsection{Quantum Numbers}
 A particularly nice sequence of polynomials involved can be defined recursively.  They are termed \emph{two-color quantum numbers}.
@@
 	\begin{enumerate}[(i)]
-		\ii Pastures $1$ through $N-1$ contain either nothing or a attached component.
+		\ii Pastures $1$ through $N-1$ contain either nothing or an attached component.
 		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.

### 2013-07-26 paper.tex
fail

@@
 \begin{definition*}[Quantum Numbers]
-	For each integer $n \ge 0$, define two polynomials $[n]_x, [n]_y \in \ZZ[x,y]$ recursively by $[0]_x = [0]_y = 0$, $[1]_x = [1]_y = 1$, $[2]_x = x$, $[2]_y = 2$, and
+	For each integer $n \ge 0$, define two polynomials $[n]_x, [n]_y \in \ZZ[x,y]$ recursively by $[0]_x = [0]_y = 0$, $[1]_x = [1]_y = 1$, $[2]_x = x$, $[2]_y = y$, and
 	\begin{align*}

### 2013-07-26 paper.tex
qq git

--- 2013-07-25 paper.tex
@@
 In section \ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.
-The most interesting results are in sections \ref{sec:res_altcase} and \ref{sec:res_altrecurse}, where we investigate the case where the given string is $ststst\cdots$.
+The most interesting results are in sections \ref{sec:res_altcase} and \ref{sec:res_altcompute}, where we investigate the case where the given string is $ststst\cdots$.
 In particular, we show that the possible resulting structures is extremely limited, and provide a recursion based on these restrictions for special cases.
@@
 We will denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
+If the two half-maps are not compatible -- i.e.
+$\Top_{\ul r} \ul a \neq \Top_{\ul r} \ul b$ -- then we will simply treat the product as the zero map.
 % Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.
@@
 
-\section{A Recursion for the Alternating Case}
-\label{sec:res_altrecurse}
+\section{Computations for the Alternating Case}
+\label{sec:res_altcompute}
+We now turn to using the tools developed in section \ref{sec:res_altcase} in order to compute polynomials. First, we add some structure to these special cases.
+
+\begin{corollary}
+	For any binary strings $\ul a$ and $\ul b$ of length $n$
+\end{corollary}<++>
+
 In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
 
+\begin{definition*}
+	We say that two strings $\ul{r_1}$ and $\ul{r_2}$ \emph{agree in $c$} if their last characters are both $c$.
+\end{definition*}
+\begin{definition*}
+	For a binary string $\ul r$, let $\ul r'$ be the string formed by deleting the last bit of $\ul r$.
+\end{definition*}
+
 \begin{proposition}
-	BLAH
+	Suppose $n \ge 1$ is an integer.
+Let $\ul a$ and $\ul b$ be two binary strings of length $n$ which agree in the last bit, which have the same top $T = \Top_{\AA_n} \ul a = \Top_{\AA_n} \ul b$.
+Suppose $M_1 = \MM_{\AA_{n-1}} (\ul a', \ul b') \neq 0$.
+Then $M = \MM_{\AA_n} (\ul a, \ul b$) is nonzero, and the following recursion holds.
+	\begin{enumerate}[(i)]
+		\ii If $\AA_n$ and $T$ have the same last character $c$ (so $T \neq \varnothing$)
+		\begin{itemize}
+			\ii If $\ul a[n] = \ul[b] = 1$, then $M = M_1$.
+			\ii If $\ul a[n] = \ul[b] = 0$, then $M = -f / \alpha_k$ where $f$ is the monomial in $M_1$ with the largest factor of $\alpha_k$, with any quantum numbers
+		\end{itemize}<++>
+	\end{enumerate}<++>
 	\label{thm:recurse}

### 2013-07-26 paper.tex

@@
 
-\subsection{Quantum Numbers}
+\subsubsection{Quantum Numbers}
 A particularly nice sequence of polynomials involved can be defined recursively.  They are termed \emph{two-color quantum numbers}.
 \begin{definition*}[Quantum Numbers]
-	For each integer $n \ge 0$, define two polynomials $[n]_x, [n]_y \in \ZZ[x,y]$ recursively by $[0]_x = [0]_y = 0$, $[1]_x = [1]_y = 1$, $[2]_x = x$, $[2]_y = 2$, and
+	For each integer $n \ge 0$, define two polynomials $[n]_x, [n]_y \in \ZZ[x,y]$ recursively by $[0]_x = [0]_y = 0$, $[1]_x = [1]_y = 1$, $[2]_x = x$, $[2]_y = y$, and
 	\begin{align*}

### 2013-07-26 paper.tex
I hate my life.

@@
 In the case where there are no consecutive identical characters (e.g.
-$\AA_n$), we will refer to them as \emph{reduced expressions}.
+the string is either $\AA_n$ or $\AA_n'$), we will refer to them as \emph{reduced expressions}.
 
@@
 
+This motivates us to make the following definition, which will be used in section \ref{sec:res_altcompute}.
+\begin{definition*}
+	For any reduced expression $\ul r$, we adopt the quantum polynomial $Q_{\ul r}$ by :
+	\[
+		Q_{\AA_n} = 
+		\begin{cases}
+			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd} \\
+			[n]_x \alpha_s + [n+1]_y \alpha_t & \text{if $n$ is even}
+		\end{cases}
+	\]
+	when $\ul r = \AA_n$, and otherwise,
+	\[
+		Q_{\AA_n'} =
+		\begin{cases}
+			[n]_x \alpha_s + [n+1]_y \alpha_t & \text{if $n$ is even} \\
+			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd}
+		\end{cases}.
+	\]
+\end{definition*}
+
+It is easy to observe that if $\ul r$ is a reduced expression of length $n+1$, then \[ \MM_{\ul r} ( \underbrace{11\dots11}_{\text{$n$ 1's}}0, \underbrace{11\dots11}_{\text{$n$ 1's}}0 ) = Q_{\ul r}.
+\]
+
 \section{Problem Statement}
@@
 \begin{proposition}
-	For any $\ul b$ of length $n$, \[
+	For any $\ul b \in \BB_n$, \[
 		\Top_{\SS_n} \ul b =
@@
 In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
-\begin{theorem}[Bubble Theorem]
+\begin{lemma}[Bubble Lemma]
 	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
 	\label{thm:bubble}
-\end{theorem}
+\end{lemma}
 \begin{theorem}[Caterpillar Theorem]
@@
 		\ii Pastures $1$ through $N-1$ contain either nothing or an attached component.
-		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.
+		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise, with color corresponding to $\AA_n[n]$.
 	\end{enumerate}
@@
 
-\subsection{Proof of the Bubble Theorem}
+\subsection{Proof of the Bubble Lemma}
 We begin with a proof of the bubble theorem, which is the crux result of the alternating case.  Indeed, both of the subsequent theorems are fairly straightforward consequences of this theorem.
 
-It's interesting to note that the Bubble Theorem is intuitively very natural.  The main difficulty is finding a clean way to handle the special cases generated by the convoluted geometry.
+It's interesting to note that the Bubble Lemma is intuitively very natural.  The main difficulty is finding a clean way to handle the special cases generated by the convoluted geometry.
 
-\begin{proof}[Proof of Theorem \ref{thm:bubble}]
+\begin{proof}[Proof of Lemma \ref{thm:bubble}]
 	Take a bubble $B$ and assume without loss of generality that it is blue.
@@
 \subsection{Proof of the Caterpillar Theorem}
-We will now derive the Caterpillar Theorem as a consequence of the Bubble Theorem.
+We will now derive the Caterpillar Theorem as a consequence of the Bubble Lemma.
 
@@
 	For the inductive step, consider an arbitrary bubble.
-Inside it is exactly one caterpillar, say $c$, by the Bubble Theorem.
+Inside it is exactly one caterpillar, say $c$, by the Bubble Lemma.
 Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
@@
 	\end{asy}
-	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Theorem from the Bubble Theorem.}
+	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Theorem from the Bubble Lemma.}
 	\label{fig:pf_pasture}
 \end{figure}
-The bubble theorem and the pasture theorem are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Theorem follows from the Bubble Theorem.
+The bubble theorem and the pasture theorem are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Theorem follows from the Bubble Lemma.
 \begin{proof}[Proof of Theorem \ref{thm:pasture}]
@@
 Now what we have done is enclose the contents of each pasture into bubbles.
-The Bubble Theorem tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.
+The Bubble Lemma tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.
 This implies the Pasture Theorem in the first case.
@@
 
-\begin{corollary}
-	For any binary strings $\ul a$ and $\ul b$ of length $n$
-\end{corollary}<++>
-
-In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
-
 \begin{definition*}
-	We say that two strings $\ul{r_1}$ and $\ul{r_2}$ \emph{agree in $c$} if their last characters are both $c$.
+	We say that two strings $\ul{r_1}$ and $\ul{r_2}$ \emph{agree}, or \emph{agree in $c$} if their last characters are both $c$.
 \end{definition*}
@@
 
+\begin{corollary}
+	For any binary strings $\ul a, \ul b \in \BB_n$, if $\MM_{\AA_n} (\ul a, \ul b)$ is nonzero and has top $T$, then for some nonnegative integers $m_x$, $m_y$, $m_s$, and $m_t$, we have 
+	\[
+		\MM_{\AA_n} (\ul a, \ul b) =
+		x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t} \cdot
+		\begin{cases}
+			1 & \text{if $T$ and $\AA_n$ agree} \\
+			Q_T & \text{otherwise}
+		\end{cases}.
+	\]
+\end{corollary}
+\begin{proof}
+	This is an immediate consequence of the Caterpillar Theorem and the Pasture Theorem.
+Everything in the first pasture is a product of monomials by the Caterpillar Theorem.
+If $T$ and $\AA_n$ agree, then the last pasture is empty and hence we obtain the first case.
+Otherwise, there is a single caterpillar of color opposite to $T$, and hence after evaluating that caterpillar, we obtain some monomial times a single barbell.
+This generates the final $Q_T$ term.
+\end{proof}
+
+In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
+
 \begin{proposition}
-	Suppose $n \ge 1$ is an integer.
-Let $\ul a$ and $\ul b$ be two binary strings of length $n$ which agree in the last bit, which have the same top $T = \Top_{\AA_n} \ul a = \Top_{\AA_n} \ul b$.
+	Let $n \ge 2$ be an integer.
+Suppose $\ul a, \ul b \in \BB_n$ have the same top $T = \Top_{\AA_n} \ul a = \Top_{\AA_n} \ul b$, and further that $\ul a$ and $\ul b$ agree.
 Suppose $M_1 = \MM_{\AA_{n-1}} (\ul a', \ul b') \neq 0$.
-Then $M = \MM_{\AA_n} (\ul a, \ul b$) is nonzero, and the following recursion holds.
+Then $M = \MM_{\AA_n} (\ul a, \ul b)$ is nonzero, and the following recursion holds.
 	\begin{enumerate}[(i)]
@@
 		\begin{itemize}
-			\ii If $\ul a[n] = \ul[b] = 1$, then $M = M_1$.
-			\ii If $\ul a[n] = \ul[b] = 0$, then $M = -f / \alpha_k$ where $f$ is the monomial in $M_1$ with the largest factor of $\alpha_k$, with any quantum numbers
-		\end{itemize}<++>
-	\end{enumerate}<++>
+			\ii If $\ul a[n] = \ul b[n] = 1$, then $M = M_1$.
+			\ii If $\ul a[n] = \ul b[n] = 0$, then $M = -f / \alpha_k$ where $f$ is the monomial in $M_1$ with the largest factor of $\alpha_k$, with any quantum numbers
+		\end{itemize}
+	\end{enumerate}
+	BLAH BLAH BLAH BLAH BLAH 
+	% TODO : figure out what the hell this is supposed to be
 	\label{thm:recurse}

### 2013-07-26 paper.tex
Ow.

@@
 We study a class of maps between Bott-Samelson bimodules.
-These maps are represented by certain types of diagrams, as described in section \ref{sec:prelim_map}.
+These maps are represented by certain types of diagrams, as described in Section~\ref{sec:prelim_map}.
 The maps are composed by juxtaposition.
@@
 
-Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in section \ref{sec:prelim_lightleave}.
+Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in Section~\ref{sec:prelim_lightleave}.
 Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.
@@
 
-Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:probstate}.
-The results begin by solving the special case of one color completely in section \ref{sec:res_onecolor}.
-In section \ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.
-The most interesting results are in sections \ref{sec:res_altcase} and \ref{sec:res_altcompute}, where we investigate the case where the given string is $ststst\cdots$.
+Because the technical description of the problem statement is quite involved, we devote the entirety of Section~\ref{sec:prelim} to preliminaries and defer the actual problem statement to Section~\ref{sec:probstate}.
+The results begin by solving the special case of one color completely in Section~\ref{sec:res_onecolor}.
+In Section~\ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.
+The most interesting results are in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate the case where the given string is $ststst\cdots$.
 In particular, we show that the possible resulting structures is extremely limited, and provide a recursion based on these restrictions for special cases.
@@
 \label{sec:prelim}
-In section \ref{sec:prelim_background}, we provide the background behind the Bott-Samelson bimodules, and the correspondence between these maps and certain diagrams.
+In Section~\ref{sec:prelim_background}, we provide the background behind the Bott-Samelson bimodules, and the correspondence between these maps and certain diagrams.
 We then introduce Libedinsky's light leaves, a basis by which maps can be constructed using binary strings.
 
-In section \ref{sec:prelim_def_notation}, we introduce several definitions which we use throughout the paper.
-Next, in section \ref{sec:prelim_explain_poly_eval}, we describe how these maps can be represent as polynomials.
+In Section~\ref{sec:prelim_def_notation}, we introduce several definitions which we use throughout the paper.
+Next, in Section~\ref{sec:prelim_explain_poly_eval}, we describe how these maps can be represent as polynomials.
 The actual problem statement is then deferred to \ref{sec:probstate}.
@@
 \label{sec:prelim_background}
-% \subsection{Coxeter Rings, and the Bott-Samelson Bimodules}
 Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be arbitrary vectors normal to these planes.
@@
 In other words, $W$ is the infinite dihedral group with the presentation \[ W = \left<s,t \mid s^2=t^2=1\right>.
-\] If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then each $v \in V$ is reflected over a hyperplane normal to any $a \in V$ via the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a.
+\]
+
+If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then for any $a \in V$, reflection over the hyperplane normal to $a$ can be written explicitly for each $v \in V$ as the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a.
 \]
@@
 We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.
-A reader who is not interested in this context can simply accept on faith the relations specified in section \ref{sec:prelim_genrel}.
+A reader who is not interested in this context can simply accept on faith the relations specified in Section~\ref{sec:prelim_genrel}.
 
@@
 
-An example of such a diagram is shown in figure \ref{fig:example_diagram}.
+An example of such a diagram is shown in Figure~\ref{fig:example_diagram}.
 
@@
 Therefore, by a combination of these structures, we can generate arbitrarily complicated maps.
-For example, the map in figure \ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d.
+For example, the map in Figure~\ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d.
 \]
@@
 With this understanding, any of the graphs described in the previous section can be viewed as compositions of the primitive structures we describe here.
-
-% Subsequently, for any polynomial $f \in R$ we will abuse notation and refer to the map $x \mapsto fx$ by simply $f$.
-In particular, one can easily verify that $\barbell{barbell_blue}$ represents $\alpha_s$.
-Note that this is \emph{not} in general the same as $x \mapsto xf$ because $x$ may belong to some bimodule rather than to $R$.
-Phrased diagrammatically, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \barbell{barbell_blue}\barbell{alpha_blue} = \alpha_s$, for instance.
 
@@
 A map which arises in such a manner is called a \emph{light leaf}.
-An example of such a light leaf is shown in figure \ref{fig:lightleaf_example}.
+An example of such a light leaf is shown in Figure~\ref{fig:lightleaf_example}.
 
@@
 		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
-		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
-	\end{cases}.
+		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2}. 
+	\end{cases}
 \]
@@
 Consider a string $\ul r$ of letters $s$ and $t$.
-Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangably) formed by the light leaves.
+Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangeably) formed by the light leaves.
 We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.
-Additionally, let $\Top_{\ul r} \ul b$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.
+Additionally, let $\Top_{\ul r}(\ul b)$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.
 
@@
 We will denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
-If the two half-maps are not compatible -- i.e.
-$\Top_{\ul r} \ul a \neq \Top_{\ul r} \ul b$ -- then we will simply treat the product as the zero map.
-% Then given two binary strings $\ul a$ and $\ul b$, we will let $\MM_{\ul r}(\ul a, \ul b)$ denote the product of $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ if $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, and $0$ otherwise.
+If the two half-maps are not compatible (that is, $\Top_{\ul r}(\ul a) \neq \Top_{\ul r}(\ul b)$) then we will simply treat the product as the zero map.
 
@@
 We will call those vertices, whether on the bottom boundary of a half-map or the center of a full-map, the \emph{anchors} for that map, and the associated sequence of letters the \emph{base}.
-Furthermore, the line on which the anchors lie will be called the \emph{anchorline}.
-
-An example of a full-map with base $\AA_5$ is given in figure \ref{fig:example_full_map}.
+
+An example of a full-map with base $\AA_5$ is given in Figure~\ref{fig:example_full_map}.
 
@@
 \end{figure}
-
-% We will now abuse notation further and refer even to components by polynomials, when the map is left alone.
-For example, $\barbell{alpha_blue}\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}$ might be referred interchangeably with $\barbell{alpha_blue} \alpha_s^2 \alpha_t$.
-Note that, even though we may write $\barbell{alpha_blue} = 1$, we still have $\barbell{alpha_blue} \alpha_s^2\alpha_t \neq \alpha_s^2\alpha_t$, because we strictly require left multiplication as the accepted convention.
 
@@
 \end{definition*}
-An example of a fence complete with two barbells is given in figure \ref{fig:def_barbell_fence}.
+An example of a fence complete with two barbells is given in Figure~\ref{fig:def_barbell_fence}.
 
@@
 
-An example of a bubble is given in figure~\ref{fig:def_bubble}.
+An example of a bubble is given in Figure~\ref{fig:def_bubble}.
 
@@
 \end{definition*}
-An example of a caterpillar is given in figure~\ref{fig:def_caterpillar}.  Notice that any barbell or bubble is a special case of a caterpillar.
+An example of a caterpillar is given in Figure~\ref{fig:def_caterpillar}.  Notice that any barbell or bubble is a special case of a caterpillar.
 
@@
 That is, any map which contains a connected component that touches any boundary only once (total) is considered zero.
-So, for example, $\barbell{break_blue} = 0$.
+So, for example, we have $\barbell{break_blue} = 0$.
 \end{enumerate}
@@
 \end{equation}
-where $\partial_s$ is the Demazure operator defined in section \ref{sec:prelim_genrel}.
+where $\partial_s$ is the Demazure operator defined in Section~\ref{sec:prelim_genrel}.
 
@@
 
-This motivates us to make the following definition, which will be used in section \ref{sec:res_altcompute}.
+This motivates us to make the following definition, which will be used in Section~\ref{sec:res_alt_compute}.
 \begin{definition*}
@@
 			[n]_x \alpha_s + [n+1]_y \alpha_t & \text{if $n$ is even} \\
-			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd}
-		\end{cases}.
+			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd}.
+		\end{cases}
 	\]
@@
 \begin{ques*}
-	For a fixed $\ul r$ and two binary sequences $\ul a$ and $\ul b$ with $\Top_{\ul r} \ul a = \Top_{\ul r} \ul b$, find a formula for $\MM_{\ul r}(\ul a, \ul b)$ in terms of $\ul r$, $\ul a$, and $\ul b$.
+	For a fixed $\ul r$ and two binary sequences $\ul a$ and $\ul b$ with $\Top_{\ul r}(\ul a) = \Top_{\ul r}(\ul b)$, find a formula for $\MM_{\ul r}(\ul a, \ul b)$ in terms of $\ul r$, $\ul a$, and $\ul b$.
 \end{ques*}
@@
 	For any $\ul b \in \BB_n$, \[
-		\Top_{\SS_n} \ul b =
+		\Top_{\SS_n}(\ul b) =
 		\begin{cases}
 			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
-			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
-		\end{cases}.
+			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2}.
+		\end{cases}
 		\]
@@
 			1 & \text{if } \ul b[1] + \ul b[2] + \dots + \ul b[i] \equiv 1 \pmod{2} \\
-			0 & \text{otherwise}
-		\end{cases}.
+			0 & \text{otherwise}.
+		\end{cases}
 	\]
@@
 \begin{theorem}
-	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
+	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n}(\ul a) = \Top_{\SS_n}(\ul b)$, then
 	\[
@@
 			0 & \text{if }\ \exists 1 \le i \le n-1:\ \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
-			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
-		\end{cases}.
+			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}.
+		\end{cases}
 	\]
@@
 \begin{proof}
-	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.
-See figure \ref{fig:pf_trivial_theorem_example} for a example of such a map.
+	We will only consider the case where $\Top(\ul a) = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.
+See Figure~\ref{fig:pf_trivial_theorem_example} for a example of such a map.
 
@@
 \label{sec:res_count_maps}
-We give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r} \ul b = \ul T$ for each expression $\ul T$ and $\ul r$.
-One can check that, by construction, $\Top \ul b$ is always a reduced expression.
+We give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r}(\ul b) = \ul T$ for each expression $\ul T$ and $\ul r$.
+One can check that, by construction, $\Top(\ul b)$ is always a reduced expression.
 
@@
 	\begin{enumerate}[(i)]
-		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r} \ul b$.
-		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r} \ul b$.
+		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r}(\ul b)$.
+		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r}(\ul b)$.
 	\end{enumerate}
@@
 
-\section{Constraints in the Alternating Case}
-\label{sec:res_altcase}
+\section{Colorful Lemmata for the Alternating Case}
+\label{sec:res_alt_restrict}
 We now turn our attention to the case of $\ul r = \AA_n$.
@@
 \end{lemma}
-\begin{theorem}[Caterpillar Theorem]
+\begin{lemma}[Caterpillar Lemma]
 	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
 	\label{thm:caterpillar}
-\end{theorem}
-\begin{theorem}[Pasture Theorem]
+\end{lemma}
+\begin{lemma}[Pasture Lemma]
 	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
@@
 	\label{thm:pasture}
-\end{theorem}
+\end{lemma}
 
 \subsection{Proof of the Bubble Lemma}
-We begin with a proof of the bubble theorem, which is the crux result of the alternating case.  Indeed, both of the subsequent theorems are fairly straightforward consequences of this theorem.
-
-It's interesting to note that the Bubble Lemma is intuitively very natural.  The main difficulty is finding a clean way to handle the special cases generated by the convoluted geometry.
+We begin with a proof of the Bubble Lemma\footnote{I should remark that attempting to construct counterexamples to the Bubble Lemma leads to a far better understanding than trying to read the following proof.}, which is the crux result of the alternating case.
+Indeed, both of the subsequent lemmas are fairly straightforward consequences of this one.
 
@@
 		\end{asy}
-		\caption{Proving the bubble theorem with quasi-connected vertices.}
+		\caption{Proving the bubble lemma with quasi-connected vertices.}
 		\label{fig:pf_bubble}
@@
 But then this contradicts the quasi-connectedness, because now it is not possible to join $u$ and $v$ by an arc on this half-map.
-This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
+This case is illustrated by the left half of Figure~\ref{fig:pf_bubble}.
 		\ii If the arc covers both $u$ and $v$, then there must be a blue arc which shields both $u$ and $v$, which is itself shielded by $A$.
 Then we can repeat the same procedure with this new blue arc.
-This case is illustrated by the right half of figure \ref{fig:pf_bubble}.
+This case is illustrated by the right half of Figure~\ref{fig:pf_bubble}.
 	\end{itemize}
@@
 
-\subsection{Proof of the Caterpillar Theorem}
-We will now derive the Caterpillar Theorem as a consequence of the Bubble Lemma.
+\subsection{Proof of the Caterpillar Lemma}
+We will now derive the Caterpillar Lemma as a consequence of the Bubble Lemma.
 
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:caterpillar}]
+\begin{proof}[Proof of Lemma \ref{thm:caterpillar}]
 	The proof is by double induction.  First we will consider caterpillars with nesting level $0$.
@@
 
-\subsection{Proof of the Pasture Theorem}
+\subsection{Proof of the Pasture Lemma}
 \begin{figure}[ht]
@@
 	\end{asy}
-	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Theorem from the Bubble Lemma.}
+	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Lemma from the Bubble Lemma.}
 	\label{fig:pf_pasture}
 \end{figure}
-The bubble theorem and the pasture theorem are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Theorem follows from the Bubble Lemma.
-\begin{proof}[Proof of Theorem \ref{thm:pasture}]
+The Bubble Lemma and the Pasture Lemma are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Lemma follows from the Bubble Lemma.
+\begin{proof}[Proof of Lemma \ref{thm:pasture}]
 	Again, let $T$ denote the top, with length $N$.
@@
 Now consider the map \[ \MM_{\AA_{n+N}} \left( \ul a', \ul b' \right).
-\]  See figure \ref{fig:pf_pasture} for an example.
+\]  See Figure~\ref{fig:pf_pasture} for an example.
 
@@
 The Bubble Lemma tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.
-This implies the Pasture Theorem in the first case.
+This implies the Pasture Lemma in the first case.
 
@@
 
-\section{Computations for the Alternating Case}
-\label{sec:res_altcompute}
-We now turn to using the tools developed in section \ref{sec:res_altcase} in order to compute polynomials. First, we add some structure to these special cases.
-
-\begin{definition*}
-	We say that two strings $\ul{r_1}$ and $\ul{r_2}$ \emph{agree}, or \emph{agree in $c$} if their last characters are both $c$.
-\end{definition*}
-\begin{definition*}
-	For a binary string $\ul r$, let $\ul r'$ be the string formed by deleting the last bit of $\ul r$.
-\end{definition*}
-
-\begin{corollary}
+\section{Algebraic Computations for the Alternating Case}
+\label{sec:res_alt_compute}
+We now turn to using the tools developed in Section~\ref{sec:res_alt_restrict} in order to compute polynomials. First, we add some structure to these special cases.
+
+\subsection{Restrictions and Definitions for the Final Output}
+Let us now endow our maps with base $\AA_n$ with some additional structure.
+\begin{theorem}
 	For any binary strings $\ul a, \ul b \in \BB_n$, if $\MM_{\AA_n} (\ul a, \ul b)$ is nonzero and has top $T$, then for some nonnegative integers $m_x$, $m_y$, $m_s$, and $m_t$, we have 
@@
 		\begin{cases}
-			1 & \text{if $T$ and $\AA_n$ agree} \\
-			Q_T & \text{otherwise}
-		\end{cases}.
-	\]
-\end{corollary}
+			1 & \text{if $T$ and $\AA_n$ have the same last character} \\
+			Q_T & \text{otherwise}.
+		\end{cases}
+	\]
+	\label{thm:alt_struct}
+\end{theorem}
 \begin{proof}
-	This is an immediate consequence of the Caterpillar Theorem and the Pasture Theorem.
-Everything in the first pasture is a product of monomials by the Caterpillar Theorem.
+	This is an immediate consequence of the Caterpillar Lemma and the Pasture Lemma.
+Everything in the first pasture is a product of monomials by the Caterpillar Lemma.
 If $T$ and $\AA_n$ agree, then the last pasture is empty and hence we obtain the first case.
@@
 
-In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
+This motivates the following definition.
+\begin{definition*}
+	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ will be called the \emph{fluff} of $M$, and the polynomial (either $1$ or $Q_T$) will be the \emph{face} of $M$.
+\end{definition*}
+\begin{remark*}
+	According to Theorem~\ref{thm:alt_struct}, a nonzero map $\MM_{\AA_n}$ has face $1$ and only if its top has the same last character as $\AA_n$.
+\end{remark*}
+
+\subsection{A Partial Recursion}
+In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.
 
 \begin{proposition}
-	Let $n \ge 2$ be an integer.
-Suppose $\ul a, \ul b \in \BB_n$ have the same top $T = \Top_{\AA_n} \ul a = \Top_{\AA_n} \ul b$, and further that $\ul a$ and $\ul b$ agree.
-Suppose $M_1 = \MM_{\AA_{n-1}} (\ul a', \ul b') \neq 0$.
-Then $M = \MM_{\AA_n} (\ul a, \ul b)$ is nonzero, and the following recursion holds.
+	Let $n \ge 2$ be an odd integer and consider two binary strings $\ul a, \ul b \in \BB_n$ such that $T = \Top_{\AA_n}(\ul a) = \Top_{\AA_n}(\ul b)$.  
+	Let $\ul a'$ and $\ul b'$ are the first $n-1$ bits of $\ul a$ and $\ul b$, respectively. 
+	Suppose $M_1 = \MM_{\AA_{n-1}} \left(\ul a', \ul b'\right)$ is a nonzero map with fluff $F$.
 	\begin{enumerate}[(i)]
-		\ii If $\AA_n$ and $T$ have the same last character $c$ (so $T \neq \varnothing$)
+		\ii If $\ul a[n] = \ul b[n] = 0$, then
+		\[ \MM_{\AA_n} (\ul a, \ul b)
+			=
+			\begin{cases}
+				M_1 \alpha_s & \text{if $T = \varnothing$} \\ % just another barbell
+				-xF & \text{if $T$ ends in $s$} \\ % closes a caterpillar like 0|
+				M_1 Q_T & \text{if $T$ ends in $t$}. \\ % just another barbell, but push it all the way through nonempty T
+			\end{cases}
+		\]
+		\ii If $\ul a[n] = \ul b[n] = 1$, then
+		\[
+			\MM \AA_n (\ul a, \ul b)
+			=
+			\begin{cases}
+				-x\alpha_sF & \text{if $T = \varnothing$} \\ % destructive 1, closes a caterpillar O
+				M_1 & \text{if $T$ ends in $s$} \\ % constructive 1
+				-xF Q_T & \text{if $T$ ends in $t$}. % destructive 1
+			\end{cases}
+		\]
+	\end{enumerate}
+	Analogous statements hold when $n$ is an even integer, with the roles of $x$ and $y$ interchanged, as well as the roles of $s$ and $t$.
+	\label{thm:recurse}
+\end{proposition}
+
+Notice that this recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
+
+\begin{proof}
+	We will only resolve the case where $n$ is odd; that is, $\AA_n$ terminates in $s$.  The other case is identical.
+	\begin{enumerate}[(i)]
+		\ii Suppose $\ul a[n] = \ul b[n] = 0$.  Note that the top of $M_1$ is also $T$.
 		\begin{itemize}
-			\ii If $\ul a[n] = \ul b[n] = 1$, then $M = M_1$.
-			\ii If $\ul a[n] = \ul b[n] = 0$, then $M = -f / \alpha_k$ where $f$ is the monomial in $M_1$ with the largest factor of $\alpha_k$, with any quantum numbers
+			\ii If $T = \varnothing$, then $M_1$ also had top $\varnothing$.
+Therefore, the addition of the $0$'s at the end simply generates an extra blue barbell.
+So the resulting map is simply a multiple by $\alpha_s$.
+			\ii The case where $T$ ends in $t$ is analogous; we simply obtain a new barbell.  However, because $T \neq \emptyset$, the extra factor is $Q_T$ instead of simply $\alpha_t$. 
+			\begin{figure}[ht]
+				\centering
+				\begin{asy}
+					size(12cm);
+					real h = 0.7;
+					pen s = blue, t = red + dashed + 0.6;
+					pen dot_s = blue, dot_t = red;
+					int n = 4;
+
+					picture one;
+					draw(one, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+					draw(one, (1,0)--(1,h), t);
+					dot(one, (1,h), dot_t);
+					draw(one, (3,0)--(3,h), t);
+					dot(one, (3,h), dot_t);
+					draw(one,(2,0)--(2,3*h), s);
+					dot(one, (2, h/2), dot_s);
+
+					picture two;
+					draw(two, (0,0)--(0,h), s);
+					dot(two, (0,h), dot_s);
+					draw(two, (1,0)--(1,h), t);
+					dot(two, (1,h), dot_t);
+					draw(two, (3,0)--(3,h), t);
+					dot(two, (3,h), dot_t);
+					draw(two,(2,0)--(2,3*h), s);
+
+					add(one); add(reflect((0,0),(1,0))*two);
+					draw((-1,0)--(4,0));
+
+					int n = 5;
+
+					picture three;
+					draw(three, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+					draw(three, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(three, (1,0)--(1,h), t);
+					dot(three, (1,h), dot_t);
+					draw(three, (3,0)--(3,h), t);
+					dot(three, (3,h), dot_t);
+					draw(three,(4,0)--(4,3*h), s);
+					dot(three, (2, h/2), dot_s);
+					dot(three, (4, h/2), dot_s);
+
+					picture four;
+					draw(four, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(four, (0,0)--(0,h), s);
+					dot(four, (0,h), dot_s);
+					draw(four, (1,0)--(1,h), t);
+					dot(four, (1,h), dot_t);
+					draw(four, (3,0)--(3,h), t);
+					dot(four, (3,h), dot_t);
+					draw(four,(4,0)--(4,3*h), s);
+					dot(four, (4, h/2), dot_s);
+
+					add(shift((7,0)) * three); add(shift((7,0)) * reflect((0,0),(1,0))*four);
+					draw((7-1,0)--(7+5,0));
+					MP("\to", (5,0), (0,0));
+				\end{asy}
+				\caption{$\MM(1000, 0010)$ on left against $\MM(10000, 00100)$ on right.}
+				\label{fig:recurse_example_destr_zero}
+			\end{figure}
+			\ii Now suppose $T$ ends in $s$.
+Then the addition of the $0$'s resulted in enclosing a caterpillar of $M_1$ in an attached bubble, as per Figure~\ref{fig:recurse_example_destr_zero}.
+Breaking out of the additional blue loop nows adds a factor of $x$, but the red caterpillar is annihilated in the process; therefore, only the fluff remains, because there is nothing to push through the fences.
+		\end{itemize}
+		\ii Now suppose that $\ul a[n] = \ul b[n] = 1$.
+		\begin{itemize}
+			\ii First, suppose $T$ ends in $s$.
+Then the additional $1$'s added simply create a fence on the far right, because there is no ``up'' blue anchors to interact with.
+Because this fence is already on the far right, it does not affect the product, hence $M = M_1$.
+			\begin{figure}[ht]
+				\centering
+				\begin{asy}
+					size(11cm);
+					real h = 0.7;
+					pen s = blue, t = red + dashed + 0.6;
+					pen dot_s = blue, dot_t = red;
+					int n = 4;
+
+					picture one;
+					draw(one, (0,0)--(0,h), s);
+					dot(one, (0,h), dot_s);
+					draw(one, (3,0)--(3,h), t);
+					dot(one, (3,h), dot_t);
+					draw(one,(1,0)--(1,3*h), t);
+					draw(one,(2,0)--(2,3*h), s);
+
+					picture two;
+					draw(two, (0,0)--(0,h), s);
+					dot(two, (0,h), dot_s);
+					draw(two, (3,0)--(3,h), t);
+					dot(two, (3,h), dot_t);
+					draw(two,(1,0)--(1,3*h), t);
+					draw(two,(2,0)--(2,3*h), s);
+
+					add(one); add(reflect((0,0),(1,0))*two);
+					draw((-1,0)--(4,0));
+
+					int n = 5;
+
+					picture three;
+					draw(three, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(three, (0,0)--(0,h), s);
+					dot(three, (0,h), dot_s);
+					draw(three, (3,0)--(3,h), t);
+					dot(three, (3,h), dot_t);
+					draw(three,(1,0)--(1,3*h), t);
+
+					picture four;
+					draw(four, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(four, (0,0)--(0,h), s);
+					dot(four, (0,h), dot_s);
+					draw(four, (3,0)--(3,h), t);
+					dot(four, (3,h), dot_t);
+					draw(four,(1,0)--(1,3*h), t);
+
+					add(shift((7,0)) * three); add(shift((7,0)) * reflect((0,0),(1,0)) * four);
+					draw((7-1,0)--(7+5,0));
+					MP("\to", (5,0), (0,0));
+				\end{asy}
+				\caption{$\MM(0110, 0110)$ on left against $\MM(01101, 01101)$ on right.}
+				\label{fig:recurse_example_destr_one}
+			\end{figure}
+			\ii Conversely, suppose that $T$ ends in $t$.   See Figure \ref{fig:recurse_example_destr_one} for an example.
+
+			In that case, $M_1$ must have had the top $T$ with an $s$ appended.
+Once again, we find that the red caterpillar from $M_1$ is enclosed in a bubble.
+This time, however, the bubble is not attached.
+Therefore, while we still obtain the extra factor of $x$ and the caterpillar is still removed, we remain with a blue barbell on the far right pasture.
+So we must push this blue barbell through $T$.
+This adds a factor of $Q_T$, and so we obtain the desired form $-xF Q_T$.
+			\ii The case where $T = \varnothing$ is analogous to the previous case; in a sense, we merely have a degenerate $Q_\varnothing = \alpha_s$.
+Specifically, the blue barbell is already on the correct pasture, so we simply add a factor of $\alpha_s$.
 		\end{itemize}
 	\end{enumerate}
-	BLAH BLAH BLAH BLAH BLAH 
-	% TODO : figure out what the hell this is supposed to be
-	\label{thm:recurse}
-\end{proposition}
+	This exhausts all the cases in the proposition, hence we're done.
+\end{proof}
 
 \section{Conclusion}
-% The conclusion should be a brief summary of what you have done.
-You wish to leave the reader with a clear impression of your ideas and what you have accomplished.
-This section is typically extremely short and in the past tense.
+The overarching goal of the paper was to compute $\MM_{\ul r} (\ul a, \ul b)$ in terms of $\ul r$, $\ul a$, and $\ul b$.
+In this paper, we solved the case where $\ul r = \SS_n$ completely, and showed that the case where $\ul r = \AA_n$ is significantly restricted.
+We also provide a partial recurrence for $\AA_n$.
+One obvious next direction would be to attempt to complete the recursion for $\AA_n$ so that $\MM_{\AA_n} (\ul a, \ul b)$ can be determined completely.
+
+What about the original problem of arbitrary $\ul r$?
+It was originally hoped that, by understanding $\AA_n$ and $\SS_n$, one could derive the general formula (perhaps by viewing strings of $s$'s in $\ul r$ as a single $s$ with a formula for $\SS_n$, and then aggregating all this information with a formula for $\AA_n$).
+Unfortunately, the lemmata of Section~\ref{sec:res_alt_restrict} show that in fact, maps with base $\AA_n$ are quite restricted.
+So, either the results of Section~\ref{sec:res_alt_compute} will have to be generalized significantly (in the context of maps outside those of base $\AA_n$), or an entirely new approach will be required.
 

### 2013-07-27 appa.tex
Yay appendices.

@@
-% This is appa.tex
+% This is sec.tex
 %
@@
 % the percent sign from the beginning of the next line.
-\endinput
+% \endinput
 
@@
 
-\section{Casework for Theorem \ref{thm:count_maps}}
-\label{appa:count_maps}
-Compute like hell.
+\section{An Extended Background}
+\label{sec:prelim_background}
+Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be arbitrary vectors normal to these planes.
+We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.
+In other words, $W$ is the infinite dihedral group with the presentation \[ W = \left<s,t \mid s^2=t^2=1\right>.
+\]
+
+If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then for any $a \in V$, reflection over the hyperplane normal to $a$ can be written explicitly for each $v \in V$ as the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a.
+\]
+In particular, if $W$ acts on $V$ by this reflection, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.
+Furthermore, using the above, we see that there exist fixed constants $x$ and $y$ such that
+\begin{align*}
+	s(\alpha_t) &= \alpha_t + x \alpha_s \\
+	t(\alpha_s) &= \alpha_s + y \alpha_t
+\end{align*}
+Explicitly, $x = \frac{-2(\alpha_s,\alpha_t)}{(\alpha_s, \alpha_s)}$ and $y = \frac{-2(\alpha_t,\alpha_s)}{(\alpha_t,\alpha_t)}$.
+Note that $x=y$ if $\left\lvert \alpha_s \right\rvert = \left\lvert \alpha_t \right\rvert$.
+
+Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.
+
+Let $R^s$ be the subring of $R$ which is invariant under $s$.  Define $R^t$ similarly.  Then a \emph{Bott-Samelson bimodule} is a bimodule of the form
+\[ R \otimes_{R^{i_1}} R \otimes_{R^{i_2}} R \otimes_{R^{i_3}} \dots \otimes_{R^{i_n}} R, \]
+where each $i_j$ is either $s$ or $t$.   Elements of such a bimodule will be written in the form $f_0 \mid f_1 \mid \dots \mid f_n$, where $f_i \in R$.
+
+We will consider maps between these bimodules that preserve left and right actions; that is, we consider the maps $\sigma$ such that
+\begin{equation}
+	\sigma(rx) = r\sigma(x) \quad\text{and}\quad \sigma(xr) = \sigma(x)r \quad\text{for every $r \in R$ and $x \in \text{Domain } \sigma$}.
+	\label{eq:respect}
+\end{equation}
+These maps can be represented using diagrammatics, as below.
+
+\subsection{Diagrammatics of Maps}
+\label{sec:prelim_map}
+\newcommand{\DD}{\mathcal D}
+Certain maps between Bott-Samelson bimodules can be described in terms of diagrams.
+We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.
+A reader who is not interested in this context can simply accept on faith the relations specified in Section~\ref{sec:prelim_genrel}.
+
+Consider a category $\DD$ whose elements are linear combinations $\sum c_i \square$ of the diagrams described below.  The coefficients $c_i$ belong to the ring $\ZZ[x,y]$.
+
+The diagrams may be described as planar graphs, not necessarily connected, drawn in a rectangle, with the following properties.
+\begin{enumerate}[(i)]
+	\ii Vertices may lie on the upper or lower boundary, but not on the left or right boundary.
+	\ii Each vertex has degree $1$ or $3$.
+	\ii Each connected component is colored either blue or red.
+\end{enumerate}
+The vertices on the boundary are by convention not explicitly shown, but are nonetheless labelled $s$ or $t$ for blue or red, respectively.
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+	size(6cm);
+	real xmax=7;
+	real ymax=5;
+	draw( (xmax,ymax)--(xmax,-ymax)--(-xmax,-ymax)--(-xmax,ymax)--cycle );
+	pair apex = (0,2);
+	path arc = (5,-5)..(2,0)..apex..(-2,0)..(-5,-5);
+	draw(arc, blue);
+	dot(apex, blue);
+	draw(apex--(0,ymax), blue);
+	draw(-apex--(0,-ymax), red + dashed + 0.6);
+	dot(-apex, red);
+	label("$s$", (0,ymax), dir(90));
+	label("$t$", (0,-ymax), dir(270));
+	label("$s$", (-5,-ymax), dir(270));
+	label("$s$", (5,-ymax), dir(270));
+	\end{asy}
+	\caption{An example of a possible diagram.}
+	\label{fig:example_diagram}
+\end{figure}
+
+An example of such a diagram is shown in Figure~\ref{fig:example_diagram}.
+
+The elements of $\DD$ can be added by simply adding corresponding coefficients.
+Multiplication is defined as follows: the product of two diagrams is the composition of the diagrams if the labels on the bottom of the first coincide with those on the top of the second.
+Otherwise, the product is $0$.
+
+In \cite{basispf}, Khovanov and Elias show that all such maps can be expressed as a linear combination of these diagrams.
+
+\subsection{Algebraic Context}
+The maps are conventionally read from bottom to top.
+The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take -- for example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.
+An unlabelled domain corresponds to $R$.
+
+Let us hasten to introduce one final definition.
+\begin{definition*}
+	The \emph{Demazure operator} $\partial_s: R \to R$ is given by $\partial_s(f) = \frac{f - sf}{\alpha_s}$.
+\end{definition*}
+
+With this, we can now describe the meanings of each type of vertex (for blue lines) in Table~\ref{tab:prim_maps}.  The corresponding equations hold for red in $t$.
+
+\begin{table}[ht]
+	\[
+	\begin{array}{rll}
+		\text{Map} & \text{Modules} & \text{Description} \\[1em]
+		\barbell{half_top} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
+		\barbell{half_bot} & R \to R \stimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
+		\barbell{tri_down} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
+		\barbell{tri_up} & R \stimes R \stimes R \to R \stimes R & 1 \mid g \mid 1 \mapsto \partial_s(g) \mid 1 \\[1em]
+		\barbell{id} & R \stimes R \to R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \\[1em]
+	\end{array}
+	\]
+	\caption{Describing the maps.}
+	\label{tab:prim_maps}
+\end{table}
+
+Note that the descriptions are sufficient to determine outputs for all values because these morphisms respect left and right actions, as prescribed in \eqref{eq:respect}.
+
+Maps are composed by juxtaposition, and disjoint portions of the diagrams act independently.
+Therefore, by a combination of these structures, we can generate arbitrarily complicated maps.
+For example, the map in Figure~\ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d.
+\]
+
+Henceforth, we will make the convenient abbreviation of $\barbell{tri_up_contract_before}$ as $\barbell{tri_up_contract_after}$.
+It will also be understood that edges need not be straight lines, but any topologically equivalent deformation shall represent the same graph.
+With this understanding, any of the graphs described in the previous section can be viewed as compositions of the primitive structures we describe here.
+
+\subsection{Operations for Diagrammatics}
+\label{sec:prelim_genrel}
+From the algebraic context given above, one can derive the following relationships, which are here encoded completely graphically.  These rules are sufficient to compute the maps we are interested in.
+
+\setcounter{op}{-1}
+\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  \end{op}
+\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$ and the similar equation for red.  \end{op}
+\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$ and the similar equation for red.  \end{op}
+\begin{op}[The Needle] We have $\barbell{needle} = 0$.  Similarly, the red needle yields zero.  \end{op}
+\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well.
+In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.
+\end{remark*}
+\begin{op}[Barbell-Forcing Rules]
+	We have the following three equalities:
+	\begin{enumerate}[(a)]
+		\ii $\barbell{barbell_blue}\barbell{alpha_blue} + \barbell{alpha_blue} \barbell{barbell_blue} = 2 \barbell{break_blue}$, and the similar equation for red.
+		\ii $\barbell{alpha_red}\barbell{barbell_blue} = -x\barbell{break_red} + \barbell{barbell_blue}\barbell{alpha_red} + x \barbell{barbell_red}\barbell{alpha_red}$.
+		\ii $\barbell{alpha_blue}\barbell{barbell_red} = -y\barbell{break_blue} + \barbell{barbell_red}\barbell{alpha_blue} + y \barbell{barbell_blue}\barbell{alpha_blue}$.
+	\end{enumerate}
+\end{op}
+
+\subsection{Libedinsky's Light Leaves}
+\label{sec:prelim_lightleave}
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+	size(10cm);
+	real h = 0.7;
+	pen s = blue, t = dashed + red + 0.6;
+	int n = 14;
+	draw(currentpicture, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+	draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
+	draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
+	draw(currentpicture, (4,0)--(4,h/2)..((4+8)/2.0,h*4)..(8,h/2)--(8,0), t);
+	draw(currentpicture, (8,0)--(8,h/2)..((8+9)/2.0,h*1)..(9,h/2)--(9,0), t);
+	draw(currentpicture, (11,0)--(11,h/2)..((11+13)/2.0,h*2)..(13,h/2)--(13,0), t);
+	draw(currentpicture, (1,0)--(1,h), t);dot(currentpicture, (1,h), red);
+	draw(currentpicture, (7,0)--(7,h), s);dot(currentpicture, (7,h), s);
+	draw(currentpicture, (12,0)--(12,h), s);dot(currentpicture, (12,h), s);
+	draw(currentpicture,(9,0)--(9,5*h), t);
+	draw(currentpicture,(10,0)--(10,5*h), s);
+	dot(currentpicture, (2, h/2), blue);
+	dot(currentpicture, (8, h/2), red);
+	dot(currentpicture, (9, h/2), red);
+	label(currentpicture, "1", (0,-1.5h), dir(90));
+	label(currentpicture, "s", (0,-0.8*h), dir(90));
+	label(currentpicture, "0", (1,-1.5h), dir(90));
+	label(currentpicture, "t", (1,-0.8*h), dir(90));
+	label(currentpicture, "0", (2,-1.5h), dir(90));
+	label(currentpicture, "s", (2,-0.8*h), dir(90));
+	label(currentpicture, "1", (3,-1.5h), dir(90));
+	label(currentpicture, "s", (3,-0.8*h), dir(90));
+	label(currentpicture, "1", (4,-1.5h), dir(90));
+	label(currentpicture, "t", (4,-0.8*h), dir(90));
+	label(currentpicture, "1", (5,-1.5h), dir(90));
+	label(currentpicture, "s", (5,-0.8*h), dir(90));
+	label(currentpicture, "1", (6,-1.5h), dir(90));
+	label(currentpicture, "s", (6,-0.8*h), dir(90));
+	label(currentpicture, "0", (7,-1.5h), dir(90));
+	label(currentpicture, "s", (7,-0.8*h), dir(90));
+	label(currentpicture, "0", (8,-1.5h), dir(90));
+	label(currentpicture, "t", (8,-0.8*h), dir(90));
+	label(currentpicture, "0", (9,-1.5h), dir(90));
+	label(currentpicture, "t", (9,-0.8*h), dir(90));
+	label(currentpicture, "1", (10,-1.5h), dir(90));
+	label(currentpicture, "s", (10,-0.8*h), dir(90));
+	label(currentpicture, "1", (11,-1.5h), dir(90));
+	label(currentpicture, "t", (11,-0.8*h), dir(90));
+	label(currentpicture, "0", (12,-1.5h), dir(90));
+	label(currentpicture, "s", (12,-0.8*h), dir(90));
+	label(currentpicture, "1", (13,-1.5h), dir(90));
+	label(currentpicture, "t", (13,-0.8*h), dir(90));
+	\end{asy}
+	\caption{An example of light leaves.}
+	\label{fig:lightleaf_example}
+\end{figure}
+
+Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any binary string $\ul b$ of length $n$, we can construct a diagram based on a series of rules.
+
+Each bit of $\ul b$ is read from left to right in order and designated either up or down.
+We say that a bit $x$ is an \emph{open neighbor} of $y$ if $x$ is marked up, $x$ and $y$ have the same color, and there are no other bits marked up between $x$ and $y$.
+\begin{itemize}
+	\ii If the bit is a $1$:
+	\begin{itemize}
+		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, and mark both bits as down.
+		\ii Otherwise, designate the current bit as up.
+	\end{itemize}
+	\ii If the bit is $0$:
+	\begin{itemize}
+		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, mark the previous bit as down, and the current bit as up.
+		\ii Otherwise, create a ``stub'', i.e. a single vertex of degree one, and mark the current bit as down.
+	\end{itemize}
+\end{itemize}
+Finally, join any bits which are up at the end of the process to the opposite end.
+A map which arises in such a manner is called a \emph{light leaf}.
+An example of such a light leaf is shown in Figure~\ref{fig:lightleaf_example}.
+
+These light leaves are interesting because, in the seventh chapter of \cite{span}, it is shown that these light leaves form a ``basis'' in the sense that all maps may be expressed by compositions of these light leaves.
+
+\section{Proof of the One-Color Theorem}
+\label{sec:s_proof}
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(7cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 8;
+		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
+		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
+		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
+		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
+		draw(currentpicture, (4,0)--(4,h), s);
+		dot(currentpicture, (4,h), dot_s);
+		draw(currentpicture, (7,0)--(7,h), s);
+		dot(currentpicture, (7,h), dot_s);
+		dot(currentpicture, (1, h/2), dot_s);
+		dot(currentpicture, (2, h/2), dot_s);
+		label(currentpicture, "1", (0,-1.5h), dir(90));
+		label(currentpicture, "s", (0,-0.8*h), dir(90));
+		label(currentpicture, "0", (1,-1.5h), dir(90));
+		label(currentpicture, "s", (1,-0.8*h), dir(90));
+		label(currentpicture, "0", (2,-1.5h), dir(90));
+		label(currentpicture, "s", (2,-0.8*h), dir(90));
+		label(currentpicture, "1", (3,-1.5h), dir(90));
+		label(currentpicture, "s", (3,-0.8*h), dir(90));
+		label(currentpicture, "0", (4,-1.5h), dir(90));
+		label(currentpicture, "s", (4,-0.8*h), dir(90));
+		label(currentpicture, "1", (5,-1.5h), dir(90));
+		label(currentpicture, "s", (5,-0.8*h), dir(90));
+		label(currentpicture, "1", (6,-1.5h), dir(90));
+		label(currentpicture, "s", (6,-0.8*h), dir(90));
+		label(currentpicture, "0", (7,-1.5h), dir(90));
+		label(currentpicture, "s", (7,-0.8*h), dir(90));
+	\end{asy}
+	\caption{A half-map with base $\SS_8$.}
+	\label{fig:pf_trivial_theorem_example}
+\end{figure}
+
+\begin{proof}[Proof of Theorem \ref{thm:s_eval}]
+	We will only consider the case where $\Top(\ul a) = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.
+See Figure~\ref{fig:pf_trivial_theorem_example} for a example of such a map.
+
+	Number the anchors $1$, $2$, \dots from left to right.
+
+	For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.
+Note that the antennae of a component always form a single contiguous sequence of anchors.
+
+	The key observation is that for $1 \le i \le n-1$, we have that $\ul b^\ast[i] = 1$ if and only if $i$ and $i+1$ are both antennae of some component in $\MM(\ul b)$.  This follows by construction.
+
+	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$ to obtain a full-map.
+Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel} each other $k$ times if they have $k$ antennae in common.
+Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because the two antenna combine to form an empty bubble.
+Furthermore, it is easy to see that any bubbles must be formed in this manner.
+In combination with the claim above, this implies the first case of the theorem.
+
+	On the other hand, suppose this product is nonzero, and consider a component from the top with $k$ antennae.
+We claim that there are $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees; this would complete the proof, because each tree contracts to a barbell.
+Notice that $\pi_1(\ul a^\ast) + \pi_1(\ul b^\ast)$ counts the number of edges between adjacent anchors ($i$ and $i+1$).
+Because there are no cycles, deleting one of these edges increases the number of connected components by exactly one (since all the connected components are trees).
+If we delete all such edges, then we obtain $n$ barbells.
+Therefore there must have been $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees to begin with, as desired.
+\end{proof}
+
+\section{Proofs of Lemmata}
+\label{sec:lemmata_proof}
+\subsection{Proof of the Bubble Lemma}
+We begin with a proof of the Bubble Lemma\footnote{I should remark that attempting to construct counterexamples to the Bubble Lemma leads to a far better understanding than trying to read the following proof.}, which is the crux result of the alternating case.
+Indeed, both of the subsequent lemmas are fairly straightforward consequences of this one.
+
+\begin{proof}[Proof of Lemma \ref{thm:bubble}]
+	Take a bubble $B$ and assume without loss of generality that it is blue.
+It is easy to see, by considering two anchors on the boundary of blue, that there is some red anchor inside $B$.
+This implies that $B$ has at least one red caterpillar.
+
+	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.
+
+	Define a pair of red anchors $u, v$, with $u$ to the left of $v$, to be \emph{quasi-connected} if (i) one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect blue lines, and (ii) there is no red anchor $w$ strictly between $u$ and $v$ for which one can draw a similar arc on the same half-map joining $w$ and $v$.
+
+	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a single arc}.
+To prove this, take such a quasi-connected pair $u$ and $v$.
+Now we'll focus only on the half-map in which the prescribed arc is drawn.
+We thus may state that an arc \emph{shields} any anchors which lie between its endpoints.
+
+	\begin{figure}[ht]
+		\centering
+		\begin{asy}
+			size(6cm);
+			pen s = blue, t = red + dashed + 0.6;
+			pen dot_s = blue, dot_t = red;
+			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
+			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
+			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
+			draw((1,0)..(3,2)..(5,0), t); // red covering arc
+			draw((2,0)..(3,1)..(4,0), s); // blue covering arc again
+			label("$u$", (3,0), dir(-90));
+			label("$v$", (5,0), dir(-90));
+		\end{asy}
+		\hspace{2em}
+		\begin{asy}
+			size(6cm);
+			pen s = blue, t = red + dashed + 0.6;
+			pen dot_s = blue, dot_t = red;
+			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
+			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
+			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
+			draw((1,0)..(4,2)..(7,0), t); // red covering arc
+			draw((2,0)..(4,1)..(6,0), s); // blue covering arc
+			label("$u$", (3,0), dir(-90));
+			label("$v$", (5,0), dir(-90));
+		\end{asy}
+		\caption{Proving the bubble lemma with quasi-connected vertices.}
+		\label{fig:pf_bubble}
+	\end{figure}
+	Because the string is alternating, we can take a blue anchor $x$ immediately to the left of $v$.
+Now, there must be some blue arc shielding $u$ and $v$ (since $u,v$ are inside a blue bubble).
+By the light-leave construction, there must be some red arc $A$ covering $x$.
+If this arc joins $u$ and $v$, then we are done.
+	Otherwise, if it has endpoint $v$ then it must completely cover $u$ by condition (ii) of quasi-connectedness; if not, then it must completely cover $v$.  This leads us to two cases.
+	\begin{itemize}
+		\ii If the arc covers exactly one of $u$ or $v$, say $u$, then there must be a blue arc shielding $u$ from $A$.
+But then this contradicts the quasi-connectedness, because now it is not possible to join $u$ and $v$ by an arc on this half-map.
+This case is illustrated by the left half of Figure~\ref{fig:pf_bubble}.
+		\ii If the arc covers both $u$ and $v$, then there must be a blue arc which shields both $u$ and $v$, which is itself shielded by $A$.
+Then we can repeat the same procedure with this new blue arc.
+This case is illustrated by the right half of Figure~\ref{fig:pf_bubble}.
+	\end{itemize}
+	Therefore any pair of quasi-connected anchors must be connected by an arc.
+However, one can verify that the red anchors in $B$ but not in any other blue bubble are ``connected'' under quasi-connectedness.\footnote{That is, one can follow a sequence of red anchors, each consecutive pair quasi-connected, from any red anchor to any other red anchor.}  Therefore all such red anchors must be connected.
+So there is a single caterpillar, as desired.
+\end{proof}
+
+\subsection{Proof of the Caterpillar Lemma}
+We will now derive the Caterpillar Lemma as a consequence of the Bubble Lemma.
+
+First, a few definitions for this section only.
+\begin{definition*}
+	Consider a caterpillar $C$ in a full-diagram with base $\AA_n$.
+Define the \emph{nesting level} of the caterpillar as the largest integer $n$ for which there exists caterpillars $C = C_0$, $C_1$, $C_2$, $\dots$, $C_n$ such that $C_i$ holds $C_{i+1}$ for each $i=0,1,\dots,n-1$.
+Define the \emph{size} of the caterpillar to be the number of bubbles it contains.
+\end{definition*}
+
+\begin{proof}[Proof of Lemma \ref{thm:caterpillar}]
+	The proof is by double induction.  First we will consider caterpillars with nesting level $0$.
+
+	We perform induction on the size of the caterpillar. 
+	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
+	This is the base step.
+	For the inductive step, consider an arbitrary bubble.
+Inside it is exactly one caterpillar, say $c$, by the Bubble Lemma.
+Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
+	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms.
+One of them is zero because it creates a new empty bubble.
+The other is the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.
+The inductive hypothesis now applies directly, and this completes the first induction.
+
+	Now suppose a caterpillar has nesting level $k \ge 1$.
+We simply apply the exact same induction on size as before.
+The only modification is that, instead of a barbell, we have a caterpillar with nesting level strictly less than $k$.
+However, these caterpillars all evaluate as a polynomial again of the form $x^my^n \alpha_s$ or $x^my^n\alpha_t$, by the outer inductive hypothesis.
+So applying equation \eqref{eq:barbell_break} in the same manner completes this induction as well.
+\end{proof}
+
+\subsection{Proof of the Pasture Lemma}
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(11cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 6;
+
+		picture before;
+		draw(before, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
+		draw(before, (2,0)--(2,h), s);
+		dot(before, (2,h), dot_s);
+		draw(before, (5,0)--(5,h), t);
+		dot(before, (5,h), dot_t);
+		draw(before,(0,0)--(0,3*h), s);
+		draw(before,(3,0)--(3,3*h), t);
+		draw(before,(4,0)--(4,3*h), s);
+		dot(before, (3, h/2), dot_t);
+
+		add(before); add(reflect((0,0),(1,0))*before);
+		draw((-1,0)--(6,0));
+
+		picture after;
+		draw(after, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
+		draw(after, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), s);
+		draw(after, (3,0)--(3,h/2)..((3+7)/2.0,h*4)..(7,h/2)--(7,0), t);
+		draw(after, (0,0)--(0,h/2)..((0+8)/2.0,h*5.5)..(8,h/2)--(8,0), s);
+		draw(after, (2,0)--(2,h), s);
+		dot(after, (2,h), dot_s);
+		draw(after, (5,0)--(5,h), t);
+		dot(after, (5,h), dot_t);
+		dot(after, (3, h/2), dot_t);
+
+		add(shift((9,0)) * after);
+		add(shift((9,0)) * reflect((0,0),(1,0))*after);
+		draw((8,0)--(18,0));
+
+		label("$\to$", (7,0));
+	\end{asy}
+	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Lemma from the Bubble Lemma.}
+	\label{fig:pf_pasture}
+\end{figure}
+The Bubble Lemma and the Pasture Lemma are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Lemma follows from the Bubble Lemma.
+\begin{proof}[Proof of Lemma \ref{thm:pasture}]
+	Again, let $T$ denote the top, with length $N$.
+In the first case, suppose $T[N] \neq \AA_n[n]$; that is, the last characters of $T$ and $\AA_n$ differ.
+Then it must be the case that the rightmost anchor is not part of a fence.
+	Now suppose the map arose from $\MM_{\AA_n}(\ul a, \ul b)$.
+Let $\ul a'$ be the string formed by appending $N$ $1$'s to $\ul a$, and define $\ul b'$ similarly.
+Now consider the map \[ \MM_{\AA_{n+N}} \left( \ul a', \ul b' \right).
+\]  See Figure~\ref{fig:pf_pasture} for an example.
+
+	It is easy to verify that the top of this new map is zero.
+Now what we have done is enclose the contents of each pasture into bubbles.
+The Bubble Lemma tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.
+This implies the Pasture Lemma in the first case.
+
+	The case where $T[N] = \AA_n[n]$ is similar.
+We simply append a zero followed by $N$ $1$'s and repeat the same procedure.
+The only difference is that the innermost barbell was generated by the $0$ we appended, and thus was not part of the original diagram.
+\end{proof}
+
+\section{Proof of the Alternating Recursion}
+\label{sec:recurse_proof}
+\begin{proof}[Proof of Proposition \ref{thm:recurse}]
+	We will only resolve the case where $n$ is odd; that is, $\AA_n$ terminates in $s$.  The other case is identical.
+	\begin{enumerate}[(i)]
+		\ii Suppose $\ul a[n] = \ul b[n] = 0$.  Note that the top of $M_1$ is also $T$.
+		\begin{itemize}
+			\ii If $T = \varnothing$, then $M_1$ also had top $\varnothing$.
+Therefore, the addition of the $0$'s at the end simply generates an extra blue barbell.
+So the resulting map is simply a multiple by $\alpha_s$.
+			\ii The case where $T$ ends in $t$ is analogous; we simply obtain a new barbell.  However, because $T \neq \emptyset$, the extra factor is $Q_T$ instead of simply $\alpha_t$. 
+			\begin{figure}[ht]
+				\centering
+				\begin{asy}
+					size(12cm);
+					real h = 0.7;
+					pen s = blue, t = red + dashed + 0.6;
+					pen dot_s = blue, dot_t = red;
+					int n = 4;
+
+					picture one;
+					draw(one, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+					draw(one, (1,0)--(1,h), t);
+					dot(one, (1,h), dot_t);
+					draw(one, (3,0)--(3,h), t);
+					dot(one, (3,h), dot_t);
+					draw(one,(2,0)--(2,3*h), s);
+					dot(one, (2, h/2), dot_s);
+
+					picture two;
+					draw(two, (0,0)--(0,h), s);
+					dot(two, (0,h), dot_s);
+					draw(two, (1,0)--(1,h), t);
+					dot(two, (1,h), dot_t);
+					draw(two, (3,0)--(3,h), t);
+					dot(two, (3,h), dot_t);
+					draw(two,(2,0)--(2,3*h), s);
+
+					add(one); add(reflect((0,0),(1,0))*two);
+					draw((-1,0)--(4,0));
+
+					int n = 5;
+
+					picture three;
+					draw(three, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+					draw(three, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(three, (1,0)--(1,h), t);
+					dot(three, (1,h), dot_t);
+					draw(three, (3,0)--(3,h), t);
+					dot(three, (3,h), dot_t);
+					draw(three,(4,0)--(4,3*h), s);
+					dot(three, (2, h/2), dot_s);
+					dot(three, (4, h/2), dot_s);
+
+					picture four;
+					draw(four, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(four, (0,0)--(0,h), s);
+					dot(four, (0,h), dot_s);
+					draw(four, (1,0)--(1,h), t);
+					dot(four, (1,h), dot_t);
+					draw(four, (3,0)--(3,h), t);
+					dot(four, (3,h), dot_t);
+					draw(four,(4,0)--(4,3*h), s);
+					dot(four, (4, h/2), dot_s);
+
+					add(shift((7,0)) * three); add(shift((7,0)) * reflect((0,0),(1,0))*four);
+					draw((7-1,0)--(7+5,0));
+					MP("\to", (5,0), (0,0));
+				\end{asy}
+				\caption{Enclosing a caterpillar in an attached component.}
+				\label{fig:recurse_example_destr_zero}
+			\end{figure}
+			\ii Now suppose $T$ ends in $s$.
+Then the addition of the $0$'s resulted in enclosing a caterpillar of $M_1$ in an attached bubble, as per Figure~\ref{fig:recurse_example_destr_zero}.
+Breaking out of the additional blue loop nows adds a factor of $x$, but the red caterpillar is annihilated in the process; therefore, only the fluff remains, because there is nothing to push through the fences.
+		\end{itemize}
+		\ii Now suppose that $\ul a[n] = \ul b[n] = 1$.
+		\begin{itemize}
+			\ii First, suppose $T$ ends in $s$.
+Then the additional $1$'s added simply create a fence on the far right, because there is no ``up'' blue anchors to interact with.
+Because this fence is already on the far right, it does not affect the product, hence $M = M_1$.
+			\begin{figure}[ht]
+				\centering
+				\begin{asy}
+					size(11cm);
+					real h = 0.7;
+					pen s = blue, t = red + dashed + 0.6;
+					pen dot_s = blue, dot_t = red;
+					int n = 4;
+
+					picture one;
+					draw(one, (0,0)--(0,h), s);
+					dot(one, (0,h), dot_s);
+					draw(one, (3,0)--(3,h), t);
+					dot(one, (3,h), dot_t);
+					draw(one,(1,0)--(1,3*h), t);
+					draw(one,(2,0)--(2,3*h), s);
+
+					picture two;
+					draw(two, (0,0)--(0,h), s);
+					dot(two, (0,h), dot_s);
+					draw(two, (3,0)--(3,h), t);
+					dot(two, (3,h), dot_t);
+					draw(two,(1,0)--(1,3*h), t);
+					draw(two,(2,0)--(2,3*h), s);
+
+					add(one); add(reflect((0,0),(1,0))*two);
+					draw((-1,0)--(4,0));
+
+					int n = 5;
+
+					picture three;
+					draw(three, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(three, (0,0)--(0,h), s);
+					dot(three, (0,h), dot_s);
+					draw(three, (3,0)--(3,h), t);
+					dot(three, (3,h), dot_t);
+					draw(three,(1,0)--(1,3*h), t);
+
+					picture four;
+					draw(four, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
+					draw(four, (0,0)--(0,h), s);
+					dot(four, (0,h), dot_s);
+					draw(four, (3,0)--(3,h), t);
+					dot(four, (3,h), dot_t);
+					draw(four,(1,0)--(1,3*h), t);
+
+					add(shift((7,0)) * three); add(shift((7,0)) * reflect((0,0),(1,0)) * four);
+					draw((7-1,0)--(7+5,0));
+					MP("\to", (5,0), (0,0));
+				\end{asy}
+				\caption{Enclosing a caterpillar in a free component.}
+				\label{fig:recurse_example_destr_one}
+			\end{figure}
+			\ii Conversely, suppose that $T$ ends in $t$.   See Figure \ref{fig:recurse_example_destr_one} for an example.
+
+			In that case, $M_1$ must have had the top $T$ with an $s$ appended.
+Once again, we find that the red caterpillar from $M_1$ is enclosed in a bubble.
+This time, however, the bubble is not attached.
+Therefore, while we still obtain the extra factor of $x$ and the caterpillar is still removed, we remain with a blue barbell on the far right pasture.
+So we must push this blue barbell through $T$.
+This adds a factor of $Q_T$, and so we obtain the desired form $-xF Q_T$.
+			\ii The case where $T = \varnothing$ is analogous to the previous case; in a sense, we merely have a degenerate $Q_\varnothing = \alpha_s$.
+Specifically, the blue barbell is already on the correct pasture, so we simply add a factor of $\alpha_s$.
+		\end{itemize}
+	\end{enumerate}
+	This exhausts all the cases in the proposition, hence we're done.
+\end{proof}
+
+\section{Complete Product Matrix for ststs}
+For reference, here is a complete product matrix for maps with base $ststs$.  The blank entries are $0$ maps.  The top is recorded as the title of each table.
+
+\begin{tabular}{|l||l|}
+\hline
+stst & 11110 \\ \hline
+11110
+& $[5]\alpha_s+[4]_y\alpha_t$ % 11110 x 11110
+\\ \hline
+\end{tabular}
+%
+\begin{tabular}{|l||l|}
+\hline
+ststs & 11111 \\ \hline
+11111
+& $1$ % 11111 x 11111
+\\ \hline
+\end{tabular}
+%
+\begin{tabular}{|l||l|}
+\hline
+tst & 01110 \\ \hline
+01110
+& $[3]\alpha_s^2+[4]_y\alpha_s\alpha_t$ % 01110 x 01110
+\\ \hline
+\end{tabular}
+%
+\begin{tabular}{|l||l|}
+\hline
+tsts & 01111 \\ \hline
+01111
+& $\alpha_s$ % 01111 x 01111
+\\ \hline
+\end{tabular}
+
+\begin{longtable}{|l||p{3.14cm}|p{3.14cm}|p{3.14cm}|p{3.14cm}|}
+\hline
+ts & 01100 & 01001 & 00011 & 10111 \\ \hline
+\endfirsthead
+ts & 01100 & 01001 & 00011 & 10111 \\ \hline
+\endhead
+\endfoot
+\hline
+\endlastfoot
+01100
+& $-[2]_x\alpha_s$ % 01100 x 01100
+& $\alpha_s$ % 01100 x 01001
+&  % 01100 x 00011
+&  % 01100 x 10111
+\\
+01001
+& $\alpha_s$ % 01001 x 01100
+& $-[2]_y\alpha_s$ % 01001 x 01001
+& $\alpha_s^2$ % 01001 x 00011
+& $\alpha_s$ % 01001 x 10111
+\\
+00011
+&  % 00011 x 01100
+& $\alpha_s^2$ % 00011 x 01001
+& $\alpha_s^2\alpha_t$ % 00011 x 00011
+& $\alpha_s\alpha_t$ % 00011 x 10111
+\\
+10111
+&  % 10111 x 01100
+& $\alpha_s$ % 10111 x 01001
+& $\alpha_s\alpha_t$ % 10111 x 00011
+& $-[2]_x\alpha_s$ % 10111 x 10111
+\\
+\end{longtable}
+
+\begin{longtable}{|l||p{3.14cm}|p{3.14cm}|p{3.14cm}|p{3.14cm}|}
+\hline
+st & 11000 & 10010 & 00110 & 11101 \\ \hline
+\endfirsthead
+st & 11000 & 10010 & 00110 & 11101 \\ \hline
+\endhead
+\endfoot
+\hline
+\endlastfoot
+11000
+& $-[2]_y[3]\alpha_s-[2]_y[2]_y\alpha_t$ % 11000 x 11000
+& $[3]\alpha_s+[2]_y\alpha_t$ % 11000 x 10010
+&  % 11000 x 00110
+& $[3]\alpha_s+[2]_y\alpha_t$ % 11000 x 11101
+\\
+10010
+& $[3]\alpha_s+[2]_y\alpha_t$ % 10010 x 11000
+& $-[2]_x[3]\alpha_s-[2]_x[2]_y\alpha_t$ % 10010 x 10010
+& $[3]\alpha_s\alpha_t+[2]_y\alpha_t^2$ % 10010 x 00110
+&  % 10010 x 11101
+\\
+00110
+&  % 00110 x 11000
+& $[3]\alpha_s\alpha_t+[2]_y\alpha_t^2$ % 00110 x 10010
+& $[3]\alpha_s^2\alpha_t+[2]_y\alpha_s\alpha_t^2$ % 00110 x 00110
+&  % 00110 x 11101
+\\
+11101
+& $[3]\alpha_s+[2]_y\alpha_t$ % 11101 x 11000
+&  % 11101 x 10010
+&  % 11101 x 00110
+& $-[2]_x[3]\alpha_s-[2]_x[2]_y\alpha_t$ % 11101 x 11101
+\\
+\end{longtable}
+
+\begin{longtable}{|l||p{3.14cm}|p{3.14cm}|p{3.14cm}|p{3.14cm}|}
+\hline
+t & 01000 & 00010 & 10110 & 01101 \\ \hline
+\endfirsthead
+t & 01000 & 00010 & 10110 & 01101 \\ \hline
+\endhead
+\endfoot
+\hline
+\endlastfoot
+01000
+& $-[2]_y\alpha_s^2-[2]_y[2]_y\alpha_s\alpha_t$ % 01000 x 01000
+& $\alpha_s^3+[2]_y\alpha_s^2\alpha_t$ % 01000 x 00010
+& $\alpha_s^2+[2]_y\alpha_s\alpha_t$ % 01000 x 10110
+& $\alpha_s^2+[2]_y\alpha_s\alpha_t$ % 01000 x 01101
+\\
+00010
+& $\alpha_s^3+[2]_y\alpha_s^2\alpha_t$ % 00010 x 01000
+& $\alpha_s^3\alpha_t+[2]_y\alpha_s^2\alpha_t^2$ % 00010 x 00010
+& $\alpha_s^2\alpha_t+[2]_y\alpha_s\alpha_t^2$ % 00010 x 10110
+&  % 00010 x 01101
+\\
+10110
+& $\alpha_s^2+[2]_y\alpha_s\alpha_t$ % 10110 x 01000
+& $\alpha_s^2\alpha_t+[2]_y\alpha_s\alpha_t^2$ % 10110 x 00010
+& $-[2]_x\alpha_s^2-[2]_x[2]_y\alpha_s\alpha_t$ % 10110 x 10110
+&  % 10110 x 01101
+\\
+01101
+& $\alpha_s^2+[2]_y\alpha_s\alpha_t$ % 01101 x 01000
+&  % 01101 x 00010
+&  % 01101 x 10110
+& $-[2]_x\alpha_s^2-[2]_x[2]_y\alpha_s\alpha_t$ % 01101 x 01101
+\\
+\end{longtable}
+
+\begin{longtable}{|l||p{3.14cm}|p{3.14cm}|p{3.14cm}|p{3.14cm}|}
+\hline
+sts & 11100 & 11001 & 10011 & 00111 \\ \hline
+\endfirsthead
+sts & 11100 & 11001 & 10011 & 00111 \\ \hline
+\endhead
+\endfoot
+\hline
+\endlastfoot
+11100
+& $-[2]_x$ % 11100 x 11100
+& $1$ % 11100 x 11001
+&  % 11100 x 10011
+&  % 11100 x 00111
+\\
+11001
+& $1$ % 11001 x 11100
+& $-[2]_y$ % 11001 x 11001
+& $1$ % 11001 x 10011
+&  % 11001 x 00111
+\\
+10011
+&  % 10011 x 11100
+& $1$ % 10011 x 11001
+& $-[2]_x$ % 10011 x 10011
+& $\alpha_t$ % 10011 x 00111
+\\
+00111
+&  % 00111 x 11100
+&  % 00111 x 11001
+& $\alpha_t$ % 00111 x 10011
+& $\alpha_s\alpha_t$ % 00111 x 00111
+\\
+\end{longtable}
+
+\begin{longtable}{|l||p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|}
+\hline
+$\varnothing$ & 00000 & 10100 & 01010 & 10001 & 00101 & 11011 \\ \hline
+\endfirsthead
+$\varnothing$ & 00000 & 10100 & 01010 & 10001 & 00101 & 11011 \\ \hline
+\endhead
+\endfoot
+\hline
+\endlastfoot
+00000
+& $\alpha_s^3\alpha_t^2$ % 00000 x 00000
+& $\alpha_s^2\alpha_t^2$ % 00000 x 10100
+& $\alpha_s^3\alpha_t$ % 00000 x 01010
+& $\alpha_s\alpha_t^2$ % 00000 x 10001
+& $\alpha_s^2\alpha_t^2$ % 00000 x 00101
+& $\alpha_s^2\alpha_t$ % 00000 x 11011
+\\
+10100
+& $\alpha_s^2\alpha_t^2$ % 10100 x 00000
+& $-[2]_x\alpha_s^2\alpha_t$ % 10100 x 10100
+& $\alpha_s^2\alpha_t$ % 10100 x 01010
+& $-[2]_x\alpha_s\alpha_t$ % 10100 x 10001
+& $\alpha_s\alpha_t^2$ % 10100 x 00101
+& $\alpha_s\alpha_t$ % 10100 x 11011
+\\
+01010
+& $\alpha_s^3\alpha_t$ % 01010 x 00000
+& $\alpha_s^2\alpha_t$ % 01010 x 10100
+& $-[2]_y\alpha_s^2\alpha_t$ % 01010 x 01010
+& $\alpha_s\alpha_t$ % 01010 x 10001
+& $\alpha_s^2\alpha_t$ % 01010 x 00101
+& $-[2]_y\alpha_s\alpha_t$ % 01010 x 11011
+\\
+10001
+& $\alpha_s\alpha_t^2$ % 10001 x 00000
+& $-[2]_x\alpha_s\alpha_t$ % 10001 x 10100
+& $\alpha_s\alpha_t$ % 10001 x 01010
+& $[2]_x[2]_x\alpha_s$ % 10001 x 10001
+& $-[2]_x\alpha_s\alpha_t$ % 10001 x 00101
+& $-[2]_x\alpha_s$ % 10001 x 11011
+\\
+00101
+& $\alpha_s^2\alpha_t^2$ % 00101 x 00000
+& $\alpha_s\alpha_t^2$ % 00101 x 10100
+& $\alpha_s^2\alpha_t$ % 00101 x 01010
+& $-[2]_x\alpha_s\alpha_t$ % 00101 x 10001
+& $-[2]_x\alpha_s^2\alpha_t$ % 00101 x 00101
+& $\alpha_s\alpha_t$ % 00101 x 11011
+\\
+11011
+& $\alpha_s^2\alpha_t$ % 11011 x 00000
+& $\alpha_s\alpha_t$ % 11011 x 10100
+& $-[2]_y\alpha_s\alpha_t$ % 11011 x 01010
+& $-[2]_x\alpha_s$ % 11011 x 10001
+& $\alpha_s\alpha_t$ % 11011 x 00101
+& $[2]_x[2]_y\alpha_s$ % 11011 x 11011
+\\
+\end{longtable}
+
+\begin{longtable}{|l||p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|}
+\hline
+s & 10000 & 00100 & 11010 & 00001 & 10101 & 01011 \\ \hline
+\endfirsthead
+s & 10000 & 00100 & 11010 & 00001 & 10101 & 01011 \\ \hline
+\endhead
+\endfoot
+\hline
+\endlastfoot
+10000
+& $[2]_x[2]_x$ % 10000 x 10000
+& $-[2]_x\alpha_t$ % 10000 x 00100
+& $-[2]_x$ % 10000 x 11010
+& $\alpha_t^2$ % 10000 x 00001
+& $-[2]_x\alpha_t$ % 10000 x 10101
+& $\alpha_t$ % 10000 x 01011
+\\
+00100
+& $-[2]_x\alpha_t$ % 00100 x 10000
+& $-[2]_x\alpha_s\alpha_t$ % 00100 x 00100
+& $\alpha_t$ % 00100 x 11010
+& $\alpha_s\alpha_t^2$ % 00100 x 00001
+& $\alpha_t^2$ % 00100 x 10101
+& $\alpha_s\alpha_t$ % 00100 x 01011
+\\
+11010
+& $-[2]_x$ % 11010 x 10000
+& $\alpha_t$ % 11010 x 00100
+& $[2]_x[2]_y$ % 11010 x 11010
+& $\alpha_s\alpha_t$ % 11010 x 00001
+& $\alpha_t$ % 11010 x 10101
+& $-[2]_y\alpha_t$ % 11010 x 01011
+\\
+00001
+& $\alpha_t^2$ % 00001 x 10000
+& $\alpha_s\alpha_t^2$ % 00001 x 00100
+& $\alpha_s\alpha_t$ % 00001 x 11010
+& $\alpha_s^2\alpha_t^2$ % 00001 x 00001
+& $\alpha_s\alpha_t^2$ % 00001 x 10101
+& $\alpha_s^2\alpha_t$ % 00001 x 01011
+\\
+10101
+& $-[2]_x\alpha_t$ % 10101 x 10000
+& $\alpha_t^2$ % 10101 x 00100
+& $\alpha_t$ % 10101 x 11010
+& $\alpha_s\alpha_t^2$ % 10101 x 00001
+& $-[2]_x\alpha_s\alpha_t$ % 10101 x 10101
+& $\alpha_s\alpha_t$ % 10101 x 01011
+\\
+01011
+& $\alpha_t$ % 01011 x 10000
+& $\alpha_s\alpha_t$ % 01011 x 00100
+& $-[2]_y\alpha_t$ % 01011 x 11010
+& $\alpha_s^2\alpha_t$ % 01011 x 00001
+& $\alpha_s\alpha_t$ % 01011 x 10101
+& $-[2]_y\alpha_s\alpha_t$ % 01011 x 01011
+\\
+\end{longtable}
+
+% \end{document}
+\section{GitHub Repository}
+For the project, I wrote several scripts to produce and/or compute diagrams.  The source code can be checked out here: \url{https://github.com/vEnhance/lightleaves}.

### 2013-07-27 paper.tex
fail
Yay appendices.

@@
 \label{sec:prelim}
-In Section~\ref{sec:prelim_background}, we provide the background behind the Bott-Samelson bimodules, and the correspondence between these maps and certain diagrams.
+In Appendix~\ref{sec:prelim_background}, we provide the background behind the Bott-Samelson bimodules, and the correspondence between these maps and certain diagrams.
 We then introduce Libedinsky's light leaves, a basis by which maps can be constructed using binary strings.
@@
 The actual problem statement is then deferred to \ref{sec:probstate}.
-\subsection{An Extended Background}
-\label{sec:prelim_background}
-Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be arbitrary vectors normal to these planes.
-We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.
-In other words, $W$ is the infinite dihedral group with the presentation \[ W = \left<s,t \mid s^2=t^2=1\right>.
-\]
-
-If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then for any $a \in V$, reflection over the hyperplane normal to $a$ can be written explicitly for each $v \in V$ as the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a.
-\]
-In particular, if $W$ acts on $V$ by this reflection, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.
-Furthermore, using the above, we see that there exist fixed constants $x$ and $y$ such that
-\begin{align*}
-	s(\alpha_t) &= \alpha_t + x \alpha_s \\
-	t(\alpha_s) &= \alpha_s + y \alpha_t
-\end{align*}
-Explicitly, $x = \frac{-2(\alpha_s,\alpha_t)}{(\alpha_s, \alpha_s)}$ and $y = \frac{-2(\alpha_t,\alpha_s)}{(\alpha_t,\alpha_t)}$.
-Note that $x=y$ if $\left\lvert \alpha_s \right\rvert = \left\lvert \alpha_t \right\rvert$.
-
-Now we define the \emph{Coxeter ring} by $R = \RR[\alpha_s, \alpha_t]$.  Then $W$ acts on $R$ by precisely the same algorithm as described above.
-
-Let $R^s$ be the subring of $R$ which is invariant under $s$.  Define $R^t$ similarly.  Then a \emph{Bott-Samelson bimodule} is a bimodule of the form
-\[ R \otimes_{R^{i_1}} R \otimes_{R^{i_2}} R \otimes_{R^{i_3}} \dots \otimes_{R^{i_n}} R, \]
-where each $i_j$ is either $s$ or $t$.   Elements of such a bimodule will be written in the form $f_0 \mid f_1 \mid \dots \mid f_n$, where $f_i \in R$.
-
-We will consider maps between these bimodules that preserve left and right actions; that is, we consider the maps $\sigma$ such that
-\begin{equation}
-	\sigma(rx) = r\sigma(x) \quad\text{and}\quad \sigma(xr) = \sigma(x)r \quad\text{for every $r \in R$ and $x \in \text{Domain } \sigma$}.
-	\label{eq:respect}
-\end{equation}
-These maps can be represented using diagrammatics, as below.
-
-\subsubsection{Diagrammatics of Maps}
-\label{sec:prelim_map}
-\newcommand{\DD}{\mathcal D}
-Certain maps between Bott-Samelson bimodules can be described in terms of diagrams.
-We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.
-A reader who is not interested in this context can simply accept on faith the relations specified in Section~\ref{sec:prelim_genrel}.
-
-Consider a category $\DD$ whose elements are linear combinations $\sum c_i \square$ of the diagrams described below.  The coefficients $c_i$ belong to the ring $\ZZ[x,y]$.
-
-The diagrams may be described as planar graphs, not necessarily connected, drawn in a rectangle, with the following properties.
-\begin{enumerate}[(i)]
-	\ii Vertices may lie on the upper or lower boundary, but not on the left or right boundary.
-	\ii Each vertex has degree $1$ or $3$.
-	\ii Each connected component is colored either blue or red.
-\end{enumerate}
-The vertices on the boundary are by convention not explicitly shown, but are nonetheless labelled $s$ or $t$ for blue or red, respectively.
-
-\begin{figure}[ht]
-	\centering
-	\begin{asy}
-	size(6cm);
-	real xmax=7;
-	real ymax=5;
-	draw( (xmax,ymax)--(xmax,-ymax)--(-xmax,-ymax)--(-xmax,ymax)--cycle );
-	pair apex = (0,2);
-	path arc = (5,-5)..(2,0)..apex..(-2,0)..(-5,-5);
-	draw(arc, blue);
-	dot(apex, blue);
-	draw(apex--(0,ymax), blue);
-	draw(-apex--(0,-ymax), red + dashed + 0.6);
-	dot(-apex, red);
-	label("$s$", (0,ymax), dir(90));
-	label("$t$", (0,-ymax), dir(270));
-	label("$s$", (-5,-ymax), dir(270));
-	label("$s$", (5,-ymax), dir(270));
-	\end{asy}
-	\caption{An example of a possible diagram.}
-	\label{fig:example_diagram}
-\end{figure}
-
-An example of such a diagram is shown in Figure~\ref{fig:example_diagram}.
-
-The elements of $\DD$ can be added by simply adding corresponding coefficients.
-Multiplication is defined as follows: the product of two diagrams is the composition of the diagrams if the labels on the bottom of the first coincide with those on the top of the second.
-Otherwise, the product is $0$.
-
-In \cite{basispf}, Khovanov and Elias show that all such maps can be expressed as a linear combination of these diagrams.
-
-\subsubsection{Algebraic Context}
-The maps are conventionally read from bottom to top.
-The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take -- for example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.
-An unlabelled domain corresponds to $R$.
-
-Let us hasten to introduce one final definition.
-\begin{definition*}
-	The \emph{Demazure operator} $\partial_s: R \to R$ is given by $\partial_s(f) = \frac{f - sf}{\alpha_s}$.
-\end{definition*}
-
-With this, we can now describe the meanings of each type of vertex (for blue lines) in Table~\ref{tab:prim_maps}.  The corresponding equations hold for red in $t$.
-
-\begin{table}[ht]
-	\[
-	\begin{array}{rll}
-		\text{Map} & \text{Modules} & \text{Description} \\[1em]
-		\barbell{half_top} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
-		\barbell{half_bot} & R \to R \stimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
-		\barbell{tri_down} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
-		\barbell{tri_up} & R \stimes R \stimes R \to R \stimes R & 1 \mid g \mid 1 \mapsto \partial_s(g) \mid 1 \\[1em]
-		\barbell{id} & R \stimes R \to R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \\[1em]
-	\end{array}
-	\]
-	\caption{Describing the maps.}
-	\label{tab:prim_maps}
-\end{table}
-
-Note that the descriptions are sufficient to determine outputs for all values because these morphisms respect left and right actions, as prescribed in \eqref{eq:respect}.
-
-Maps are composed by juxtaposition, and disjoint portions of the diagrams act independently.
-Therefore, by a combination of these structures, we can generate arbitrarily complicated maps.
-For example, the map in Figure~\ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d.
-\]
-
-Henceforth, we will make the convenient abbreviation of $\barbell{tri_up_contract_before}$ as $\barbell{tri_up_contract_after}$.
-It will also be understood that edges need not be straight lines, but any topologically equivalent deformation shall represent the same graph.
-With this understanding, any of the graphs described in the previous section can be viewed as compositions of the primitive structures we describe here.
-
-\subsubsection{Operations for Diagrammatics}
-\label{sec:prelim_genrel}
-From the algebraic context given above, one can derive the following relationships, which are here encoded completely graphically.  These rules are sufficient to compute the maps we are interested in.
-
-\setcounter{op}{-1}
-\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  \end{op}
-\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$ and the similar equation for red.  \end{op}
-\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$ and the similar equation for red.  \end{op}
-\begin{op}[The Needle] We have $\barbell{needle} = 0$.  Similarly, the red needle yields zero.  \end{op}
-\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well.
-In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.
-\end{remark*}
-\begin{op}[Barbell-Forcing Rules]
-	We have the following three equalities:
-	\begin{enumerate}[(a)]
-		\ii $\barbell{barbell_blue}\barbell{alpha_blue} + \barbell{alpha_blue} \barbell{barbell_blue} = 2 \barbell{break_blue}$, and the similar equation for red.
-		\ii $\barbell{alpha_red}\barbell{barbell_blue} = -x\barbell{break_red} + \barbell{barbell_blue}\barbell{alpha_red} + x \barbell{barbell_red}\barbell{alpha_blue}$.
-		\ii $\barbell{alpha_blue}\barbell{barbell_red} = -y\barbell{break_blue} + \barbell{barbell_red}\barbell{alpha_blue} + y \barbell{barbell_blue}\barbell{alpha_red}$.
-	\end{enumerate}
-\end{op}
-
-% Furthermore, one can again verify that $\barbell{barbell_blue}$, when on the far left, is simply $\alpha_s$.
-
-\subsubsection{Libedinsky's Light Leaves}
-\label{sec:prelim_lightleave}
-\begin{figure}[ht]
-	\centering
-	\begin{asy}
-	size(10cm);
-	real h = 0.7;
-	pen s = blue, t = dashed + red + 0.6;
-	int n = 14;
-	draw(currentpicture, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
-	draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
-	draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
-	draw(currentpicture, (4,0)--(4,h/2)..((4+8)/2.0,h*4)..(8,h/2)--(8,0), t);
-	draw(currentpicture, (8,0)--(8,h/2)..((8+9)/2.0,h*1)..(9,h/2)--(9,0), t);
-	draw(currentpicture, (11,0)--(11,h/2)..((11+13)/2.0,h*2)..(13,h/2)--(13,0), t);
-	draw(currentpicture, (1,0)--(1,h), t);dot(currentpicture, (1,h), red);
-	draw(currentpicture, (7,0)--(7,h), s);dot(currentpicture, (7,h), s);
-	draw(currentpicture, (12,0)--(12,h), s);dot(currentpicture, (12,h), s);
-	draw(currentpicture,(9,0)--(9,5*h), t);
-	draw(currentpicture,(10,0)--(10,5*h), s);
-	dot(currentpicture, (2, h/2), blue);
-	dot(currentpicture, (8, h/2), red);
-	dot(currentpicture, (9, h/2), red);
-	label(currentpicture, "1", (0,-1.5h), dir(90));
-	label(currentpicture, "s", (0,-0.8*h), dir(90));
-	label(currentpicture, "0", (1,-1.5h), dir(90));
-	label(currentpicture, "t", (1,-0.8*h), dir(90));
-	label(currentpicture, "0", (2,-1.5h), dir(90));
-	label(currentpicture, "s", (2,-0.8*h), dir(90));
-	label(currentpicture, "1", (3,-1.5h), dir(90));
-	label(currentpicture, "s", (3,-0.8*h), dir(90));
-	label(currentpicture, "1", (4,-1.5h), dir(90));
-	label(currentpicture, "t", (4,-0.8*h), dir(90));
-	label(currentpicture, "1", (5,-1.5h), dir(90));
-	label(currentpicture, "s", (5,-0.8*h), dir(90));
-	label(currentpicture, "1", (6,-1.5h), dir(90));
-	label(currentpicture, "s", (6,-0.8*h), dir(90));
-	label(currentpicture, "0", (7,-1.5h), dir(90));
-	label(currentpicture, "s", (7,-0.8*h), dir(90));
-	label(currentpicture, "0", (8,-1.5h), dir(90));
-	label(currentpicture, "t", (8,-0.8*h), dir(90));
-	label(currentpicture, "0", (9,-1.5h), dir(90));
-	label(currentpicture, "t", (9,-0.8*h), dir(90));
-	label(currentpicture, "1", (10,-1.5h), dir(90));
-	label(currentpicture, "s", (10,-0.8*h), dir(90));
-	label(currentpicture, "1", (11,-1.5h), dir(90));
-	label(currentpicture, "t", (11,-0.8*h), dir(90));
-	label(currentpicture, "0", (12,-1.5h), dir(90));
-	label(currentpicture, "s", (12,-0.8*h), dir(90));
-	label(currentpicture, "1", (13,-1.5h), dir(90));
-	label(currentpicture, "t", (13,-0.8*h), dir(90));
-	\end{asy}
-	\caption{An example of light leaves.}
-	\label{fig:lightleaf_example}
-\end{figure}
-
-Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any binary string $\ul b$ of length $n$, we can construct a diagram based on a series of rules.
-
-Each bit of $\ul b$ is read from left to right in order and designated either up or down.
-We say that a bit $x$ is an \emph{open neighbor} of $y$ if $x$ is marked up, $x$ and $y$ have the same color, and there are no other bits marked up between $x$ and $y$.
-\begin{itemize}
-	\ii If the bit is a $1$:
-	\begin{itemize}
-		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, and mark both bits as down.
-		\ii Otherwise, designate the current bit as up.
-	\end{itemize}
-	\ii If the bit is $0$:
-	\begin{itemize}
-		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, mark the previous bit as down, and the current bit as up.
-		\ii Otherwise, create a ``stub'', i.e. a single vertex of degree one, and mark the current bit as down.
-	\end{itemize}
-\end{itemize}
-Finally, join any bits which are up at the end of the process to the opposite end.
-A map which arises in such a manner is called a \emph{light leaf}.
-An example of such a light leaf is shown in Figure~\ref{fig:lightleaf_example}.
-
-These light leaves are interesting because, in the seventh chapter of \cite{span}, it is shown that these light leaves form a ``basis'' in the sense that all maps may be expressed by compositions of these light leaves.
-
 \subsection{Definitions and Notations}
 \label{sec:prelim_def_notation}
+Take an infinite dihedral group $W=\left<s,t\mid s^2=t^2=1\right>$ and let $R = \RR[\alpha_s, \alpha_t]$ be the Coxeter ring as defined in Appendix~\ref{sec:prelim_background}, where $\alpha_s$ denotes reflection over the hyperplane normal to $s$.
 \subsubsection{Notations for Strings}
@@
 Consider a string $\ul r$ of letters $s$ and $t$.
-Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangeably) formed by the light leaves.
+Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangeably) formed by the light leaves, as prescribed in Appendix~\ref{sec:prelim_lightleave}.
 We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.
@@
 We will denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
-If the two half-maps are not compatible (that is, $\Top_{\ul r}(\ul a) \neq \Top_{\ul r}(\ul b)$) then we will simply treat the product as the zero map.
+If the two half-maps are not compatible (that is, $\Top_{\ul r}(\ul a) \neq \Top_{\ul r}(\ul b)$) then we will simply set $\MM_{\ul r}(\ul a, \ul b) = 0$.
 
@@
 \subsubsection{Nomenclature for Certain Structures in Diagrams}
-Let us make a few convenient definitions.
+Let us make a few convenient definitions for some recurring characters in our full-diagrams.
 
@@
 \end{theorem}
-\begin{figure}[ht]
-	\centering
-	\begin{asy}
-		size(7cm);
-		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
-		int n = 8;
-		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
-		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
-		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
-		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
-		draw(currentpicture, (4,0)--(4,h), s);
-		dot(currentpicture, (4,h), dot_s);
-		draw(currentpicture, (7,0)--(7,h), s);
-		dot(currentpicture, (7,h), dot_s);
-		dot(currentpicture, (1, h/2), dot_s);
-		dot(currentpicture, (2, h/2), dot_s);
-		label(currentpicture, "1", (0,-1.5h), dir(90));
-		label(currentpicture, "s", (0,-0.8*h), dir(90));
-		label(currentpicture, "0", (1,-1.5h), dir(90));
-		label(currentpicture, "s", (1,-0.8*h), dir(90));
-		label(currentpicture, "0", (2,-1.5h), dir(90));
-		label(currentpicture, "s", (2,-0.8*h), dir(90));
-		label(currentpicture, "1", (3,-1.5h), dir(90));
-		label(currentpicture, "s", (3,-0.8*h), dir(90));
-		label(currentpicture, "0", (4,-1.5h), dir(90));
-		label(currentpicture, "s", (4,-0.8*h), dir(90));
-		label(currentpicture, "1", (5,-1.5h), dir(90));
-		label(currentpicture, "s", (5,-0.8*h), dir(90));
-		label(currentpicture, "1", (6,-1.5h), dir(90));
-		label(currentpicture, "s", (6,-0.8*h), dir(90));
-		label(currentpicture, "0", (7,-1.5h), dir(90));
-		label(currentpicture, "s", (7,-0.8*h), dir(90));
-	\end{asy}
-	\caption{A half-map with base $\SS_8$.}
-	\label{fig:pf_trivial_theorem_example}
-\end{figure}
-\begin{proof}
-	We will only consider the case where $\Top(\ul a) = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.
-See Figure~\ref{fig:pf_trivial_theorem_example} for a example of such a map.
-
-	Number the anchors $1$, $2$, \dots from left to right.
-
-	For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.
-Note that the antennae of a component always form a single contiguous sequence of anchors.
-
-	The key observation is that for $1 \le i \le n-1$, we have that $\ul b^\ast[i] = 1$ if and only if $i$ and $i+1$ are both antennae of some component in $\MM(\ul b)$.  This follows by construction.
-
-	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$ to obtain a full-map.
-Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel} each other $k$ times if they have $k$ antennae in common.
-Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because the two antenna combine to form an empty bubble.
-Furthermore, it is easy to see that any bubbles must be formed in this manner.
-In combination with the claim above, this implies the first case of the theorem.
-
-	On the other hand, suppose this product is nonzero, and consider a component from the top with $k$ antennae.
-We claim that there are $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees; this would complete the proof, because each tree contracts to a barbell.
-Notice that $\pi_1(\ul a^\ast) + \pi_1(\ul b^\ast)$ counts the number of edges between adjacent anchors ($i$ and $i+1$).
-Because there are no cycles, deleting one of these edges increases the number of connected components by exactly one (since all the connected components are trees).
-If we delete all such edges, then we obtain $n$ barbells.
-Therefore there must have been $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees to begin with, as desired.
-\end{proof}
+The proof is given in Appendix~\ref{sec:s_proof}; it is essentially only a matter of finding loops and counting connected components.
 
@@
 
-In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
+In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  The proofs are given in Appendix~\ref{sec:lemmata_proof}.
 \begin{lemma}[Bubble Lemma]
@@
 \end{lemma}
-
-\subsection{Proof of the Bubble Lemma}
-We begin with a proof of the Bubble Lemma\footnote{I should remark that attempting to construct counterexamples to the Bubble Lemma leads to a far better understanding than trying to read the following proof.}, which is the crux result of the alternating case.
-Indeed, both of the subsequent lemmas are fairly straightforward consequences of this one.
-
-\begin{proof}[Proof of Lemma \ref{thm:bubble}]
-	Take a bubble $B$ and assume without loss of generality that it is blue.
-It is easy to see, by considering two anchors on the boundary of blue, that there is some red anchor inside $B$.
-This implies that $B$ has at least one red caterpillar.
-
-	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.
-
-	Define a pair of red anchors $u, v$, with $u$ to the left of $v$, to be \emph{quasi-connected} if (i) one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect blue lines, and (ii) there is no red anchor $w$ strictly between $u$ and $v$ for which one can draw a similar arc on the same half-map joining $w$ and $v$.
-
-	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a single arc}.
-To prove this, take such a quasi-connected pair $u$ and $v$.
-Now we'll focus only on the half-map in which the prescribed arc is drawn.
-We thus may state that an arc \emph{shields} any anchors which lie between its endpoints.
-
-	\begin{figure}[ht]
-		\centering
-		\begin{asy}
-			size(6cm);
-			pen s = blue, t = red + dashed + 0.6;
-			pen dot_s = blue, dot_t = red;
-			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
-			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
-			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
-			draw((1,0)..(3,2)..(5,0), t); // red covering arc
-			draw((2,0)..(3,1)..(4,0), s); // blue covering arc again
-			label("$u$", (3,0), dir(-90));
-			label("$v$", (5,0), dir(-90));
-		\end{asy}
-		\hspace{2em}
-		\begin{asy}
-			size(6cm);
-			pen s = blue, t = red + dashed + 0.6;
-			pen dot_s = blue, dot_t = red;
-			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
-			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
-			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
-			draw((1,0)..(4,2)..(7,0), t); // red covering arc
-			draw((2,0)..(4,1)..(6,0), s); // blue covering arc
-			label("$u$", (3,0), dir(-90));
-			label("$v$", (5,0), dir(-90));
-		\end{asy}
-		\caption{Proving the bubble lemma with quasi-connected vertices.}
-		\label{fig:pf_bubble}
-	\end{figure}
-	Because the string is alternating, we can take a blue anchor $x$ immediately to the left of $v$.
-Now, there must be some blue arc shielding $u$ and $v$ (since $u,v$ are inside a blue bubble).
-By the light-leave construction, there must be some red arc $A$ covering $x$.
-If this arc joins $u$ and $v$, then we are done.
-	Otherwise, if it has endpoint $v$ then it must completely cover $u$ by condition (ii) of quasi-connectedness; if not, then it must completely cover $v$.  This leads us to two cases.
-	\begin{itemize}
-		\ii If the arc covers exactly one of $u$ or $v$, say $u$, then there must be a blue arc shielding $u$ from $A$.
-But then this contradicts the quasi-connectedness, because now it is not possible to join $u$ and $v$ by an arc on this half-map.
-This case is illustrated by the left half of Figure~\ref{fig:pf_bubble}.
-		\ii If the arc covers both $u$ and $v$, then there must be a blue arc which shields both $u$ and $v$, which is itself shielded by $A$.
-Then we can repeat the same procedure with this new blue arc.
-This case is illustrated by the right half of Figure~\ref{fig:pf_bubble}.
-	\end{itemize}
-	Therefore any pair of quasi-connected anchors must be connected by an arc.
-However, one can verify that the red anchors in $B$ but not in any other blue bubble are ``connected'' under quasi-connectedness.\footnote{That is, one can follow a sequence of red anchors, each consecutive pair quasi-connected, from any red anchor to any other red anchor.}  Therefore all such red anchors must be connected.
-So there is a single caterpillar, as desired.
-\end{proof}
-
-\subsection{Proof of the Caterpillar Lemma}
-We will now derive the Caterpillar Lemma as a consequence of the Bubble Lemma.
-
-First, a few definitions for this section only.
-\begin{definition*}
-	Consider a caterpillar $C$ in a full-diagram with base $\AA_n$.
-Define the \emph{nesting level} of the caterpillar as the largest integer $n$ for which there exists caterpillars $C = C_0$, $C_1$, $C_2$, $\dots$, $C_n$ such that $C_i$ holds $C_{i+1}$ for each $i=0,1,\dots,n-1$.
-Define the \emph{size} of the caterpillar to be the number of bubbles it contains.
-\end{definition*}
-
-\begin{proof}[Proof of Lemma \ref{thm:caterpillar}]
-	The proof is by double induction.  First we will consider caterpillars with nesting level $0$.
-
-	We perform induction on the size of the caterpillar. 
-	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
-	This is the base step.
-	For the inductive step, consider an arbitrary bubble.
-Inside it is exactly one caterpillar, say $c$, by the Bubble Lemma.
-Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
-	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms.
-One of them is zero because it creates a new empty bubble.
-The other is the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.
-The inductive hypothesis now applies directly, and this completes the first induction.
-
-	Now suppose a caterpillar has nesting level $k \ge 1$.
-We simply apply the exact same induction on size as before.
-The only modification is that, instead of a barbell, we have a caterpillar with nesting level strictly less than $k$.
-However, these caterpillars all evaluate as a polynomial again of the form $x^my^n \alpha_s$ or $x^my^n\alpha_t$, by the outer inductive hypothesis.
-So applying equation \eqref{eq:barbell_break} in the same manner completes this induction as well.
-\end{proof}
-
-\subsection{Proof of the Pasture Lemma}
-\begin{figure}[ht]
-	\centering
-	\begin{asy}
-		size(11cm);
-		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
-		int n = 6;
-
-		picture before;
-		draw(before, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
-		draw(before, (2,0)--(2,h), s);
-		dot(before, (2,h), dot_s);
-		draw(before, (5,0)--(5,h), t);
-		dot(before, (5,h), dot_t);
-		draw(before,(0,0)--(0,3*h), s);
-		draw(before,(3,0)--(3,3*h), t);
-		draw(before,(4,0)--(4,3*h), s);
-		dot(before, (3, h/2), dot_t);
-
-		add(before); add(reflect((0,0),(1,0))*before);
-		draw((-1,0)--(6,0));
-
-		picture after;
-		draw(after, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
-		draw(after, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), s);
-		draw(after, (3,0)--(3,h/2)..((3+7)/2.0,h*4)..(7,h/2)--(7,0), t);
-		draw(after, (0,0)--(0,h/2)..((0+8)/2.0,h*5.5)..(8,h/2)--(8,0), s);
-		draw(after, (2,0)--(2,h), s);
-		dot(after, (2,h), dot_s);
-		draw(after, (5,0)--(5,h), t);
-		dot(after, (5,h), dot_t);
-		dot(after, (3, h/2), dot_t);
-
-		add(shift((9,0)) * after);
-		add(shift((9,0)) * reflect((0,0),(1,0))*after);
-		draw((8,0)--(18,0));
-
-		label("$\to$", (7,0));
-	\end{asy}
-	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Lemma from the Bubble Lemma.}
-	\label{fig:pf_pasture}
-\end{figure}
-The Bubble Lemma and the Pasture Lemma are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Lemma follows from the Bubble Lemma.
-\begin{proof}[Proof of Lemma \ref{thm:pasture}]
-	Again, let $T$ denote the top, with length $N$.
-In the first case, suppose $T[N] \neq \AA_n[n]$; that is, the last characters of $T$ and $\AA_n$ differ.
-Then it must be the case that the rightmost anchor is not part of a fence.
-	Now suppose the map arose from $\MM_{\AA_n}(\ul a, \ul b)$.
-Let $\ul a'$ be the string formed by appending $N$ $1$'s to $\ul a$, and define $\ul b'$ similarly.
-Now consider the map \[ \MM_{\AA_{n+N}} \left( \ul a', \ul b' \right).
-\]  See Figure~\ref{fig:pf_pasture} for an example.
-
-	It is easy to verify that the top of this new map is zero.
-Now what we have done is enclose the contents of each pasture into bubbles.
-The Bubble Lemma tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.
-This implies the Pasture Lemma in the first case.
-
-	The case where $T[N] = \AA_n[n]$ is similar.
-We simply append a zero followed by $N$ $1$'s and repeat the same procedure.
-The only difference is that the innermost barbell was generated by the $0$ we appended, and thus was not part of the original diagram.
-\end{proof}
+These results show that the structure in maps with base $\AA_n$ is quite limited.
 
@@
 \subsection{A Partial Recursion}
-In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.
+In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  The proof is given in Appendix~\ref{sec:recurse_proof}.
 
@@
 
-\begin{proof}
-	We will only resolve the case where $n$ is odd; that is, $\AA_n$ terminates in $s$.  The other case is identical.
-	\begin{enumerate}[(i)]
-		\ii Suppose $\ul a[n] = \ul b[n] = 0$.  Note that the top of $M_1$ is also $T$.
-		\begin{itemize}
-			\ii If $T = \varnothing$, then $M_1$ also had top $\varnothing$.
-Therefore, the addition of the $0$'s at the end simply generates an extra blue barbell.
-So the resulting map is simply a multiple by $\alpha_s$.
-			\ii The case where $T$ ends in $t$ is analogous; we simply obtain a new barbell.  However, because $T \neq \emptyset$, the extra factor is $Q_T$ instead of simply $\alpha_t$. 
-			\begin{figure}[ht]
-				\centering
-				\begin{asy}
-					size(12cm);
-					real h = 0.7;
-					pen s = blue, t = red + dashed + 0.6;
-					pen dot_s = blue, dot_t = red;
-					int n = 4;
-
-					picture one;
-					draw(one, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
-					draw(one, (1,0)--(1,h), t);
-					dot(one, (1,h), dot_t);
-					draw(one, (3,0)--(3,h), t);
-					dot(one, (3,h), dot_t);
-					draw(one,(2,0)--(2,3*h), s);
-					dot(one, (2, h/2), dot_s);
-
-					picture two;
-					draw(two, (0,0)--(0,h), s);
-					dot(two, (0,h), dot_s);
-					draw(two, (1,0)--(1,h), t);
-					dot(two, (1,h), dot_t);
-					draw(two, (3,0)--(3,h), t);
-					dot(two, (3,h), dot_t);
-					draw(two,(2,0)--(2,3*h), s);
-
-					add(one); add(reflect((0,0),(1,0))*two);
-					draw((-1,0)--(4,0));
-
-					int n = 5;
-
-					picture three;
-					draw(three, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
-					draw(three, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
-					draw(three, (1,0)--(1,h), t);
-					dot(three, (1,h), dot_t);
-					draw(three, (3,0)--(3,h), t);
-					dot(three, (3,h), dot_t);
-					draw(three,(4,0)--(4,3*h), s);
-					dot(three, (2, h/2), dot_s);
-					dot(three, (4, h/2), dot_s);
-
-					picture four;
-					draw(four, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
-					draw(four, (0,0)--(0,h), s);
-					dot(four, (0,h), dot_s);
-					draw(four, (1,0)--(1,h), t);
-					dot(four, (1,h), dot_t);
-					draw(four, (3,0)--(3,h), t);
-					dot(four, (3,h), dot_t);
-					draw(four,(4,0)--(4,3*h), s);
-					dot(four, (4, h/2), dot_s);
-
-					add(shift((7,0)) * three); add(shift((7,0)) * reflect((0,0),(1,0))*four);
-					draw((7-1,0)--(7+5,0));
-					MP("\to", (5,0), (0,0));
-				\end{asy}
-				\caption{$\MM(1000, 0010)$ on left against $\MM(10000, 00100)$ on right.}
-				\label{fig:recurse_example_destr_zero}
-			\end{figure}
-			\ii Now suppose $T$ ends in $s$.
-Then the addition of the $0$'s resulted in enclosing a caterpillar of $M_1$ in an attached bubble, as per Figure~\ref{fig:recurse_example_destr_zero}.
-Breaking out of the additional blue loop nows adds a factor of $x$, but the red caterpillar is annihilated in the process; therefore, only the fluff remains, because there is nothing to push through the fences.
-		\end{itemize}
-		\ii Now suppose that $\ul a[n] = \ul b[n] = 1$.
-		\begin{itemize}
-			\ii First, suppose $T$ ends in $s$.
-Then the additional $1$'s added simply create a fence on the far right, because there is no ``up'' blue anchors to interact with.
-Because this fence is already on the far right, it does not affect the product, hence $M = M_1$.
-			\begin{figure}[ht]
-				\centering
-				\begin{asy}
-					size(11cm);
-					real h = 0.7;
-					pen s = blue, t = red + dashed + 0.6;
-					pen dot_s = blue, dot_t = red;
-					int n = 4;
-
-					picture one;
-					draw(one, (0,0)--(0,h), s);
-					dot(one, (0,h), dot_s);
-					draw(one, (3,0)--(3,h), t);
-					dot(one, (3,h), dot_t);
-					draw(one,(1,0)--(1,3*h), t);
-					draw(one,(2,0)--(2,3*h), s);
-
-					picture two;
-					draw(two, (0,0)--(0,h), s);
-					dot(two, (0,h), dot_s);
-					draw(two, (3,0)--(3,h), t);
-					dot(two, (3,h), dot_t);
-					draw(two,(1,0)--(1,3*h), t);
-					draw(two,(2,0)--(2,3*h), s);
-
-					add(one); add(reflect((0,0),(1,0))*two);
-					draw((-1,0)--(4,0));
-
-					int n = 5;
-
-					picture three;
-					draw(three, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
-					draw(three, (0,0)--(0,h), s);
-					dot(three, (0,h), dot_s);
-					draw(three, (3,0)--(3,h), t);
-					dot(three, (3,h), dot_t);
-					draw(three,(1,0)--(1,3*h), t);
-
-					picture four;
-					draw(four, (2,0)--(2,h/2)..((2+4)/2.0,h*2)..(4,h/2)--(4,0), s);
-					draw(four, (0,0)--(0,h), s);
-					dot(four, (0,h), dot_s);
-					draw(four, (3,0)--(3,h), t);
-					dot(four, (3,h), dot_t);
-					draw(four,(1,0)--(1,3*h), t);
-
-					add(shift((7,0)) * three); add(shift((7,0)) * reflect((0,0),(1,0)) * four);
-					draw((7-1,0)--(7+5,0));
-					MP("\to", (5,0), (0,0));
-				\end{asy}
-				\caption{$\MM(0110, 0110)$ on left against $\MM(01101, 01101)$ on right.}
-				\label{fig:recurse_example_destr_one}
-			\end{figure}
-			\ii Conversely, suppose that $T$ ends in $t$.   See Figure \ref{fig:recurse_example_destr_one} for an example.
-
-			In that case, $M_1$ must have had the top $T$ with an $s$ appended.
-Once again, we find that the red caterpillar from $M_1$ is enclosed in a bubble.
-This time, however, the bubble is not attached.
-Therefore, while we still obtain the extra factor of $x$ and the caterpillar is still removed, we remain with a blue barbell on the far right pasture.
-So we must push this blue barbell through $T$.
-This adds a factor of $Q_T$, and so we obtain the desired form $-xF Q_T$.
-			\ii The case where $T = \varnothing$ is analogous to the previous case; in a sense, we merely have a degenerate $Q_\varnothing = \alpha_s$.
-Specifically, the blue barbell is already on the correct pasture, so we simply add a factor of $\alpha_s$.
-		\end{itemize}
-	\end{enumerate}
-	This exhausts all the cases in the proposition, hence we're done.
-\end{proof}
-
 \section{Conclusion}
@@
 \section{Acknowledgments} 
-I wish to thank the MIT Math Department for organizing the Math RSI, and in particular the head mentor Dr. Tanya Khovanova (MIT) for providing individual discussion with me.
-I also wish to thank my tutor Mr. Antoni Rangachev (Northeaster University) for his invaluable advice in preparing both this paper and my final presentation.
-I would also like to thank the Center for Excellence in Education and the Research Science Institute, as well as the Massachusetts Institute of Technology, for generously providing the facilities for the research.
+I wish to thank the MIT Math Department for organizing the Math RSI, and in particular the head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me.
+I also wish to thank my tutor Mr. Antoni Rangachev, Northeastern University, for his invaluable advice in preparing both this paper and my final presentation.
+I also thank the Center for Excellence in Education and the Research Science Institute, as well as the Massachusetts Institute of Technology, for generously providing the facilities for the research.
+
+I would also like to thank my sponsors from RSI 2013:
+\begin{inparaenum}[]
+	\ii Ms. Alexa Margalith, The Leonetti/O'Connell Family Foundation;
+	\ii Mr. Arvind Parthasarathi, YarcData;
+	\ii Mr. Samuel Chen and Ms. Kathy Chang;
+	\ii Dr. Robert E. Curry;
+	\ii Mr. and Mrs. William Hellman;
+	\ii Mr. Ronald Houhauser;
+	\ii Ms. Chienlan Hsu-Hoffman; and
+	\ii Mr. and Mrs. George Keiter.
+\end{inparaenum}
 
 Finally, I offer my sincerest gratitude to my mentor Mr.
-Francisco Unda (MIT) for daily mentorship, and Professor Benjamin Elias (MIT), for providing the project and for often meeting with me personally to discuss it.
+Francisco Unda, MIT, for daily mentorship, and Professor Benjamin Elias, MIT, for providing the project and for often meeting with me personally to discuss it.
 That sounded horribly fake, but I really mean it.  You guys are the best.  Thank you for a great project.

### 2013-07-27 appa.tex
Penultimate drafts.  QQ.

@@
 Otherwise, the product is $0$.
-
-In \cite{basispf}, Khovanov and Elias show that all such maps can be expressed as a linear combination of these diagrams.
 
@@
 \end{figure}
+We now present the algorithm for Libedinsky's light leaves, in the special case where $W$ is the infinite dihedral group.
+A full construction for more general Coxeter groups is given in \cite{gr4all}.
 
@@
 An example of such a light leaf is shown in Figure~\ref{fig:lightleaf_example}.
-
-These light leaves are interesting because, in the seventh chapter of \cite{span}, it is shown that these light leaves form a ``basis'' in the sense that all maps may be expressed by compositions of these light leaves.
 
@@
 Therefore, the addition of the $0$'s at the end simply generates an extra blue barbell.
-So the resulting map is simply a multiple by $\alpha_s$.
-			\ii The case where $T$ ends in $t$ is analogous; we simply obtain a new barbell.  However, because $T \neq \emptyset$, the extra factor is $Q_T$ instead of simply $\alpha_t$. 
+So the resulting map is simply a multiple by $\alpha_s$; i.e.
+$M = \alpha_sM_1$.
+			\ii The case where $T$ ends in $t$ is analogous; we simply obtain a new barbell.
+However, because $T \neq \varnothing$, the extra factor is $Q_T$ instead of simply $\alpha_t$.
+Hence, $M = Q_TM_1$.
 			\begin{figure}[ht]
@@
 				\end{asy}
-				\caption{Enclosing a caterpillar in an attached component.}
+				\caption{$\MM(1000,0010)$ on the left, and $\MM(10000,00100)$ on right.}
 				\label{fig:recurse_example_destr_zero}
@@
 Breaking out of the additional blue loop nows adds a factor of $x$, but the red caterpillar is annihilated in the process; therefore, only the fluff remains, because there is nothing to push through the fences.
+Hence, $M = -xF$.
 		\end{itemize}
@@
 				\end{asy}
-				\caption{Enclosing a caterpillar in a free component.}
+				\caption{$\MM(0110,0110)$ on the left, and $\MM(01101,01101)$ on right.}
 				\label{fig:recurse_example_destr_one}
@@
 So we must push this blue barbell through $T$.
-This adds a factor of $Q_T$, and so we obtain the desired form $-xF Q_T$.
+This adds a factor of $Q_T$, and so we obtain the desired form $M = -xF Q_T$.
 			\ii The case where $T = \varnothing$ is analogous to the previous case; in a sense, we merely have a degenerate $Q_\varnothing = \alpha_s$.
 Specifically, the blue barbell is already on the correct pasture, so we simply add a factor of $\alpha_s$.
+Therefore, $M = -xF \alpha_s$.
 		\end{itemize}

### 2013-07-27 paper.tex
Penultimate drafts.  QQ.

@@
 % This is paper.tex
-
 \section{Introduction}
@@
 We study a class of maps between Bott-Samelson bimodules.  
-These maps are represented by certain types of diagrams, as described in Section~\ref{sec:prelim_map}.
-The maps are composed by juxtaposition.
+% These maps are represented by certain types of diagrams, as described in Section~\ref{sec:prelim_map}.  The maps are composed by juxtaposition.  
+Bott-Samelson bimodules arise from the study of Soergel bimodules, as mentioned in \cite{gr4all}, in the sense that a description of the category of Bott-Samelson bimodules is sufficient to understand that of the Soergel bimodules.
+However, Bott-Samelson bimodules admit a combinatorial description.
+In particular, \cite{gr4all} gives a presentation for the category of Bott-Samelson bimodules in terms of planar diagrammatics (i.e.
+diagrams in the plane).
 
-TODO: Expand on history, motivation, importance, etc. (meeting Ben on Monday)
+This paper investigates some of the properties of these diagrammatics from a combinatorial perspective.
+However, in this paper, we consider only the special case of an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group).
 
 Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in Section~\ref{sec:prelim_lightleave}.
+These light leaves are interesting because they form a spanning set for the maps we are interest in, as shown in \cite{gr4all}.
 Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.
-We describe the relationship between the final result of such a composition and the two binary strings being composed.
+The goal of the project is to describe the relationship between the final result of such a composition and the two binary strings.
 
-Because the technical description of the problem statement is quite involved, we devote the entirety of Section~\ref{sec:prelim} to preliminaries and defer the actual problem statement to Section~\ref{sec:probstate}.
+The technical description of the problem statement is quite involved.
+Thusly, the preliminaries for the problem are given in Appendix~\ref{sec:prelim_background}, while the definitions used in this paper are recorded in Section~\ref{sec:prelim}.
+The problem statement is given in Section~\ref{sec:probstate}.
 The results begin by solving the special case of one color completely in Section~\ref{sec:res_onecolor}.
@@
 
-In Section~\ref{sec:prelim_def_notation}, we introduce several definitions which we use throughout the paper.
-Next, in Section~\ref{sec:prelim_explain_poly_eval}, we describe how these maps can be represent as polynomials.
-The actual problem statement is then deferred to \ref{sec:probstate}.
+In Section~\ref{sec:prelim_def_notation}, we introduce several of our definitions which we use throughout the paper.
+Next, in Section~\ref{sec:prelim_explain_poly_eval}, we describe how these maps can be represented as polynomials.
+The actual problem statement is then deferred to Section~\ref{sec:probstate}.
 \subsection{Definitions and Notations}
@@
 
-Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.
+Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.  In general, underline Roman letters denote strings.
 
@@
 \begin{definition*}
-	A connected component which (i) is a tree, and (ii) does not touch the top or bottom boundaries is called a \emph{barbell}.
+	A connected component which (i) is acyclic, and (ii) does not touch the top or bottom boundaries is called a \emph{barbell}.
 \end{definition*}
@@
 \begin{definition*}
-	For any reduced expression $\ul r$, we adopt the quantum polynomial $Q_{\ul r}$ by :
+	For any reduced expression $\ul r$, we define the quantum polynomial $Q_{\ul r}$ by :
 	\[
@@
 
-Subsequently, we make the following definition.
+Subsequently, we make the following definition for this section only.
 \begin{definition*}
@@
 \end{theorem}
-The proof is given in Appendix~\ref{sec:s_proof}; it is essentially only a matter of finding loops and counting connected components.
+The proof is essentially only a matter of finding loops and counting connected components.
+As such, it is deferred to in Appendix~\ref{sec:s_proof};
 
@@
 
-In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  The proofs are given in Appendix~\ref{sec:lemmata_proof}.
+We now present three results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  
 \begin{lemma}[Bubble Lemma]
@@
 \end{lemma}
-These results show that the structure in maps with base $\AA_n$ is quite limited.
+The Bubble Lemma is the key combinatorial observation, which hinges on the fact that any two anchors with the same color have a third anchor of the other color between them.
+The other two lemmas follow almost directly from it.
+The details of the proofs are given in Appendix~\ref{sec:lemmata_proof}.
 
@@
 
-This motivates the following definition.
+This motivates the following definition, which is relevant for Proposition~\ref{thm:recurse}.
 \begin{definition*}
@@
 \subsection{A Partial Recursion}
-In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  The proof is given in Appendix~\ref{sec:recurse_proof}.
+In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.
 
@@
 			\begin{cases}
-				M_1 \alpha_s & \text{if $T = \varnothing$} \\ % just another barbell
+				\alpha_s M_1 & \text{if $T = \varnothing$} \\ % just another barbell
 				-xF & \text{if $T$ ends in $s$} \\ % closes a caterpillar like 0|
-				M_1 Q_T & \text{if $T$ ends in $t$}. \\ % just another barbell, but push it all the way through nonempty T
+				 Q_T M_1 & \text{if $T$ ends in $t$}. \\ % just another barbell, but push it all the way through nonempty T
 			\end{cases}
@@
 \end{proposition}
+The recursion arises because, using the lemmata, we are able to see exactly what happens in the rightmost pasture if a pair of $1$'s or a pair of $0$'s is added.
+In short, either a barbell or fence is added on the far right, or a caterpillar is enclosed in a bubble; each of these leads to one of the cases above.
+The full computation is given in Appendix~\ref{sec:recurse_proof}.
 
@@
 So, either the results of Section~\ref{sec:res_alt_compute} will have to be generalized significantly (in the context of maps outside those of base $\AA_n$), or an entirely new approach will be required.
+
+Yet another possible direction is to search for similar results when the order of $st$ in $W$ is finite, or even if $W$ is an arbitrary Coxeter group.
 

### 2013-07-29 abstract.tex
Hell Week Monday 11AM update.

@@
 This paper considers left/right action-preserving morphisms between Bott-Samelson bimodules from a combinatorial perspective; specifically, using a diagrammatic representation.
-We examine the maps formed by a basis known as Libedinsky's light leaves, which constructs a map based on a sequence of letters $\underline r$ (composed of $s$ and $t$) and a binary string $\underline b$.
+We examine the maps formed by a basis known as Libedinsky's light leaves, which constructs a map based on a string $\underline r$, composed of the letters $s$ and $t$, and a binary string $\underline b$.
 The eventual goal is to find a formula for the composition of two such maps based on their binary strings $\underline b$.

### 2013-07-29 appa.tex
Hell Week Monday 11AM update.

@@
 Explicitly, $x = \frac{-2(\alpha_s,\alpha_t)}{(\alpha_s, \alpha_s)}$ and $y = \frac{-2(\alpha_t,\alpha_s)}{(\alpha_t,\alpha_t)}$.
-Note that $x=y$ if $\left\lvert \alpha_s \right\rvert = \left\lvert \alpha_t \right\rvert$.
 
@@
 
-Let $R^s$ be the subring of $R$ which is invariant under $s$.  Define $R^t$ similarly.  Then a \emph{Bott-Samelson bimodule} is a bimodule of the form
+Let $R^s$ be the subring of $R$ which is invariant under $s$.  In other words,
+\[ R^s \defeq \left\{ r \in R \mid s(r) = r \right\}. \]
+Define $R^t$ similarly.  Then a \emph{Bott-Samelson bimodule} is a bimodule of the form
 \[ R \otimes_{R^{i_1}} R \otimes_{R^{i_2}} R \otimes_{R^{i_3}} \dots \otimes_{R^{i_n}} R, \]
@@
 \newcommand{\DD}{\mathcal D}
-Certain maps between Bott-Samelson bimodules can be described in terms of diagrams.
+These maps can be described in terms of diagrams.
 We take a detour and first describe the appearance of such diagrams; in the subsequent section we will explain their algebraic meaning.
-A reader who is not interested in this context can simply accept on faith the relations specified in Section~\ref{sec:prelim_genrel}.
+A reader who is not interested in this context can simply accept on faith the relations specified in Appendix~\ref{sec:prelim_genrel}.
 
-Consider a category $\DD$ whose elements are linear combinations $\sum c_i \square$ of the diagrams described below.  The coefficients $c_i$ belong to the ring $\ZZ[x,y]$.
+Consider a category $\DD$ whose elements are linear combinations $\sum c_i \square$ of the diagrams described below (where the boxes are diagrams).
+The coefficients $c_i$ belong to the ring $\ZZ[x,y]$.
 
@@
 \begin{enumerate}[(i)]
-	\ii Vertices may lie on the upper or lower boundary, but not on the left or right boundary.
+	\ii Vertices may lie on the upper or lower boundary, but not on the left or right boundary.  In other words, the graph is embedded in $\RR \times [0,1]$.
 	\ii Each vertex has degree $1$ or $3$.
@@
 
-The elements of $\DD$ can be added by simply adding corresponding coefficients.
+The elements of $\DD$ can be added by simply adding corresponding coefficients in front of each diagram; no other relations exist.
 Multiplication is defined as follows: the product of two diagrams is the composition of the diagrams if the labels on the bottom of the first coincide with those on the top of the second.
+By composition, we mean that the first diagram is vertically juxtaposed on top of the second diagram; see Figure~\ref{fig:example_compose} for an example.
 Otherwise, the product is $0$.
@@
 \begin{definition*}
-	The \emph{Demazure operator} $\partial_s: R \to R$ is given by $\partial_s(f) = \frac{f - sf}{\alpha_s}$.
+	The \emph{Demazure operator} $\partial_s: R \to R$ is given by $\partial_s(f) = \frac{f - s(f)}{\alpha_s}$.
 \end{definition*}
@@
 	\end{asy}
-	\caption{An example of light leaves.}
+	\caption{An example of a light leaf.}
 	\label{fig:lightleaf_example}
@@
 \end{itemize}
-Finally, join any bits which are up at the end of the process to the opposite end.
+Finally, join any bits which are up at the end of the process to the upper boundary of the diagram.
 A map which arises in such a manner is called a \emph{light leaf}.
 An example of such a light leaf is shown in Figure~\ref{fig:lightleaf_example}.
+
+The \emph{top} of such a map is the expression which appears on the upper boundary; i.e.
+the bits which are still up at the end of the algorithm.
+For example, the map in Figure~\ref{fig:lightleaf_example} has top $ts$.
+Note that any top is a reduced expression.
 
@@
 
-	Number the anchors $1$, $2$, \dots from left to right.
+	Number the anchors $1,2,\dots,n$ $1,2,\dots,n$ $1,2,\dots,n$ $1,2,\dots,n$ from left to right.
 
@@
 Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel} each other $k$ times if they have $k$ antennae in common.
-Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because the two antenna combine to form an empty bubble.
+Notice that if any two components feel each other at least twice, then there exist two adjacent common antennae, whence the composition of the entire map is zero because the two antennae combine to form an empty bubble.
 Furthermore, it is easy to see that any bubbles must be formed in this manner.
@@
 	On the other hand, suppose this product is nonzero, and consider a component from the top with $k$ antennae.
-We claim that there are $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees; this would complete the proof, because each tree contracts to a barbell.
+It suffices to show that there are $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ barbells.
 Notice that $\pi_1(\ul a^\ast) + \pi_1(\ul b^\ast)$ counts the number of edges between adjacent anchors ($i$ and $i+1$).
-Because there are no cycles, deleting one of these edges increases the number of connected components by exactly one (since all the connected components are trees).
+Because there are no cycles, deleting one of these edges increases the number of connected components by exactly one (since all the connected components are barbells).
 If we delete all such edges, then we obtain $n$ barbells.
-Therefore there must have been $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ trees to begin with, as desired.
+Therefore there must have been $n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast)$ barbells to begin with, as desired.
 \end{proof}
@@
 	Take a bubble $B$ and assume without loss of generality that it is blue.
-It is easy to see, by considering two anchors on the boundary of blue, that there is some red anchor inside $B$.
-This implies that $B$ has at least one red caterpillar.
-
-	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.
+It is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.
+Furthermore, it is evident that the bubble is nonempty; hence there is at least one red caterpillar in $B$.
+We will show that there is exactly one.
 
@@
 
-	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a single arc}.
+	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a red arc}.
 To prove this, take such a quasi-connected pair $u$ and $v$.
@@
 			draw((2,0)..(3,1)..(4,0), s); // blue covering arc again
+			label("$A$", (4.1,1.6), dir(60));
 			label("$u$", (3,0), dir(-90));
+			label("$x$", (4,0), dir(-90));
 			label("$v$", (5,0), dir(-90));
@@
 			draw((2,0)..(4,1)..(6,0), s); // blue covering arc
+			label("$A$", (5.6,1.5), dir(60));
 			label("$u$", (3,0), dir(-90));
+			label("$x$", (4,0), dir(-90));
 			label("$v$", (5,0), dir(-90));
@@
 	Therefore any pair of quasi-connected anchors must be connected by an arc.
-However, one can verify that the red anchors in $B$ but not in any other blue bubble are ``connected'' under quasi-connectedness.\footnote{That is, one can follow a sequence of red anchors, each consecutive pair quasi-connected, from any red anchor to any other red anchor.}  Therefore all such red anchors must be connected.
+However, one can verify that the red anchors in $B$ but not in any other bubble are ``connected'' under quasi-connectedness.\footnote{That is, one can follow a sequence of red anchors, each consecutive pair quasi-connected, from any red anchor to any other red anchor.}  Therefore all such red anchors must be connected.
 So there is a single caterpillar, as desired.
@@
 We will now derive the Caterpillar Lemma as a consequence of the Bubble Lemma.
+
+It is worth intuitively explaining the main idea of the proof; the rest is book-keeping.
+Essentially, because caterpillars may only hold a single other caterpillar, we may ``descend down'' until we find a caterpillar which contains barbells in its bubbles.
+Now we break each of the bubbles of this caterpillar one at a time using the barbell forcing rule.
+This generates several $x$ and $y$ terms, but the barbell disappears at each such move.
+Hence, we break all cycles in the caterpillar, at which point it becomes a barbell (modulo the addition of new $x$ and $y$ terms).
+Rinse and repeat.
 
@@
 	We perform induction on the size of the caterpillar. 
-	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
+	If there are no bubbles, then the caterpillar is simply a barbell.
 	This is the base step.
@@
 \section{Complete Product Matrix for ststs}
+\label{sec:ststs_matrix}
 For reference, here is a complete product matrix for maps with base $ststs$.  The blank entries are $0$ maps.  The top is recorded as the title of each table.
@@
 %
+%
 \begin{tabular}{|l||l|}
@@
 \end{tabular}
+%
 %
@@
 \end{tabular}
+
+\vspace{-0.4em}
 
@@
 \end{longtable}
+\vspace{-0.4em}
 
@@
 
-% \end{document}
 \section{GitHub Repository}

### 2013-07-29 paper.tex
Hell Week Monday 11AM update.

@@
 We study a class of maps between Bott-Samelson bimodules.  
-% These maps are represented by certain types of diagrams, as described in Section~\ref{sec:prelim_map}.  The maps are composed by juxtaposition.  
-Bott-Samelson bimodules arise from the study of Soergel bimodules, as mentioned in \cite{gr4all}, in the sense that a description of the category of Bott-Samelson bimodules is sufficient to understand that of the Soergel bimodules.
-However, Bott-Samelson bimodules admit a combinatorial description.
-In particular, \cite{gr4all} gives a presentation for the category of Bott-Samelson bimodules in terms of planar diagrammatics (i.e.
+Bott-Samelson bimodules arise from the study of Soergel bimodules, as mentioned in \cite{gr4all}, in the sense that a description of the category of maps between Bott-Samelson bimodules is sufficient to understand the corresponding category for the Soergel bimodules.
+However, the morphisms of Bott-Samelson bimodules admit a combinatorial description.
+In particular, \cite{gr4all} gives a presentation for the category of these morphisms in terms of planar diagrammatics (i.e.
 diagrams in the plane).
@@
 
-Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in Section~\ref{sec:prelim_lightleave}.
-These light leaves are interesting because they form a spanning set for the maps we are interest in, as shown in \cite{gr4all}.
-Since two diagrams may be composed, we may construct a new map given two binary strings by composing the results of two applications of the light leaves.
-The goal of the project is to describe the relationship between the final result of such a composition and the two binary strings.
+Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in Appendix~\ref{sec:prelim_lightleave}.
+These light leaves are interesting because they form a spanning set for the maps we are interested in, as shown in \cite{gr4all}.
+The project deals with composing two maps formed in such a manner.
+The goal of the project is to describe the relationship between such a composition and the two original binary strings.
 
@@
 The most interesting results are in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate the case where the given string is $ststst\cdots$.
-In particular, we show that the possible resulting structures is extremely limited, and provide a recursion based on these restrictions for special cases.
+In particular, we show that the possible resulting structures are extremely limited, and provide a recursion based on these restrictions for that case.
 
@@
 In general, a string of $s$'s and $t$'s will be referred to as an \emph{expression}.
-In the case where there are no consecutive identical characters (e.g.
-the string is either $\AA_n$ or $\AA_n'$), we will refer to them as \emph{reduced expressions}.
+In the case where there are no consecutive identical characters (in other words, the string is either $\AA_n$ or $\AA_n'$), we will refer to them as \emph{reduced expressions}.
 
@@
 
-Finally, given a string $\ul x$ (either a binary string or a string of $s$'s and $t$'s) we will denote the $i\th$ character as $\ul x[i]$.  In general, underline Roman letters denote strings.
+Finally, given a string $\ul x$ (either a binary string or an expression) we will denote the $i\th$ character as $\ul x[i]$.  In general, underlined Roman letters denote strings.
 
 \subsubsection{Definitions for Maps and Diagram}
-Consider a string $\ul r$ of letters $s$ and $t$.
+Consider an expression $\ul r$.
 Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangeably) formed by the light leaves, as prescribed in Appendix~\ref{sec:prelim_lightleave}.
 We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.
-Additionally, let $\Top_{\ul r}(\ul b)$ denote the top of the half-diagram $\MM_{\ul r}(\ul b)$.
+Figure~\ref{fig:lightleaf_example} (in Appendix~\ref{sec:prelim_lightleave}) gives an example of such a half-map.
+
+Additionally, let $\Top_{\ul r}(\ul b)$ denote the \emph{top} of the half-diagram $\MM_{\ul r}(\ul b)$, as described in Appendix~\ref{sec:prelim_lightleave}.  
+Note that the top of any half-map is always a reduced expression.  In fact, one can verify that the top of a map is given explicitly by
+\begin{equation}
+	\Top_{\ul r}(\ul b) = \prod_{i=1}^n \left( \ul r[i] \right)^{\ul b[i]} \in W.
+	\label{eq:top}
+\end{equation}
 
@@
 \end{definition*}
-Notice that, by homotopy, every blue barbell is simply $\barbell{barbell_blue}$, which we will see later evaluates as $\alpha_s$.
-Similarly, every red barbell is simply $\barbell{barbell_red} = \alpha_t$.
+Notice that, by combining homotopy and contraction (see Appendix~\ref{sec:prelim_genrel}), every blue barbell is simply $\barbell{barbell_blue}$.
+Similarly, every red barbell is simply $\barbell{barbell_red}$.
 
@@
 paths between the labelled vertices).
-The diagram is divided by these fences into \emph{pastures}, which will be numbered from left to right as $0$, $1$, \dots, $k$, where $k$ is the number of fences.
+The diagram is divided by these fences into \emph{pastures}.
 \end{definition*}
 \begin{definition*}
-	A component is called \emph{attached} if it is connected to a fence.  Otherwise, it is \emph{free}.  By convention, any attached components belong to the pasture to the left of the associated fence.
+	A component is called \emph{attached} if it is connected to a fence.
+Otherwise, it is \emph{free}.
+By convention, any attached components belong to the pasture to the left of the fence to which it is attached.
 \end{definition*}
@@
 \begin{definition*}
-	A \emph{bubble} is a bounded face alongside with any components contained within it.  The \emph{color} of the bubble is the color of the edges which form the bounded face.  
+	A \emph{bubble} is a bounded face alongside with any components contained within the face.  The \emph{color} of the bubble is the color of the edges which form the bounded face.  
 \end{definition*}
@@
 \begin{definition*}
-	A \emph{caterpillar} consists of a free component and the contents of any bubbles it contains.  A caterpillar \emph{holds} a component if some bubble of the caterpillar holds it.
+	A \emph{caterpillar} consists of a free component and the contents of any bubbles formed by its edges.  A caterpillar \emph{holds} a component if some bubble of the caterpillar holds it.
 \end{definition*}
@@
 	\ii The map $x \mapsto fx$ will be abbreviated as $f$ from this point forward.  
-	\par Note that, in particular, $\barbell{barbell_blue} = \alpha_s$.
+	\par Note that, in particular, $\barbell{barbell_blue} = \alpha_s$ follows from a straightforward computation.
 Furthermore, one can check that, say, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.
@@
 Hence, any full-diagram can be reduced to linear combinations of maps of the form $f \mapsto \alpha_s^m \alpha_t^n f$.
-In other words, every full diagram can be represented as a polynomial in $\RR[x,y][\alpha_s,\alpha_t]$.
+In other words, every full-diagram can be represented as a polynomial in $\RR[x,y][\alpha_s,\alpha_t]$.
 
@@
 \end{equation}
-where $\partial_s$ is the Demazure operator defined in Section~\ref{sec:prelim_genrel}.
+where $\partial_s$ is the Demazure operator defined in Appendix~\ref{sec:prelim_genrel}.
+
+For reference, Appendix~\ref{sec:ststs_matrix} contains a complete table of all maps of the form $\MM_{\AA_5} (\ul a, \ul b)$.
 
 \subsubsection{Quantum Numbers}
+\label{sec:quantum}
 A particularly nice sequence of polynomials involved can be defined recursively.  They are termed \emph{two-color quantum numbers}.
@@
 \end{definition*}
-The quantities $[n]_x$ and $[n]_y$ are closely related.  In particular, $[2k+1]_x = [2k+1]_y$ and $[2]_x[2k]_y = [2]_y[2k]_x$ for all integers $k$.
+The quantities $[n]_x$ and $[n]_y$ are closely related.  In particular, $[2k+1]_x = [2k+1]_y$ and $[2]_x[2k]_y = [2]_y[2k]_x$ for all integers $k$.  This follows immediately by induction.
 
@@
 One can verify \eqref{eq:quantum} immediately follows from definitions.
-This allows us to recursively compute the polynomial which results from pushing a barbell through multiple alternating fences.
+This gives us a robust way to express the results of action on $\alpha_s$ or $\alpha_t$ by elements of $W$.
 For example, $ststst(\alpha_s) = ststst([1]_x\alpha_s + [0]_y\alpha_t) = [7]_x\alpha_s + [6]_y\alpha_t$.
@@
 
-It is easy to observe that if $\ul r$ is a reduced expression of length $n+1$, then \[ \MM_{\ul r} ( \underbrace{11\dots11}_{\text{$n$ 1's}}0, \underbrace{11\dots11}_{\text{$n$ 1's}}0 ) = Q_{\ul r}.
-\]
+The significance is that, if $\ul r$ is a reduced expression of length $n+1$, then \[ \MM_{\ul r} ( \underbrace{11\dots11}_{\text{$n$ 1's}}0, \underbrace{11\dots11}_{\text{$n$ 1's}}0 ) = Q_{\ul r}. \]
+An illustration of such a full-map is given in Figure~\ref{fig:push_quantum}.
+This follows from \eqref{eq:barbell_break}.
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(4cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 5;
+
+		picture one;
+		draw(one, (4,0)--(4,h), s);
+		dot(one, (4,h), dot_s);
+		draw(one,(0,0)--(0,3*h), s);
+		draw(one,(1,0)--(1,3*h), t);
+		draw(one,(2,0)--(2,3*h), s);
+		draw(one,(3,0)--(3,3*h), t);
+
+		picture two;
+		draw(two, (4,0)--(4,h), s);
+		dot(two, (4,h), dot_s);
+		draw(two,(0,0)--(0,3*h), s);
+		draw(two,(1,0)--(1,3*h), t);
+		draw(two,(2,0)--(2,3*h), s);
+		draw(two,(3,0)--(3,3*h), t);
+
+		add(one); add(reflect((0,0),(1,0))*two);
+		draw((-1,0)--(5,0));
+	\end{asy}
+	\caption{$\MM(11110,11110)$.}
+	\label{fig:push_quantum}
+\end{figure}
 
@@
 \begin{definition*}
-	A map is \emph{idempotent} if multiplying it with itself returns the original graph.
+	A map is \emph{idempotent} if multiplying it with itself returns the original map.
 \end{definition*}
@@
 If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.
-This motivates us to construct potential idempotents by taking two light leaves whose top sequences are identical, and composing $A$ upside-down with $B$.
-If $AB=1$, then this will yield an idempotent.
+This motivates us to construct potential idempotents by taking two light leaves whose top sequences are identical, and composing $A$ upside-down with $B$, in the hope that $AB=1$.
 
@@
 \label{sec:res_onecolor}
-In this section we provide a complete characterization for the $\MM_{\SS_n}(\ul a, \ul b)$.
+In this section we provide a complete characterization for $\MM_{\SS_n}(\ul a, \ul b)$.
 % The proof is effectively trivial, but requires some rather irritating details and definitions in order to be clear.
@@
 \begin{definition*}
-	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
+	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$.
 \end{definition*}
@@
 			0 & \text{if }\ \exists 1 \le i \le n-1:\ \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
-			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}.
+			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) + \ul a^\ast[n]} & \text{otherwise}.
 		\end{cases}
@@
 The proof is essentially only a matter of finding loops and counting connected components.
-As such, it is deferred to in Appendix~\ref{sec:s_proof};
+As such, it is deferred to Appendix~\ref{sec:s_proof}.
 
@@
 We give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r}(\ul b) = \ul T$ for each expression $\ul T$ and $\ul r$.
-One can check that, by construction, $\Top(\ul b)$ is always a reduced expression.
 
@@
 This follows by induction on $n$.
-The main idea is that, for the binary strings of length $n$, we consider those that end with $1$ and those that end with $0$.
-Those that end with a $0$ have the same top when the trailing $0$ is deleted, whilst those with end bit $1$ have a top which differs by one character if the trailing $1$ is deleted.
-We simply check that in all eight cases, the binomial coefficients add up to give the new binomial coefficients (via Pascal's identity).
-The computation is left to a reader.
+The main idea is that, for the binary strings of length $n$ giving a top $T$, we consider those that end with $1$ and those that end with $0$.
+Using \eqref{eq:top}, we may then write the new quantity in terms of the number of strings of length $n-1$ with a different top.
+	% After deleting the last bit, the former type have a top which differs by one character according to $\AA_n[n]$, while the latter have the same top.
+	We simply check that in all eight cases, the binomial coefficients add up to give the new binomial coefficients (via Pascal's identity).  The computation is left to a diligent reader.
 
-	To finish to all cases, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there a $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
+	To finish the case $\ell \neq n$, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there a $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
 (This follows from Proposition \ref{prop:s_top}.)  This reduces to the previous case $\ul r = \AA_n$, but with some extra factors of $2$; aggregating all of them yields the factor of $2^{\ell-n}$, as desired.
@@
 \begin{lemma}[Caterpillar Lemma]
-	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
+	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ if it is red.
 	\label{thm:caterpillar}
@@
 		\ii Pastures $1$ through $N-1$ contain either nothing or an attached component.
-		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise, with color corresponding to $\AA_n[n]$.
+		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.  The caterpillar is blue if $\AA_n[n]$ is $s$, and red otherwise.
 	\end{enumerate}
@@
 \end{lemma}
+
+Included in Figure~\ref{fig:large_alt_example} is an example of a map with base $\AA_{27}$.   The Bubble Lemma and Pasture Lemma can be readily observed in this example.
+
+\begin{figure}[ht]
+	\centering
+	\begin{asy}
+		size(17cm);
+		real h = 0.7;
+		pen s = blue, t = red + dashed + 0.6;
+		pen dot_s = blue, dot_t = red;
+		int n = 27;
+
+		picture one;
+		draw(one, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
+		draw(one, (5,0)--(5,h/2)..((5+7)/2.0,h*2)..(7,h/2)--(7,0), t);
+		draw(one, (7,0)--(7,h/2)..((7+9)/2.0,h*2)..(9,h/2)--(9,0), t);
+		draw(one, (12,0)--(12,h/2)..((12+14)/2.0,h*2)..(14,h/2)--(14,0), s);
+		draw(one, (11,0)--(11,h/2)..((11+15)/2.0,h*4)..(15,h/2)--(15,0), t);
+		draw(one, (17,0)--(17,h/2)..((17+19)/2.0,h*2)..(19,h/2)--(19,0), t);
+		draw(one, (21,0)--(21,h/2)..((21+23)/2.0,h*2)..(23,h/2)--(23,0), t);
+		draw(one, (23,0)--(23,h/2)..((23+25)/2.0,h*2)..(25,h/2)--(25,0), t);
+		draw(one, (20,0)--(20,h/2)..((20+26)/2.0,h*6)..(26,h/2)--(26,0), s);
+		draw(one, (1,0)--(1,h), t);
+		dot(one, (1,h), dot_t);
+		draw(one, (3,0)--(3,h), t);
+		dot(one, (3,h), dot_t);
+		draw(one, (6,0)--(6,h), s);
+		dot(one, (6,h), dot_s);
+		draw(one, (8,0)--(8,h), s);
+		dot(one, (8,h), dot_s);
+		draw(one, (13,0)--(13,h), t);
+		dot(one, (13,h), dot_t);
+		draw(one, (18,0)--(18,h), s);
+		dot(one, (18,h), dot_s);
+		draw(one, (22,0)--(22,h), s);
+		dot(one, (22,h), dot_s);
+		draw(one, (24,0)--(24,h), s);
+		dot(one, (24,h), dot_s);
+		draw(one,(4,0)--(4,7*h), s);
+		draw(one,(9,0)--(9,7*h), t);
+		draw(one,(10,0)--(10,7*h), s);
+		draw(one,(15,0)--(15,7*h), t);
+		draw(one,(16,0)--(16,7*h), s);
+		draw(one,(19,0)--(19,7*h), t);
+		dot(one, (7, h/2), dot_t);
+		dot(one, (23, h/2), dot_t);
+		dot(one, (9, h/2), dot_t);
+		dot(one, (15, h/2), dot_t);
+		dot(one, (19, h/2), dot_t);
+
+		picture two;
+		draw(two, (5,0)--(5,h/2)..((5+7)/2.0,h*2)..(7,h/2)--(7,0), t);
+		draw(two, (7,0)--(7,h/2)..((7+9)/2.0,h*2)..(9,h/2)--(9,0), t);
+		draw(two, (12,0)--(12,h/2)..((12+14)/2.0,h*2)..(14,h/2)--(14,0), s);
+		draw(two, (14,0)--(14,h/2)..((14+16)/2.0,h*2)..(16,h/2)--(16,0), s);
+		draw(two, (17,0)--(17,h/2)..((17+19)/2.0,h*2)..(19,h/2)--(19,0), t);
+		draw(two, (21,0)--(21,h/2)..((21+23)/2.0,h*2)..(23,h/2)--(23,0), t);
+		draw(two, (23,0)--(23,h/2)..((23+25)/2.0,h*2)..(25,h/2)--(25,0), t);
+		draw(two, (20,0)--(20,h/2)..((20+26)/2.0,h*6)..(26,h/2)--(26,0), s);
+		draw(two, (0,0)--(0,h), s);
+		dot(two, (0,h), dot_s);
+		draw(two, (1,0)--(1,h), t);
+		dot(two, (1,h), dot_t);
+		draw(two, (2,0)--(2,h), s);
+		dot(two, (2,h), dot_s);
+		draw(two, (3,0)--(3,h), t);
+		dot(two, (3,h), dot_t);
+		draw(two, (6,0)--(6,h), s);
+		dot(two, (6,h), dot_s);
+		draw(two, (8,0)--(8,h), s);
+		dot(two, (8,h), dot_s);
+		draw(two, (13,0)--(13,h), t);
+		dot(two, (13,h), dot_t);
+		draw(two, (15,0)--(15,h), t);
+		dot(two, (15,h), dot_t);
+		draw(two, (18,0)--(18,h), s);
+		dot(two, (18,h), dot_s);
+		draw(two, (22,0)--(22,h), s);
+		dot(two, (22,h), dot_s);
+		draw(two, (24,0)--(24,h), s);
+		dot(two, (24,h), dot_s);
+		draw(two,(4,0)--(4,7*h), s);
+		draw(two,(9,0)--(9,7*h), t);
+		draw(two,(10,0)--(10,7*h), s);
+		draw(two,(11,0)--(11,7*h), t);
+		draw(two,(16,0)--(16,7*h), s);
+		draw(two,(19,0)--(19,7*h), t);
+		dot(two, (7, h/2), dot_t);
+		dot(two, (14, h/2), dot_s);
+		dot(two, (23, h/2), dot_t);
+		dot(two, (9, h/2), dot_t);
+		dot(two, (16, h/2), dot_s);
+		dot(two, (19, h/2), dot_t);
+
+		add(one); add(reflect((0,0),(1,0))*two);
+		draw((-1,0)--(27,0));
+	\end{asy}
+	\caption{A large map with base $\AA_{27}$.}
+	\label{fig:large_alt_example}
+\end{figure}
+
 The Bubble Lemma is the key combinatorial observation, which hinges on the fact that any two anchors with the same color have a third anchor of the other color between them.
@@
 \end{theorem}
+Here, $Q_T$ is the quantum polynomial defined in Section~\ref{sec:quantum}.
 \begin{proof}
@@
 Otherwise, there is a single caterpillar of color opposite to $T$, and hence after evaluating that caterpillar, we obtain some monomial times a single barbell.
-This generates the final $Q_T$ term.
+This generates the final $Q_T$ term after the barbell is pushed through all the fences; the broken fences are all zero because they are lower terms.
 \end{proof}
@@
 \begin{definition*}
-	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ will be called the \emph{fluff} of $M$, and the polynomial (either $1$ or $Q_T$) will be the \emph{face} of $M$.
+	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ will be called the \emph{fluff} of $M$, and the polynomial (either $1$ or $Q_T$) will be called the \emph{face} of $M$.
 \end{definition*}
@@
 	Let $n \ge 2$ be an odd integer and consider two binary strings $\ul a, \ul b \in \BB_n$ such that $T = \Top_{\AA_n}(\ul a) = \Top_{\AA_n}(\ul b)$.  
-	Let $\ul a'$ and $\ul b'$ are the first $n-1$ bits of $\ul a$ and $\ul b$, respectively. 
+	Let $\ul a'$ and $\ul b'$ be the first $n-1$ bits of $\ul a$ and $\ul b$, respectively. 
 	Suppose $M_1 = \MM_{\AA_{n-1}} \left(\ul a', \ul b'\right)$ is a nonzero map with fluff $F$.
@@
 		\[
-			\MM \AA_n (\ul a, \ul b)
+			\MM_{\AA_n} (\ul a, \ul b)
 			=

### 2013-07-29 appa.tex
where are my cannolis

@@
-% This is sec.tex
-%
-% This file is for appendices.  If you don't have any appendices, delete
-% the percent sign from the beginning of the next line.
-% \endinput
-
+% This is appa.tex
 \appendix
 
-% Add additional appendices by replicating the line below.
+%TODO restate all theorems
 
@@
 \label{sec:prelim_background}
-Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in a real Euclidean space $V$, and let $\alpha_s$ and $\alpha_t$ be arbitrary vectors normal to these planes.
+Let $V$ be a (real) Euclidean space endowed with a positive definite symmetric bilinear form $(\mu, \lambda)$.
+Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in $V$, and let $\alpha_s$ and $\alpha_t$ be arbitrary vectors normal to these planes.
 We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.
-In other words, $W$ is the infinite dihedral group with the presentation \[ W = \left<s,t \mid s^2=t^2=1\right>.
-\]
 
-If $V$ has a positive definite symmetric bilinear form $(\mu, \lambda)$, then for any $a \in V$, reflection over the hyperplane normal to $a$ can be written explicitly for each $v \in V$ as the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a.
-\]
+In other words, $W$ is the infinite dihedral group with the presentation \[ W = \left<s,t \mid s^2=t^2=1\right>. \]
+
+Then for any $a \in V$, reflection over the hyperplane normal to $a$ can be written explicitly for each $v \in V$ as the map \[ v \mapsto v - \frac{2(v,a)}{(a,a)} a. \]  
 In particular, if $W$ acts on $V$ by this reflection, $s(\alpha_s) = -\alpha_s$ and $t(\alpha_t) = -\alpha_t$.
@@
 \end{equation}
-These maps can be represented using diagrammatics, as below.
+These maps may be represented diagrammatically.
 
@@
 
-Consider a category $\DD$ whose elements are linear combinations $\sum c_i \square$ of the diagrams described below (where the boxes are diagrams).
+Consider a category $\DD$ whose elements are linear combinations $\sum c_i \square$ of the diagrams described below (where the $\square$'s are diagrams).
 The coefficients $c_i$ belong to the ring $\ZZ[x,y]$.
@@
 The maps are conventionally read from bottom to top.
-The labels on the upper and lower boundaries specify the domain and codomain of the map by simply transcribing the tensor products to take -- for example, a map with bottom $stt$ and top $s$ represents a map from $R \stimes R \ttimes R \ttimes R$ to $R \stimes R$.
+The labels on the upper and lower boundaries specify the domain and codomain of the map by ``transcribing'' the tensor products to take -- for example, a map with bottom $stt$ and top $s$ represents a map with domain $R \stimes R \ttimes R \ttimes R$ and codomain $R \stimes R$.
 An unlabelled domain corresponds to $R$.
 
-Let us hasten to introduce one final definition.
-\begin{definition*}
-	The \emph{Demazure operator} $\partial_s: R \to R$ is given by $\partial_s(f) = \frac{f - s(f)}{\alpha_s}$.
-\end{definition*}
+Let us introduce one final definition.
+\begin{definition}
+	The \emph{Demazure operator} $\partial_s: R \to R$ is given by \[ \partial_s(f) = \frac{f - s(f)}{\alpha_s}. \]
+\end{definition}
 
@@
 Therefore, by a combination of these structures, we can generate arbitrarily complicated maps.
-For example, the map in Figure~\ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d.
+For example, the diagram in Figure~\ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d.
 \]
@@
 \label{sec:prelim_genrel}
-From the algebraic context given above, one can derive the following relationships, which are here encoded completely graphically.  These rules are sufficient to compute the maps we are interested in.
+From the algebraic context given above, one can derive the following relationships, which are here described completely graphically.
+These rules are sufficient to compute the maps we are interested in.
+
+Unless multiple colors appear in an equation, blue represents a generic color.
 
@@
 \begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  \end{op}
-\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$ and the similar equation for red.  \end{op}
-\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$ and the similar equation for red.  \end{op}
-\begin{op}[The Needle] We have $\barbell{needle} = 0$.  Similarly, the red needle yields zero.  \end{op}
+\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$.  \end{op}
+\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$.  \end{op}
+\begin{op}[The Needle] We have $\barbell{needle} = 0$.  \end{op}
 \begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well.
@@
 
-Each bit of $\ul b$ is read from left to right in order and designated either up or down.
-We say that a bit $x$ is an \emph{open neighbor} of $y$ if $x$ is marked up, $x$ and $y$ have the same color, and there are no other bits marked up between $x$ and $y$.
+Each bit of $\ul b$ is read from left to right in order and designated either open or closed; the state of a bit can change more than once.
+Initially all bits are closed.
+We say that a bit $x$ is an \emph{open neighbor} of $y$ if $x$ is marked open, $x$ and $y$ have the same color, and there are no other bits marked open between $x$ and $y$.
+Note that each bit will have at most one open neighbor.
+
 \begin{itemize}
@@
 	\begin{itemize}
-		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, and mark both bits as down.
-		\ii Otherwise, designate the current bit as up.
+		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, and mark both bits as closed.
+		\ii Otherwise, designate the current bit as open.
 	\end{itemize}
@@
 	\begin{itemize}
-		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, mark the previous bit as down, and the current bit as up.
+		\ii If the current bit has an open neighbor, then draw an arc joining the two bits, mark the previous bit as closed, and the current bit as open.
 		\ii Otherwise, create a ``stub'', i.e. a single vertex of degree one, and mark the current bit as down.
@@
 \end{itemize}
-Finally, join any bits which are up at the end of the process to the upper boundary of the diagram.
+Finally, join any bits which are open at the end of the process to the upper boundary of the diagram.
 A map which arises in such a manner is called a \emph{light leaf}.
@@
 Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel} each other $k$ times if they have $k$ antennae in common.
-Notice that if any two components feel each other at least twice, then there exist two adjacent common antennae, whence the composition of the entire map is zero because the two antennae combine to form an empty bubble.
-Furthermore, it is easy to see that any bubbles must be formed in this manner.
+Notice that if any two components feel each other at least twice, then there exist two adjacent common antennae, forcing the composition of the entire map to be zero because the two antennae combine to form an empty bubble.
+Furthermore, it is evident that any bubbles must be formed in this manner.
 In combination with the claim above, this implies the first case of the theorem.
@@
 \subsection{Proof of the Bubble Lemma}
-We begin with a proof of the Bubble Lemma\footnote{I should remark that attempting to construct counterexamples to the Bubble Lemma leads to a far better understanding than trying to read the following proof.}, which is the crux result of the alternating case.
+We begin with a proof of the Bubble Lemma\footnote{I should remark that attempting to construct counterexamples to the Bubble Lemma leads to a far better understanding than trying to read the following proof.}, which is the fundamental lemma for the alternating case.
 Indeed, both of the subsequent lemmas are fairly straightforward consequences of this one.
@@
 	Take a bubble $B$ and assume without loss of generality that it is blue.
-It is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.
-Furthermore, it is evident that the bubble is nonempty; hence there is at least one red caterpillar in $B$.
-We will show that there is exactly one.
+By construction all caterpillars held inside $B$ must be red.
+This implies that there must be at least one red caterpillar, because there is at least one red anchor inside $B$.
 
@@
 Now, there must be some blue arc shielding $u$ and $v$ (since $u,v$ are inside a blue bubble).
-By the light-leave construction, there must be some red arc $A$ covering $x$.
+By construction, there must be some red arc $A$ covering $x$.
 If this arc joins $u$ and $v$, then we are done.
@@
 First, a few definitions for this section only.
-\begin{definition*}
+\begin{definition}
 	Consider a caterpillar $C$ in a full-diagram with base $\AA_n$.
@@
 Define the \emph{size} of the caterpillar to be the number of bubbles it contains.
-\end{definition*}
+\end{definition}
 
@@
 
-	It is easy to verify that the top of this new map is zero.
+	Clearly the top of this new map is zero, say by \eqref{eq:top}.
 Now what we have done is enclose the contents of each pasture into bubbles.

### 2013-07-29 paper.tex
where are my cannolis

@@
 Consider an expression $\ul r$.
-Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangeably) formed by the light leaves, as prescribed in Appendix~\ref{sec:prelim_lightleave}.
-We will refer to such structures as \emph{half-maps} or \emph{half-diagrams} should such a need arise.
+Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangeably) formed by the light leaves, as described in Appendix~\ref{sec:prelim_lightleave}.
+We will refer to such structures as \emph{half-maps} or \emph{half-diagrams}.
 Figure~\ref{fig:lightleaf_example} (in Appendix~\ref{sec:prelim_lightleave}) gives an example of such a half-map.
@@
 
-Such structures will analogously be called \emph{full-maps} or \emph{full-diagrams} for clarity.
-If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.
+Such structures will be called \emph{full-maps} or \emph{full-diagrams} for clarity.  If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.
 
@@
 	\end{asy}
-	\caption{Two blue barbells with a very twisted fence, which creates two pastures.}
+	\caption{Two red barbells with a very twisted fence, which creates two pastures.}
 	\label{fig:def_barbell_fence}
@@
 
-\begin{definition*}
+\begin{definition}
 	A connected component which (i) is acyclic, and (ii) does not touch the top or bottom boundaries is called a \emph{barbell}.
-\end{definition*}
+\end{definition}
 Notice that, by combining homotopy and contraction (see Appendix~\ref{sec:prelim_genrel}), every blue barbell is simply $\barbell{barbell_blue}$.
@@
 
-\begin{definition*}
+\begin{definition}
 	A \emph{fence} is a contiguous path which runs from the top of the boundary to the bottom of the boundary (i.e.
@@
 The diagram is divided by these fences into \emph{pastures}.
-\end{definition*}
-\begin{definition*}
+\end{definition}
+\begin{definition}
 	A component is called \emph{attached} if it is connected to a fence.
@@
 By convention, any attached components belong to the pasture to the left of the fence to which it is attached.
-\end{definition*}
+\end{definition}
 An example of a fence complete with two barbells is given in Figure~\ref{fig:def_barbell_fence}.
@@
 
-\begin{definition*}
-	A \emph{bubble} is a bounded face alongside with any components contained within the face.  The \emph{color} of the bubble is the color of the edges which form the bounded face.  
-\end{definition*}
-\begin{definition*}
+\begin{definition}
+	A \emph{bubble} is a bounded face along with any components contained within the face.  The \emph{color} of the bubble is the color of the edges which form the bounded face.  
+\end{definition}
+\begin{definition}
 	We say that the bubble $B$ \emph{holds} a component $c$ if $c$ is inside $B$, but there is no other bubble $B'$ inside $B$ which contains $c$.  
-\end{definition*}
+\end{definition}
 
@@
 
-\begin{definition*}
+\begin{definition}
 	A \emph{caterpillar} consists of a free component and the contents of any bubbles formed by its edges.  A caterpillar \emph{holds} a component if some bubble of the caterpillar holds it.
-\end{definition*}
+\end{definition}
 An example of a caterpillar is given in Figure~\ref{fig:def_caterpillar}.  Notice that any barbell or bubble is a special case of a caterpillar.
@@
 	\ii The map $x \mapsto fx$ will be abbreviated as $f$ from this point forward.  
-	\par Note that, in particular, $\barbell{barbell_blue} = \alpha_s$ follows from a straightforward computation.
+	\par In particular, the map $\barbell{barbell_blue}$ is $\alpha_s$.
+This follows from a straightforward computation.
 Furthermore, one can check that, say, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.
@@
 \label{sec:quantum}
-A particularly nice sequence of polynomials involved can be defined recursively.  They are termed \emph{two-color quantum numbers}.
-\begin{definition*}[Quantum Numbers]
+A particularly nice sequence of polynomials can be defined recursively.  They are termed \emph{two-color quantum numbers}.
+\begin{definition}[Quantum Numbers]
 	For each integer $n \ge 0$, define two polynomials $[n]_x, [n]_y \in \ZZ[x,y]$ recursively by $[0]_x = [0]_y = 0$, $[1]_x = [1]_y = 1$, $[2]_x = x$, $[2]_y = y$, and
@@
 	Finally, $[-n]_x = -[n]_x$ and $[-n]_y = -[n]_y$ for each $n \ge 0$.
-\end{definition*}
+\end{definition}
 The quantities $[n]_x$ and $[n]_y$ are closely related.  In particular, $[2k+1]_x = [2k+1]_y$ and $[2]_x[2k]_y = [2]_y[2k]_x$ for all integers $k$.  This follows immediately by induction.
@@
 and its analogous form for $t$.
-One can verify \eqref{eq:quantum} immediately follows from definitions.
+One can verify that \eqref{eq:quantum} immediately follows from definitions.
 This gives us a robust way to express the results of action on $\alpha_s$ or $\alpha_t$ by elements of $W$.
@@
 This motivates us to make the following definition, which will be used in Section~\ref{sec:res_alt_compute}.
-\begin{definition*}
+\begin{definition}
 	For any reduced expression $\ul r$, we define the quantum polynomial $Q_{\ul r}$ by :
@@
 	\]
-\end{definition*}
+\end{definition}
 
@@
 The motivation for this problem arises from the following definition.
-\begin{definition*}
+\begin{definition}
 	A map is \emph{idempotent} if multiplying it with itself returns the original map.
-\end{definition*}
-Colloquially, $m^2=m$ if and only if $m$ is idempotent.
-
+\end{definition}
 Fix an $\ul r$.
@@
 
-First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
-\begin{definition*}
+First, we need a criteria to determine the top.  Fortunately, this is not hard.
+\begin{definition}
 	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$.
-\end{definition*}
+\end{definition}
 \begin{proposition}
@@
 Subsequently, we make the following definition for this section only.
-\begin{definition*}
+\begin{definition}
 	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
@@
 	\]
-\end{definition*}
+\end{definition}
 This lets us state our main result for this section. 
@@
 
-\begin{definition*}
+\begin{definition}
 	Let $R(\ul r)$ denote $\ul r$ with any consecutive blocks of $s$'s replaced by a single $s$, and similarly for $t$.
-\end{definition*}
+\end{definition}
 For example, $R(sststttts) = ststs$.
@@
 	% After deleting the last bit, the former type have a top which differs by one character according to $\AA_n[n]$, while the latter have the same top.
-	We simply check that in all eight cases, the binomial coefficients add up to give the new binomial coefficients (via Pascal's identity).  The computation is left to a diligent reader.
+	We simply check that in all eight cases, the binomial coefficients add up to give the new binomial coefficients (via Pascal's identity).  The computation is left to the reader.
 
-	To finish the case $\ell \neq n$, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there a $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
+	To finish the case $\ell \neq n$, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there are $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
 (This follows from Proposition \ref{prop:s_top}.)  This reduces to the previous case $\ul r = \AA_n$, but with some extra factors of $2$; aggregating all of them yields the factor of $2^{\ell-n}$, as desired.
@@
 The Bubble Lemma is the key combinatorial observation, which hinges on the fact that any two anchors with the same color have a third anchor of the other color between them.
-The other two lemmas follow almost directly from it.
+The other two lemmas follow directly from it.
 The details of the proofs are given in Appendix~\ref{sec:lemmata_proof}.
@@
 This motivates the following definition, which is relevant for Proposition~\ref{thm:recurse}.
-\begin{definition*}
+\begin{definition}
 	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ will be called the \emph{fluff} of $M$, and the polynomial (either $1$ or $Q_T$) will be called the \emph{face} of $M$.
-\end{definition*}
+\end{definition}
 \begin{remark*}
@@
 \section{Acknowledgments} 
-I wish to thank the MIT Math Department for organizing the Math RSI, and in particular the head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me.
+I would like to thank my head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me, and the MIT Math Department for making my project possible.
 I also wish to thank my tutor Mr. Antoni Rangachev, Northeastern University, for his invaluable advice in preparing both this paper and my final presentation.
@@
 
-I would also like to thank my sponsors from RSI 2013:
+I would also like to thank my sponsors:
 \begin{inparaenum}[]
-	\ii Ms. Alexa Margalith, The Leonetti/O'Connell Family Foundation;
+	\ii Ms. Alexa Margalith, The Leonetti\slash O'Connell Family Foundation;
 	\ii Mr. Arvind Parthasarathi, YarcData;

### 2013-07-29 paper.tex
qq intro

@@
 
-We study a class of maps between Bott-Samelson bimodules.  
-Bott-Samelson bimodules arise from the study of Soergel bimodules, as mentioned in \cite{gr4all}, in the sense that a description of the category of maps between Bott-Samelson bimodules is sufficient to understand the corresponding category for the Soergel bimodules.
-However, the morphisms of Bott-Samelson bimodules admit a combinatorial description.
-In particular, \cite{gr4all} gives a presentation for the category of these morphisms in terms of planar diagrammatics (i.e.
+The Hecke Algebra (or Iwahori-Hecke Algebra) $\HH$ of a Weyl group $W$ is an object of significant interest, studied in representation theory, algebraic number theory, and combinatorics.
+
+In 1979, Kazhdan and Lusztig \cite{ref:KaLu1,ref:KaLu2} gave a categorification of $\HH$, using a construction involving a complicated structure known as perverse sheaves on the flag variety.
+The result became known as the Hecke category.
+% If $K = \RR$, the resulting basis of $\HH$ is understood, and called the Kazhdan-Lusztig basis.  However, if $K$ is a field of some other characteristic $p$, the basis is unknown.
+Soergel \cite{ref:Soe1,ref:Soe2} simplified this construction significantly in 1990 with an algebraic approach, using the aptly named Soergel bimodules.
+The Soergel bimodules permit an easier understanding of the categorification of $\HH$; their advantage is that they are easier to define and are combinatorial in nature.
+Furthermore, Soergel's construction extends the Hecke category to apply for arbitrary Coxeter systems $W$.
+
+For a full treatise, we refer the reader to \cite{ref:Humphreys}.
+
+Soergel bimodules can be described as summands of another class of bimodules, known as the \emph{Bott-Samelson bimodules}.
+Now the morphisms of Bott-Samelson bimodules admit a combinatorial description.
+In particular, \cite{ref:gr4all} gives a presentation for the category of these morphisms in terms of planar diagrammatics (i.e.
 diagrams in the plane).
@@
 This paper investigates some of the properties of these diagrammatics from a combinatorial perspective.
-However, in this paper, we consider only the special case of an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group).
+However, in this paper, we consider only the special case of an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).
 
-Given a sequence consisting of the letters $s$ and $t$ of length $n$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves, as detailed in Appendix~\ref{sec:prelim_lightleave}.
-These light leaves are interesting because they form a spanning set for the maps we are interested in, as shown in \cite{gr4all}.
-The project deals with composing two maps formed in such a manner.
-The goal of the project is to describe the relationship between such a composition and the two original binary strings.
+Given a string of length $n$ composed of the letters $s$ and $t$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves.
+The light leaves were derived by Libednisky in \cite{ref:Lib} and are detailed in Appendix~\ref{sec:prelim_lightleave}.
+These light leaves are interesting because they form a basis for a certain span of maps, as shown in \cite{ref:gr4all}.
+We develop tools to understand the composition of two such maps given the original binary strings, with the eventual goal of deriving a combinatorial formula.
+%The project deals with composing two maps formed in such a manner.
+%The goal of the project is to describe the relationship between such a composition and the two original binary strings.
 
-The technical description of the problem statement is quite involved.
-Thusly, the preliminaries for the problem are given in Appendix~\ref{sec:prelim_background}, while the definitions used in this paper are recorded in Section~\ref{sec:prelim}.
-The problem statement is given in Section~\ref{sec:probstate}.
+The preliminaries for the problem -- namely, the light leaves and their algebraic meaning -- are given in Appendix~\ref{sec:prelim_background}.
+A minimal set of definitions used in this paper are given in Section~\ref{sec:prelim}.
+The problem statement in its full technicality is given in Section~\ref{sec:probstate}.
+
 The results begin by solving the special case of one color completely in Section~\ref{sec:res_onecolor}.
 In Section~\ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.
-The most interesting results are in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate the case where the given string is $ststst\cdots$.
+The most interesting results are in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate a special ``alternating'' case.
 In particular, we show that the possible resulting structures are extremely limited, and provide a recursion based on these restrictions for that case.

### 2013-07-30 paper.tex
lol intro

@@
 
-For a full treatise, we refer the reader to \cite{ref:Humphreys}.
+For a full treatise on the topic, we refer the reader to \cite{ref:Humphreys}.
 
@@
 \label{sec:probstate}
+\begin{definition}
+	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are orthogonal if their product is zero.
+\end{definition}
+Fix an expression $\ul r$.
+If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.
+More generally, however, if $AB = c$ for some scalar $c$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.
+In other words, any two maps with nonzero product can be used to construct an idempotent.
 
-The motivation for this problem arises from the following definition.
-\begin{definition}
-	A map is \emph{idempotent} if multiplying it with itself returns the original map.
-\end{definition}
-Fix an $\ul r$.
-If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.
-This motivates us to construct potential idempotents by taking two light leaves whose top sequences are identical, and composing $A$ upside-down with $B$, in the hope that $AB=1$.
+However, if we are interested in finding sets of pairwise orthogonal idempotents, then this becomes a linear algebra problem in which we require a matrix of all possible products.
+The construction of such a set of idempotents is closely related to the decomposition of these bimodules, which in turn gives information about the Soergel bimodules\footnote{Actually, the Soergel bimodules may be defined as the images of idempotents in the endomorphism rings of the Bott-Samelson bimodules.}.
 

### 2013-07-30 appa.tex
qq intro
8 hours qq

@@
 \appendix
-
-%TODO restate all theorems
 
@@
 Let $W$ be a group with two generators $s$ and $t$ corresponding to reflecting over two hyperplanes in $V$, and let $\alpha_s$ and $\alpha_t$ be arbitrary vectors normal to these planes.
-We will assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.
+We assume that the angle formed by $\alpha_s$ and $\alpha_t$ is not a rational multiple of $\pi$, so that the order of $st$ in $W$ is infinite.
 
@@
 \[ R \otimes_{R^{i_1}} R \otimes_{R^{i_2}} R \otimes_{R^{i_3}} \dots \otimes_{R^{i_n}} R, \]
-where each $i_j$ is either $s$ or $t$.   Elements of such a bimodule will be written in the form $f_0 \mid f_1 \mid \dots \mid f_n$, where $f_i \in R$.
+where each $i_j$ is either $s$ or $t$.   We write elements of such a bimodule in the form $f_0 \mid f_1 \mid \dots \mid f_n$, where $f_i \in R$.
 
-We will consider maps between these bimodules that preserve left and right actions; that is, we consider the maps $\sigma$ such that
+We consider maps between these bimodules that preserve left and right actions; that is, we consider the maps $\sigma$ such that
 \begin{equation}
@@
 \subsection{Algebraic Context}
+\label{sec:prelim_alg_context}
 The maps are conventionally read from bottom to top.
@@
 
-Maps are composed by juxtaposition, and disjoint portions of the diagrams act independently.
-Therefore, by a combination of these structures, we can generate arbitrarily complicated maps.
-For example, the diagram in Figure~\ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d.
-\]
+Maps are composed by juxtaposition, and disjoint portions of the diagrams act independently.  Therefore, by a combination of these structures, we can generate arbitrarily complicated maps.  
+\begin{example*}
+	The diagram in Figure~\ref{fig:example_diagram} represents a map \[ R \stimes R \ttimes R \stimes R \to R \stimes R \quad\text{by}\quad a \mid b \mid c \mid d \mapsto a \partial_s(bc) \mid d. \]
+\end{example*}
 
@@
 \setcounter{op}{-1}
-\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  \end{op}
+\begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  In other words, the maps are isotropy invariant  \end{op}
+The reasons for the above operation are not obvious; see page 7 of \cite{ref:gr4all} for an explanation.
 \begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$.  \end{op}
@@
 We now present the algorithm for Libedinsky's light leaves, in the special case where $W$ is the infinite dihedral group.
-A full construction for more general Coxeter groups is given in \cite{gr4all}.
+A full construction for more general Coxeter groups is given in \cite{ref:gr4all}.
 
-Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any binary string $\ul b$ of length $n$, we can construct a diagram based on a series of rules.
+Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any binary string $\ul b$ of length $n$ we can construct a diagram based on a series of rules.
 
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:s_eval}]
+\onecolor*
+\begin{proof}[Proof of Theorem \ref{thm:onecolor}]
 	We will only consider the case where $\Top(\ul a) = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.
@@
 
-	Number the anchors $1,2,\dots,n$ $1,2,\dots,n$ $1,2,\dots,n$ $1,2,\dots,n$ from left to right.
-
+	Number the anchors $1,2,\dots,n$ from left to right.
 For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.
@@
 
+\section{Computation for Map Counting}
+\label{sec:count_map_computation}
+\countmaps*
+The main idea of the proof was given earlier on page~\pageref{thm:count_maps}.  Here are the details.
+
+\begin{proof}[Proof of Proposition \ref{thm:count_maps}]
+	First we resolve the case where $\ul r = \AA_n$, so that $\ell = n$ and $2^{\ell-n} = 1$.
+We proceed by induction on $n \ge 1$ and consider eight cases.
+(The base case is trivial.) The strategy for each is that, for the binary strings of length $n$ and top $T$, we consider those binary strings which end with $1$ and those which end with $0$.
+Using \eqref{eq:top}, we may then write the new quantity in terms of the number of strings of length $n-1$ with a different top.
+
+	When $n = 2k+1$, we have $\AA_n[n] = s$ and $n-1 = 2k$.  Let $\ul b'$ denote the first $n-1$ characters of $\ul b$.  Then,
+	\newcommand{\aoeu}[5]{The top #1 ends in #2.  So, if $\ul b[n] = 1$ then we have top #3 for $\ul b'$, and otherwise $\ul b'$ has the same top #4.  In total, we get #5.}
+	\begin{itemize}
+		\ii \aoeu{$\AA_{2m+1}$}{$s$}{$\AA_{2m} = \AA_{2(m-1)+2}$}{$\AA_{2m+1}$}%
+		{$\binom{n-2}{(m-1)+k} + \binom{n-2}{m+k} = \binom{n-1}{m+k}$}
+		\ii \aoeu{$\AA_{2m}$}{$t$}{$\AA_{2m+1}$}{$\AA_{2m} = \AA_{2(m-1)+2}$}%
+		{$\binom{n-2}{m+k} + \binom{n-2}{(m-1)+k} = \binom{n-1}{m+k}$}
+		\ii \aoeu{$\AA_{2m-1}'$}{$t$}{$\AA_{2m}'$}{$\AA_{2m-1}' = \AA_{2(m-1)+1}'$}%
+		{$\binom{n-2}{m+k} + \binom{n-2}{(m-1)+k} = \binom{n-1}{m+k}$}
+		\ii \aoeu{$\AA_{2m}'$}{$s$}{$\AA_{2m-1}' = \AA_{2(m-1)+1}'$}{$\AA_{2m}'$}%
+		{$\binom{n-2}{(m-1)+k} + \binom{n-2}{m+k} = \binom{n-1}{m+k}$}
+	\end{itemize}
+	The case where $n=2k$ is similar, but $n-1=2(k-1)+1$.  Now the last bit changes the top by $t$.
+	\begin{itemize}
+		\ii \aoeu{$\AA_{2m+1}$}{$s$}{$\AA_{2m+2} = \AA_{2(m+1)}$}{$\AA_{2m+1}$}%
+		{$\binom{n-2}{(m+1)+(k-1)} + \binom{n-2}{m+(k-1)} = \binom{n-1}{m+k}$}
+		\ii \aoeu{$\AA_{2m+2}$}{$t$}{$\AA_{2m+1}$}{$\AA_{2m+2} = \AA_{2(m+1)}$}%
+		{$\binom{n-2}{m+(k-1)} + \binom{n-2}{(m+1)+(k-1)} = \binom{n-1}{m+k}$}
+		\ii \aoeu{$\AA_{2m}'$}{$s$}{$\AA_{2m+1}' = \AA_{2(m+1)-1}'$}{$\AA_{2m}'$}%
+		{$\binom{n-2}{(m+1)+(k-1)} + \binom{n-2}{m+(k-1)} = \binom{n-1}{m+k}$}
+		\ii \aoeu{$\AA_{2m+1}'$}{$t$}{$\AA_{2m}'$}{$\AA_{2m+1}'=\AA_{2(m+1)-1}'$}%
+		{$\binom{n-2}{m+(k-1)} + \binom{n-2}{(m+1)+(k-1)} = \binom{n-1}{m+k}$}
+	\end{itemize}
+	This completes the inductive step.  Hence, the proposition is true for $\ell = n$.
+
+	To finish the case $\ell \neq n$, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there are $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
+(This follows from Proposition~\ref{prop:s_top}.)  This reduces to the previous case $\ul r = \AA_n$ multiplied by additional factors of $2$; aggregating all of them yields the factor of $2^{\ell-n}$, as desired.
+\end{proof}
+
 \section{Proofs of Lemmata}
@@
 
+\bubble*
 \begin{proof}[Proof of Lemma \ref{thm:bubble}]
@@
 We will now derive the Caterpillar Lemma as a consequence of the Bubble Lemma.  
+\caterpillar*
 
@@
 The Bubble Lemma and the Pasture Lemma are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Lemma follows from the Bubble Lemma.
+
+\pasture*
 \begin{proof}[Proof of Lemma \ref{thm:pasture}]
@@
 \label{sec:recurse_proof}
+\recurse*
 \begin{proof}[Proof of Proposition \ref{thm:recurse}]

### 2013-07-30 paper.tex
8 hours qq

@@
 % This is paper.tex
+
+% TODO restate all theorems in appendix
+% TODO rewrite summary
+
 \section{Introduction}
@@
 
-In 1979, Kazhdan and Lusztig \cite{ref:KaLu1,ref:KaLu2} gave a categorification of $\HH$, using a construction involving a complicated structure known as perverse sheaves on the flag variety.
+In 1979, Kazhdan and Lusztig \cite{ref:KaLu1,ref:KaLu2} gave a categorification of $\HH$, using a somewhat complicated construction\footnote{The technique involved using something called \emph{perverse sheaves on the flag variety}.}.
 The result became known as the Hecke category.
@@
 The Soergel bimodules permit an easier understanding of the categorification of $\HH$; their advantage is that they are easier to define and are combinatorial in nature.
-Furthermore, Soergel's construction extends the Hecke category to apply for arbitrary Coxeter systems $W$.
+Furthermore, Soergel's construction extends the Hecke category to the case where $W$ is an arbitrary Coxeter group, as opposed to a Weyl group.
 
-For a full treatise on the topic, we refer the reader to \cite{ref:Humphreys}.
+For a full treatise on the topic, we refer the reader to Humphreys \cite{ref:Humphreys}.
 
@@
 Now the morphisms of Bott-Samelson bimodules admit a combinatorial description.
-In particular, \cite{ref:gr4all} gives a presentation for the category of these morphisms in terms of planar diagrammatics (i.e.
-diagrams in the plane).
+In particular, Elias and Williamson \cite{ref:gr4all}, building off earlier works such as Elias and Khovanov \cite{ref:EKh}, give a presentation for the category of these morphisms in terms of colored planar diagrammatics (i.e.
+colored planar graphs).
 
 This paper investigates some of the properties of these diagrammatics from a combinatorial perspective.
-However, in this paper, we consider only the special case of an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).
+In this paper, we consider only the special case where $W$ is an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).
 
 Given a string of length $n$ composed of the letters $s$ and $t$, as well as a binary string of length $n$, one can construct such a diagram using an algorithm known as Libedinsky's light leaves.
-The light leaves were derived by Libednisky in \cite{ref:Lib} and are detailed in Appendix~\ref{sec:prelim_lightleave}.
-These light leaves are interesting because they form a basis for a certain span of maps, as shown in \cite{ref:gr4all}.
+The light leaves were derived by Libedinsky in \cite{ref:Lib} and are detailed in Appendix~\ref{sec:prelim_lightleave}.
+These light leaves are interesting because they form a basis for a certain span of these maps, as shown in \cite{ref:gr4all}.
 We develop tools to understand the composition of two such maps given the original binary strings, with the eventual goal of deriving a combinatorial formula.
@@
 
-The preliminaries for the problem -- namely, the light leaves and their algebraic meaning -- are given in Appendix~\ref{sec:prelim_background}.
-A minimal set of definitions used in this paper are given in Section~\ref{sec:prelim}.
-The problem statement in its full technicality is given in Section~\ref{sec:probstate}.
+Appendix~\ref{sec:prelim_background} contains the preliminaries for the problem -- namely, the light leaves and the relation between the diagrams and maps.
+A minimal set of definitions used in this paper is given in Section~\ref{sec:prelim}.
+In Section~\ref{sec:probstate}, the problem statement is given in its full technicality.
 
@@
 In Section~\ref{sec:res_count_maps}, we also present a formula for the number of maps between two given bimodules.
-The most interesting results are in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate a special ``alternating'' case.
+The most important results of this paper are presented in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate a special ``alternating'' case.
 In particular, we show that the possible resulting structures are extremely limited, and provide a recursion based on these restrictions for that case.
@@
 
-In Section~\ref{sec:prelim_def_notation}, we introduce several of our definitions which we use throughout the paper.
+In Section~\ref{sec:prelim_def_notation} we introduce several of our definitions which we use throughout the paper.
 Next, in Section~\ref{sec:prelim_explain_poly_eval}, we describe how these maps can be represented as polynomials.
@@
 \]
-Similarly, let $\AA_n'$ denote $\AA_n$, except with the roles of $s$ and $t$ switched.  Note that $\AA_0 = \AA_0' = \varnothing$.
+Similarly, let $\AA_n'$ denote the string obtained by switching $s$ with $t$ in $\AA_n$.  Note that $\AA_0 = \AA_0' = \varnothing$.
 
 In general, a string of $s$'s and $t$'s will be referred to as an \emph{expression}.
-In the case where there are no consecutive identical characters (in other words, the string is either $\AA_n$ or $\AA_n'$), we will refer to them as \emph{reduced expressions}.
+In the case where there are no consecutive identical characters (in other words, the string is either $\AA_n$ or $\AA_n'$), we refer to them as \emph{reduced expressions}.
 
@@
 
-Finally, given a string $\ul x$ (either a binary string or an expression) we will denote the $i\th$ character as $\ul x[i]$.  In general, underlined Roman letters denote strings.
+Finally, given a string $\ul x$ (either a binary string or an expression), let $\ul x[i]$ denote the $i\th$ character.  In general, underlined Roman letters denote strings.
 
@@
 Consider an expression $\ul r$.
-Given a binary string $\ul b$, we will let $\MM_{\ul r}(\ul b)$ denote the map (or its associated diagram; we will refer to maps and their associated diagrams interchangeably) formed by the light leaves, as described in Appendix~\ref{sec:prelim_lightleave}.
-We will refer to such structures as \emph{half-maps} or \emph{half-diagrams}.
-Figure~\ref{fig:lightleaf_example} (in Appendix~\ref{sec:prelim_lightleave}) gives an example of such a half-map.
+Given a binary string $\ul b$, let $\MM_{\ul r}(\ul b)$ denote the map formed by the light leaves, as described in Appendix~\ref{sec:prelim_lightleave}.
+We refer to maps and their associated diagrams interchangeably.
 
-Additionally, let $\Top_{\ul r}(\ul b)$ denote the \emph{top} of the half-diagram $\MM_{\ul r}(\ul b)$, as described in Appendix~\ref{sec:prelim_lightleave}.  
+Maps constructed by the light leaves are called \emph{half-maps} or \emph{half-diagrams} (since subsequently we compose pairs of them).
+Figure~\ref{fig:lightleaf_example} (in Appendix~\ref{sec:prelim_lightleave}, on page~\pageref{sec:prelim_lightleave}) gives an example of such a half-map.
+
+Additionally, let $\Top_{\ul r}(\ul b)$ denote the \emph{top} of the half-diagram $\MM_{\ul r}(\ul b)$, as defined in Appendix~\ref{sec:prelim_lightleave}.  
 Note that the top of any half-map is always a reduced expression.  In fact, one can verify that the top of a map is given explicitly by
@@
 Two maps $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ with identical tops may be composed by juxtaposing $\MM_{\ul r}(\ul a)$ with a flipped copy of $\MM_{\ul r}(\ul b)$; an example of such a composition is given in Figure~\ref{fig:example_compose}.
-We will denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
-If the two half-maps are not compatible (that is, $\Top_{\ul r}(\ul a) \neq \Top_{\ul r}(\ul b)$) then we will simply set $\MM_{\ul r}(\ul a, \ul b) = 0$.
+We denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
+If the two half-maps are not compatible (that is, $\Top_{\ul r}(\ul a) \neq \Top_{\ul r}(\ul b)$) then we simply set $\MM_{\ul r}(\ul a, \ul b) = 0$.
 
-Such structures will be called \emph{full-maps} or \emph{full-diagrams} for clarity.  If $\ul r$ is clear from context, we will abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.
+Such structures are called \emph{full-maps} or \emph{full-diagrams} for clarity.  If $\ul r$ is clear from context, we abbreviate $\MM_{\ul r}$ as simply $\MM$ and $\Top_{\ul r}$ as $\Top$.
 
 Recall that the light leaves are based off a sequence of vertices at the bottom boundary of a half-map.
-We will call those vertices, whether on the bottom boundary of a half-map or the center of a full-map, the \emph{anchors} for that map, and the associated sequence of letters the \emph{base}.
+We call these vertices, whether on the bottom boundary of a half-map or the center of a full-map, the \emph{anchors} for that map, and the associated sequence of letters the \emph{base}.
 
@@
 	A component is called \emph{attached} if it is connected to a fence.
-Otherwise, it is \emph{free}.
+Otherwise, it is called \emph{free}.
 By convention, any attached components belong to the pasture to the left of the fence to which it is attached.
@@
 \label{sec:prelim_explain_poly_eval}
+Recall that every diagram represents a map using the generators and relations in Appendix~\ref{sec:prelim_alg_context} and Appendix~\ref{sec:prelim_genrel}.
 
@@
 \begin{enumerate}
-	\ii The map $x \mapsto fx$ will be abbreviated as $f$ from this point forward.  
+	\ii For any $f \in R$, the map $x \mapsto fx$ (i.e. multiplication on the left) will be abbreviated as $f$ from this point forward.  
 	\par In particular, the map $\barbell{barbell_blue}$ is $\alpha_s$.
 This follows from a straightforward computation.
-Furthermore, one can check that, say, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.
-	Please note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \alpha_s$.
-	\ii We will work \emph{modulo lower terms}.
+Furthermore, one can check that, for example, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.
+	Note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \alpha_s$.
+	\ii We work \emph{modulo lower terms}.
 That is, any map which contains a connected component that touches any boundary only once (total) is considered zero.
@@
 \end{enumerate}
-Henceforth, we will refer to diagrams and their associated polynomials interchangeably.
+Henceforth, we refer to diagrams and their associated polynomials interchangeably.
 
@@
 \label{sec:quantum}
-A particularly nice sequence of polynomials can be defined recursively.  They are termed \emph{two-color quantum numbers}.
+A particularly nice sequence of polynomials can be defined recursively.  These polynomials are termed \emph{two-color quantum numbers}.
 \begin{definition}[Quantum Numbers]
@@
 \end{definition}
+As an example, $[3]_x = [2]_x[2]_y+[1]_x = xy+1$.
+
 The quantities $[n]_x$ and $[n]_y$ are closely related.  In particular, $[2k+1]_x = [2k+1]_y$ and $[2]_x[2k]_y = [2]_y[2k]_x$ for all integers $k$.  This follows immediately by induction.
 
-The quantum numbers are relevant to the problem because of the identity
+Recall that the generators $s$ and $t$ of $W$ act on $R$ by the action given in Appendix~\ref{sec:prelim_background}.  The quantum numbers are relevant to the problem because of the identity
 \begin{equation}
@@
 One can verify that \eqref{eq:quantum} immediately follows from definitions.
-This gives us a robust way to express the results of action on $\alpha_s$ or $\alpha_t$ by elements of $W$.
+This gives us a robust way to express the results of action on $\alpha_s$ or $\alpha_t$ by the elements of $W$.
 For example, $ststst(\alpha_s) = ststst([1]_x\alpha_s + [0]_y\alpha_t) = [7]_x\alpha_s + [6]_y\alpha_t$.
 
-This motivates us to make the following definition, which will be used in Section~\ref{sec:res_alt_compute}.
+This motivates us to make the following definition, which we use in Section~\ref{sec:res_alt_compute}.
 \begin{definition}
-	For any reduced expression $\ul r$, we define the quantum polynomial $Q_{\ul r}$ by :
+	For any reduced expression $\ul r$, we define the quantum polynomial $Q_{\ul r}$ by:
 	\[
@@
 Fix an expression $\ul r$.
-If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ will be an idempotent.
+If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.
 More generally, however, if $AB = c$ for some scalar $c$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.
@@
 
-This motivates the main objective of study.
+This motivates the main objective of our study.
 \begin{ques*}
@@
 \end{ques*}
-Here, we are interested in computing the polynomial which corresponds to this map.
+In this paper, we are interested in computing the polynomial which corresponds to this map.
 
@@
 
-First, we need a criteria to determine the top.  Fortunately, this is not hard.
+First, we need a criteria to determine the top of such compositions.
 \begin{definition}
@@
 \end{definition}
-This lets us state our main result for this section. 
-\begin{theorem}
-	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n}(\ul a) = \Top_{\SS_n}(\ul b)$, then
+We are now ready to state our main result for this section. 
+\begin{restatable}[One-Color Theorem]{theorem}{onecolor}
+	If $\ul a, \ul b \in \BB_n$ satisfy $\Top_{\SS_n}(\ul a) = \Top_{\SS_n}(\ul b)$, then
 	\[
@@
 		\begin{cases}
-			0 & \text{if }\ \exists 1 \le i \le n-1:\ \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
+			0 & \text{if there exists } 1 \le i \le n-1:\ \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
 			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) + \ul a^\ast[n]} & \text{otherwise}.
@@
 	\]
-	\label{thm:s_eval}
-\end{theorem}
+	\label{thm:onecolor}
+\end{restatable}
 The proof is essentially only a matter of finding loops and counting connected components.
-As such, it is deferred to Appendix~\ref{sec:s_proof}.
+As such, it is deferred to Appendix~\ref{sec:s_proof}, on page \pageref{sec:s_proof}.
 
@@
 
-\begin{proposition}
+\begin{restatable}{proposition}{countmaps}
 	Let $\ul r$ be an expression of length $\ell$, and suppose $R(\ul r) = \AA_n$.
 	\begin{enumerate}[(i)]
-		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r}(\ul b)$.
-		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r}(\ul b)$.
+		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{n-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r}(\ul b)$.
+		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{n-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r}(\ul b)$.
 	\end{enumerate}
 	\label{thm:count_maps}
-\end{proposition}
-Of course, if $\ul r$ begins with the character $t$, then one can simply reverse the roles of $s$ and $t$ in the above theorem to obtain an analogous formula.
+\end{restatable}
+If $\ul r$ begins with the character $t$, then one can simply reverse the roles of $s$ and $t$ in the above theorem to obtain an analogous formula.
 
-The main idea of the proof is to reduce the problem to the case when $\ell = n$, and then apply induction on $n$.  We fill in the details below.
-
-\begin{proof}[Proof of Proposition \ref{thm:count_maps}]
-	First we will resolve the case where $\ul r = \AA_n$, so that $\ell = n$ and $2^{\ell-n} = 1$.
-This follows by induction on $n$.
-The main idea is that, for the binary strings of length $n$ giving a top $T$, we consider those that end with $1$ and those that end with $0$.
-Using \eqref{eq:top}, we may then write the new quantity in terms of the number of strings of length $n-1$ with a different top.
-	% After deleting the last bit, the former type have a top which differs by one character according to $\AA_n[n]$, while the latter have the same top.
-	We simply check that in all eight cases, the binomial coefficients add up to give the new binomial coefficients (via Pascal's identity).  The computation is left to the reader.
-
-	To finish the case $\ell \neq n$, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there are $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.
-(This follows from Proposition \ref{prop:s_top}.)  This reduces to the previous case $\ul r = \AA_n$, but with some extra factors of $2$; aggregating all of them yields the factor of $2^{\ell-n}$, as desired.
-\end{proof}
+The proof proceeds in two steps.
+The first is to resolve the case $\ell = n$.
+We do so by using induction on $n$, and applying \eqref{eq:top}.
+By splitting into the case where $\ul b[n] = 1$ and $\ul b[n] = 0$, we get two binomial coefficients; the computation is to verify that by Pascal's identity they sum to the desired coefficient.
+The second step is to reduce the case where $\ell \neq n$ to the previous step using Proposition~\ref{prop:s_top}.
+We give the proof in Appendix~\ref{sec:count_map_computation}, on page~\pageref{sec:count_map_computation}.
 
@@
 
-We now present three results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  
-\begin{lemma}[Bubble Lemma]
+Below we present three results which show that the possible outputs of a map with base $\AA_n$ are structurally very limited.
+\begin{restatable}[Bubble Lemma]{lemma}{bubble}
 	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
 	\label{thm:bubble}
-\end{lemma}
-\begin{lemma}[Caterpillar Lemma]
+\end{restatable}
+\begin{restatable}[Caterpillar Lemma]{lemma}{caterpillar}
 	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ if it is red.
 	\label{thm:caterpillar}
-\end{lemma}
-\begin{lemma}[Pasture Lemma]
-	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
+\end{restatable}
+\begin{restatable}[Pasture Lemma]{lemma}{pasture}
+	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then
 	\begin{enumerate}[(i)]
-		\ii Pastures $1$ through $N-1$ contain either nothing or an attached component.
-		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.  The caterpillar is blue if $\AA_n[n]$ is $s$, and red otherwise.
+		\ii Pastures $1$ through $N-1$ are either empty or contain an attached component.
+		\ii Pasture $N$ is empty if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.  The caterpillar is blue if $\AA_n[n]$ is $s$, and red otherwise.
 	\end{enumerate}
 	\label{thm:pasture}
-\end{lemma}
+\end{restatable}
 
@@
 The other two lemmas follow directly from it.
-The details of the proofs are given in Appendix~\ref{sec:lemmata_proof}.
+The details of the proofs are given in Appendix~\ref{sec:lemmata_proof}, on page~\pageref{sec:lemmata_proof}.
 
@@
 \label{sec:res_alt_compute}
-We now turn to using the tools developed in Section~\ref{sec:res_alt_restrict} in order to compute polynomials. First, we add some structure to these special cases.
+We now turn to using the tools developed in Section~\ref{sec:res_alt_restrict} in order to compute polynomials.
 
@@
 
-This motivates the following definition, which is relevant for Proposition~\ref{thm:recurse}.
+Theorem~\ref{thm:alt_struct} motivates the following definition, which is relevant for Proposition~\ref{thm:recurse}.
 \begin{definition}
-	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ will be called the \emph{fluff} of $M$, and the polynomial (either $1$ or $Q_T$) will be called the \emph{face} of $M$.
+	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then we call the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ the \emph{fluff} of $M$, and call the polynomial (either $1$ or $Q_T$) the \emph{face} of $M$.
 \end{definition}
@@
 \subsection{A Partial Recursion}
-In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.
+In this section we present a partial recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.
 
-\begin{proposition}
+\begin{restatable}{proposition}{recurse}
 	Let $n \ge 2$ be an odd integer and consider two binary strings $\ul a, \ul b \in \BB_n$ such that $T = \Top_{\AA_n}(\ul a) = \Top_{\AA_n}(\ul b)$.  
@@
 	\label{thm:recurse}
-\end{proposition}
-The recursion arises because, using the lemmata, we are able to see exactly what happens in the rightmost pasture if a pair of $1$'s or a pair of $0$'s is added.
+\end{restatable}
+The recursion arises because, using the lemmata of Section~\ref{sec:res_alt_restrict}, we are able to see exactly what happens in the rightmost pasture if a pair of $1$'s or a pair of $0$'s is added.
 In short, either a barbell or fence is added on the far right, or a caterpillar is enclosed in a bubble; each of these leads to one of the cases above.
-The full computation is given in Appendix~\ref{sec:recurse_proof}.
+The full computation is given in Appendix~\ref{sec:recurse_proof}, on page \pageref{sec:recurse_proof}.
 
@@
 The overarching goal of the paper was to compute $\MM_{\ul r} (\ul a, \ul b)$ in terms of $\ul r$, $\ul a$, and $\ul b$.
-In this paper, we solved the case where $\ul r = \SS_n$ completely, and showed that the case where $\ul r = \AA_n$ is significantly restricted.
+In this paper, we solved the case where $\ul r = \SS_n$ completely, and showed that outputs in the case $\ul r = \AA_n$ are substantially constrained.
 We also provide a partial recurrence for $\AA_n$.
-One obvious next direction would be to attempt to complete the recursion for $\AA_n$ so that $\MM_{\AA_n} (\ul a, \ul b)$ can be determined completely.
+An obvious next direction would be to attempt to complete the recursion for $\AA_n$ so that $\MM_{\AA_n} (\ul a, \ul b)$ can be determined completely.
 
@@
 \section{Acknowledgments} 
-I would like to thank my head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me, and the MIT Math Department for making my project possible.
+I offer my sincerest gratitude to my mentor Mr.
+Francisco Unda, MIT, for daily mentorship, and Professor Benjamin Elias, MIT, for providing the project and for often meeting with me personally to discuss it.
+That sounded horribly fake, but I really mean it.
+You guys are the best.
+Thank you for a great project.
+
+Furthermore, I would like to thank my head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me, and the MIT Math Department for making my project possible.
 I also wish to thank my tutor Mr. Antoni Rangachev, Northeastern University, for his invaluable advice in preparing both this paper and my final presentation.
-I also thank the Center for Excellence in Education and the Research Science Institute, as well as the Massachusetts Institute of Technology, for generously providing the facilities for the research.
 
-I would also like to thank my sponsors:
+I also thank my sponsors for RSI 2013:
 \begin{inparaenum}[]
@@
 
-Finally, I offer my sincerest gratitude to my mentor Mr.
-Francisco Unda, MIT, for daily mentorship, and Professor Benjamin Elias, MIT, for providing the project and for often meeting with me personally to discuss it.
-That sounded horribly fake, but I really mean it.  You guys are the best.  Thank you for a great project.
+Finally, I also thank the Center for Excellence in Education and the Research Science Institute, as well as the Massachusetts Institute of Technology, for generously providing the facilities for the research.

### 2013-07-30 summary.tex
Hell Week Monday 11AM update.
where are my cannolis
8 hours qq

--- 2013-07-19 summary.tex
@@
 
-The non-technical summary is like an abstract, but without any technical
-terminology. So instead of $v = (v_0, v_1, \ldots, v_n)$, you might say
-something along the lines of ``pick a point in high-dimensional space.''
-Don't worry about this section yet; you'll receive more guidance
-later on, when you're near the end of your mentorship.
+We take a certain class of maps and represent them with colored diagrams.
+These colored diagrams provide a combinatorial way for us to study and compute these maps.
+Now an algorithm of Libedinsky allows us to construct such diagrams from a string of $1$'s and $0$'s; furthermore, we can ocmpose two such diagrams together to obtain a third diagram.
+We develop tools to compute this third diagram based on the original binary strings.
+
+%TODO write one

### 2013-07-30 appa.tex
< 2 hours

@@
 \label{sec:count_map_computation}
+\defredcountmaps*
 \countmaps*
@@
 We proceed by induction on $n \ge 1$ and consider eight cases.
-(The base case is trivial.) The strategy for each is that, for the binary strings of length $n$ and top $T$, we consider those binary strings which end with $1$ and those which end with $0$.
+(The base case is trivial.) The strategy for each is that, for the binary strings of length $n$ and top $\ul w$, we consider those binary strings which end with $1$ and those which end with $0$.
 Using \eqref{eq:top}, we may then write the new quantity in terms of the number of strings of length $n-1$ with a different top.
@@
 	\end{itemize}
-	The case where $n=2k$ is similar, but $n-1=2(k-1)+1$.  Now the last bit changes the top by $t$.
+	The case where $n=2k$ is similar, but we now have $n-1=2(k-1)+1$.  Now the last bit changes the top by $t$.
 	\begin{itemize}
@@
 \begin{proof}[Proof of Lemma \ref{thm:pasture}]
-	Again, let $T$ denote the top, with length $N$.
-In the first case, suppose $T[N] \neq \AA_n[n]$; that is, the last characters of $T$ and $\AA_n$ differ.
+	Again, let $\ul w$ denote the top, with length $N$.
+In the first case, suppose $\ul w[N] \neq \AA_n[n]$; that is, the last characters of $\ul w$ and $\AA_n$ differ.
 Then it must be the case that the rightmost anchor is not part of a fence.
@@
 
-	The case where $T[N] = \AA_n[n]$ is similar.
+	The case where $\ul w[N] = \AA_n[n]$ is similar.
 We simply append a zero followed by $N$ $1$'s and repeat the same procedure.
@@
 	\begin{enumerate}[(i)]
-		\ii Suppose $\ul a[n] = \ul b[n] = 0$.  Note that the top of $M_1$ is also $T$.
+		\ii Suppose $\ul a[n] = \ul b[n] = 0$.  Note that the top of $M_1$ is also $\ul w$.
 		\begin{itemize}
-			\ii If $T = \varnothing$, then $M_1$ also had top $\varnothing$.
+			\ii If $\ul w = \varnothing$, then $M_1$ also had top $\varnothing$.
 Therefore, the addition of the $0$'s at the end simply generates an extra blue barbell.
@@
 $M = \alpha_sM_1$.
-			\ii The case where $T$ ends in $t$ is analogous; we simply obtain a new barbell.
-However, because $T \neq \varnothing$, the extra factor is $Q_T$ instead of simply $\alpha_t$.
-Hence, $M = Q_TM_1$.
+			\ii The case where $\ul w$ ends in $t$ is analogous; we simply obtain a new barbell.
+However, because $\ul w \neq \varnothing$, the extra factor is $Q_{\ul w}$ instead of simply $\alpha_t$.
+Hence, $M = Q_{\ul w}M_1$.
 			\begin{figure}[ht]
@@
 			\end{figure}
-			\ii Now suppose $T$ ends in $s$.
+			\ii Now suppose $\ul w$ ends in $s$.
 Then the addition of the $0$'s resulted in enclosing a caterpillar of $M_1$ in an attached bubble, as per Figure~\ref{fig:recurse_example_destr_zero}.
@@
 		\begin{itemize}
-			\ii First, suppose $T$ ends in $s$.
+			\ii First, suppose $\ul w$ ends in $s$.
 Then the additional $1$'s added simply create a fence on the far right, because there is no ``up'' blue anchors to interact with.
@@
 			\end{figure}
-			\ii Conversely, suppose that $T$ ends in $t$.   See Figure \ref{fig:recurse_example_destr_one} for an example.
+			\ii Conversely, suppose that $\ul w$ ends in $t$.   See Figure \ref{fig:recurse_example_destr_one} for an example.
 
-			In that case, $M_1$ must have had the top $T$ with an $s$ appended.
+			In that case, $M_1$ must have had the top $\ul w$ with an $s$ appended.
 Once again, we find that the red caterpillar from $M_1$ is enclosed in a bubble.
@@
 Therefore, while we still obtain the extra factor of $x$ and the caterpillar is still removed, we remain with a blue barbell on the far right pasture.
-So we must push this blue barbell through $T$.
-This adds a factor of $Q_T$, and so we obtain the desired form $M = -xF Q_T$.
-			\ii The case where $T = \varnothing$ is analogous to the previous case; in a sense, we merely have a degenerate $Q_\varnothing = \alpha_s$.
+So we must push this blue barbell through $\ul w$.
+This adds a factor of $Q_T$, and so we obtain the desired form $M = -xF Q_{\ul w}$.
+			\ii The case where $\ul w = \varnothing$ is analogous to the previous case; in a sense, we merely have a degenerate $Q_\varnothing = \alpha_s$.
 Specifically, the blue barbell is already on the correct pasture, so we simply add a factor of $\alpha_s$.

### 2013-07-30 paper.tex
< 2 hours

@@
 % This is paper.tex
-
-% TODO restate all theorems in appendix
-% TODO rewrite summary
 
@@
 
-The Hecke Algebra (or Iwahori-Hecke Algebra) $\HH$ of a Weyl group $W$ is an object of significant interest, studied in representation theory, algebraic number theory, and combinatorics.
-
-In 1979, Kazhdan and Lusztig \cite{ref:KaLu1,ref:KaLu2} gave a categorification of $\HH$, using a somewhat complicated construction\footnote{The technique involved using something called \emph{perverse sheaves on the flag variety}.}.
+The Hecke Algebra (or Iwahori-Hecke Algebra) is an object of significant interest, studied in representation theory, algebraic number theory, and combinatorics.
+In 1979, Kazhdan and Lusztig \cite{ref:KaLu1,ref:KaLu2} gave a categorification of the Hecke algebra, using a somewhat complicated construction\footnote{The technique involved using something called \emph{perverse sheaves on the flag variety}.}.
 The result became known as the Hecke category.
@@
 Soergel \cite{ref:Soe1,ref:Soe2} simplified this construction significantly in 1990 with an algebraic approach, using the aptly named Soergel bimodules.
-The Soergel bimodules permit an easier understanding of the categorification of $\HH$; their advantage is that they are easier to define and are combinatorial in nature.
-Furthermore, Soergel's construction extends the Hecke category to the case where $W$ is an arbitrary Coxeter group, as opposed to a Weyl group.
+The Soergel bimodules permit an easier understanding of this categorification; their advantage is that they are easier to define and are combinatorial in nature.
+% Furthermore, Soergel's construction extends the Hecke category to the case where $W$ is an arbitrary Coxeter group, as opposed to a Weyl group.
 
@@
 
-Soergel bimodules can be described as summands of another class of bimodules, known as the \emph{Bott-Samelson bimodules}.
+Soergel bimodules can be described in terms of another class of bimodules, known as the \emph{Bott-Samelson bimodules}.
 Now the morphisms of Bott-Samelson bimodules admit a combinatorial description.
 In particular, Elias and Williamson \cite{ref:gr4all}, building off earlier works such as Elias and Khovanov \cite{ref:EKh}, give a presentation for the category of these morphisms in terms of colored planar diagrammatics (i.e.
-colored planar graphs).
+colored diagrams).
 
 This paper investigates some of the properties of these diagrammatics from a combinatorial perspective.
-In this paper, we consider only the special case where $W$ is an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).
+In this paper, we consider only the special case where the underlying group $W$ of the Hecke algebra is an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).
 
@@
 These light leaves are interesting because they form a basis for a certain span of these maps, as shown in \cite{ref:gr4all}.
-We develop tools to understand the composition of two such maps given the original binary strings, with the eventual goal of deriving a combinatorial formula.
+In this paper, we develop tools to understand the composition of two such maps given the original binary strings, with the eventual goal of deriving a combinatorial formula.
 %The project deals with composing two maps formed in such a manner.
@@
 
-Appendix~\ref{sec:prelim_background} contains the preliminaries for the problem -- namely, the light leaves and the relation between the diagrams and maps.
+Appendix~\ref{sec:prelim_background} contains the preliminaries for the problem; it describes the light leaves and defines the relation between diagrams and maps.
 A minimal set of definitions used in this paper is given in Section~\ref{sec:prelim}.
@@
 \label{sec:prelim}
-In Appendix~\ref{sec:prelim_background}, we provide the background behind the Bott-Samelson bimodules, and the correspondence between these maps and certain diagrams.
+In Appendix~\ref{sec:prelim_background}, we provide the background behind the Bott-Samelson bimodules, and the correspondence between our maps and diagrams.
 We then introduce Libedinsky's light leaves, a basis by which maps can be constructed using binary strings.
@@
 
-This motivates us to make the following definition, which we use in Section~\ref{sec:res_alt_compute}.
+Now \eqref{eq:quantum} motivates us to make the following definition, which we use in Section~\ref{sec:res_alt_compute}.
 \begin{definition}
@@
 \begin{definition}
-	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are orthogonal if their product is zero.
+	A map is \emph{idempotent} if multiplying it with itself returns the original map.  Two idempotents are \emph{orthogonal} if their product is zero.
 \end{definition}
@@
 If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.
-More generally, however, if $AB = c$ for some scalar $c$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.
+More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.
 In other words, any two maps with nonzero product can be used to construct an idempotent.
@@
 \end{ques*}
-In this paper, we are interested in computing the polynomial which corresponds to this map.
+In this paper, we wish to compute the polynomial which corresponds to the map.
 
@@
 \begin{proof}
-	Straightforward induction on $n$.  
+	This is a direct application of \eqref{eq:top}.
 \end{proof}
@@
 \label{sec:res_count_maps}
-We give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r}(\ul b) = \ul T$ for each expression $\ul T$ and $\ul r$.
+We give a formula for the number of binary strings $\ul b$ such that $\Top_{\ul r}(\ul b) = \ul w$ for each expression $\ul w$ and $\ul r$.
 
-\begin{definition}
+\begin{restatable}{definition}{defredcountmaps}
 	Let $R(\ul r)$ denote $\ul r$ with any consecutive blocks of $s$'s replaced by a single $s$, and similarly for $t$.
-\end{definition}
+\end{restatable}
 For example, $R(sststttts) = ststs$.
@@
 \begin{restatable}[Pasture Lemma]{lemma}{pasture}
-	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then
+	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $\ul w$.  Suppose further that $N \ge 1$ (or equivalently, $\ul w \neq \varnothing$).  Then
 	\begin{enumerate}[(i)]
 		\ii Pastures $1$ through $N-1$ are either empty or contain an attached component.
-		\ii Pasture $N$ is empty if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.  The caterpillar is blue if $\AA_n[n]$ is $s$, and red otherwise.
+		\ii Pasture $N$ is empty if $\ul w[N] = \AA_n[n]$, and contains a single caterpillar otherwise.  The caterpillar is blue if $\AA_n[n]$ is $s$, and red otherwise.
 	\end{enumerate}
@@
 \begin{theorem}
-	For any binary strings $\ul a, \ul b \in \BB_n$, if $\MM_{\AA_n} (\ul a, \ul b)$ is nonzero and has top $T$, then for some nonnegative integers $m_x$, $m_y$, $m_s$, and $m_t$, we have 
+	For any binary strings $\ul a, \ul b \in \BB_n$, if $\MM_{\AA_n} (\ul a, \ul b)$ is nonzero and has top $\ul w$, then for some nonnegative integers $m_x$, $m_y$, $m_s$, and $m_t$, we have 
 	\[
@@
 		\begin{cases}
-			1 & \text{if $T$ and $\AA_n$ have the same last character} \\
-			Q_T & \text{otherwise}.
+			1 & \text{if $\ul w$ and $\AA_n$ have the same last character} \\
+			Q_{\ul w} & \text{otherwise}.
 		\end{cases}
@@
 \end{theorem}
-Here, $Q_T$ is the quantum polynomial defined in Section~\ref{sec:quantum}.
+Here, $Q_{\ul w}$ is the quantum polynomial defined in Section~\ref{sec:quantum}.
 \begin{proof}
@@
 Everything in the first pasture is a product of monomials by the Caterpillar Lemma.
-If $T$ and $\AA_n$ agree, then the last pasture is empty and hence we obtain the first case.
-Otherwise, there is a single caterpillar of color opposite to $T$, and hence after evaluating that caterpillar, we obtain some monomial times a single barbell.
-This generates the final $Q_T$ term after the barbell is pushed through all the fences; the broken fences are all zero because they are lower terms.
+If $\ul w$ and $\AA_n$ agree, then the last pasture is empty and hence we obtain the first case.
+Otherwise, there is a single caterpillar of color opposite to $\ul w$, and hence after evaluating that caterpillar, we obtain some monomial times a single barbell.
+This generates the final $Q_{\ul w}$ term after the barbell is pushed through all the fences; the broken fences are all zero because they are lower terms.
 \end{proof}
@@
 \begin{definition}
-	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then we call the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ the \emph{fluff} of $M$, and call the polynomial (either $1$ or $Q_T$) the \emph{face} of $M$.
+	If a nonzero map $M$ with base $\AA_n$ is presented as in Theorem~\ref{thm:alt_struct}, then we call the term $x^{m_x}y^{m_y}\alpha_s^{m_s}\alpha_t^{m_t}$ the \emph{fluff} of $M$, and call the polynomial (either $1$ or $Q_{\ul w}$) the \emph{face} of $M$.
 \end{definition}
@@
 \begin{restatable}{proposition}{recurse}
-	Let $n \ge 2$ be an odd integer and consider two binary strings $\ul a, \ul b \in \BB_n$ such that $T = \Top_{\AA_n}(\ul a) = \Top_{\AA_n}(\ul b)$.  
+	Let $n \ge 2$ be an odd integer and consider two binary strings $\ul a, \ul b \in \BB_n$ such that $\ul w = \Top_{\AA_n}(\ul a) = \Top_{\AA_n}(\ul b)$.  
 	Let $\ul a'$ and $\ul b'$ be the first $n-1$ bits of $\ul a$ and $\ul b$, respectively. 
@@
 			\begin{cases}
-				\alpha_s M_1 & \text{if $T = \varnothing$} \\ % just another barbell
-				-xF & \text{if $T$ ends in $s$} \\ % closes a caterpillar like 0|
-				 Q_T M_1 & \text{if $T$ ends in $t$}. \\ % just another barbell, but push it all the way through nonempty T
+				\alpha_s M_1 & \text{if $\ul w = \varnothing$} \\ % just another barbell
+				-xF & \text{if $\ul w$ ends in $s$} \\ % closes a caterpillar like 0|
+				Q_{\ul w} M_1 & \text{if $\ul w$ ends in $t$}. \\ % just another barbell, but push it all the way through nonempty w
 			\end{cases}
@@
 			\begin{cases}
-				-x\alpha_sF & \text{if $T = \varnothing$} \\ % destructive 1, closes a caterpillar O
-				M_1 & \text{if $T$ ends in $s$} \\ % constructive 1
-				-xF Q_T & \text{if $T$ ends in $t$}. % destructive 1
+				-x\alpha_sF & \text{if $\ul w = \varnothing$} \\ % destructive 1, closes a caterpillar O
+				M_1 & \text{if $\ul w$ ends in $s$} \\ % constructive 1
+				-xF Q_{\ul w} & \text{if $\ul w$ ends in $t$}. % destructive 1
 			\end{cases}

### 2013-07-30 summary.tex
< 2 hours

@@
 These colored diagrams provide a combinatorial way for us to study and compute these maps.
-Now an algorithm of Libedinsky allows us to construct such diagrams from a string of $1$'s and $0$'s; furthermore, we can ocmpose two such diagrams together to obtain a third diagram.
+Now an algorithm of Libedinsky allows us to construct such diagrams from a string of $1$'s and $0$'s; furthermore, we can compose two such diagrams together to obtain a third diagram.
 We develop tools to compute this third diagram based on the original binary strings.

### 2013-07-30 paper.tex
k

@@
 \end{definition}
-Fix an expression $\ul r$.
-If we can find two maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.
+If we can find two half-maps $A$ and $B$ (with the same top and base) for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.
 More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.
@@
 
-However, if we are interested in finding sets of pairwise orthogonal idempotents, then this becomes a linear algebra problem in which we require a matrix of all possible products.
+However, if we are interested in finding sets of \emph{pairwise orthogonal} idempotents, then this becomes a linear algebra problem in which we require a matrix of all possible products.
 The construction of such a set of idempotents is closely related to the decomposition of these bimodules, which in turn gives information about the Soergel bimodules\footnote{Actually, the Soergel bimodules may be defined as the images of idempotents in the endomorphism rings of the Bott-Samelson bimodules.}.

### 2013-07-30 appa.tex
Color.

@@
 	real h = 0.7;
-	pen s = blue, t = dashed + red + 0.6;
-	int n = 14;
 	draw(currentpicture, (0,0)--(0,h/2)..((0+2)/2.0,h*2)..(2,h/2)--(2,0), s);
@@
 		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
 		int n = 8;
@@
 			size(6cm);
-			pen s = blue, t = red + dashed + 0.6;
-			pen dot_s = blue, dot_t = red;
 			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
@@
 		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
 		int n = 6;
@@
 					real h = 0.7;
-					pen s = blue, t = red + dashed + 0.6;
-					pen dot_s = blue, dot_t = red;
 					int n = 4;

### 2013-07-30 paper.tex
Color.

@@
 \section{Introduction}
-\textbf{Note:} If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.
+%\textbf{Note:} If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.
 
@@
 	real h = 0.7;
-	pen s = blue, t = red + dashed + 0.6;
-	pen dot_s = blue, dot_t = red;
 	int n = 7;
@@
 		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
 		int n = 5;
@@
 		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
 		int n = 10;
@@
 		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
 		int n = 4;
@@
 		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
 		int n = 7;
@@
 		real h = 0.7;
-		pen s = blue, t = red + dashed + 0.6;
-		pen dot_s = blue, dot_t = red;
 		int n = 27;

### 2013-07-30 abstract.tex
8 hours qq
Almost done.

@@
 We examine the maps formed by a basis known as Libedinsky's light leaves, which constructs a map based on a string $\underline r$, composed of the letters $s$ and $t$, and a binary string $\underline b$.
-The eventual goal is to find a formula for the composition of two such maps based on their binary strings $\underline b$.
-The paper provides a complete formula for the case $\underline r = sss\dots$, and shows that the possible structures of maps when $\underline r = ststs\dots$ are extremely limited.
+The eventual goal is to find a formula for the composition of two such maps based on the two original binary strings.
+The paper provides a complete formula for the case $\underline r = sss\dots$, and shows that the possible structures of maps when $\underline r = ststs\dots$ are, in a certain sense, limited.
 We additionally provide a formula for the number of maps between two arbitrary Bott-Samelson bimodules.

### 2013-07-30 appa.tex
Almost done.

@@
 	path arc = (5,-5)..(2,0)..apex..(-2,0)..(-5,-5);
-	draw(arc, blue);
-	dot(apex, blue);
-	draw(apex--(0,ymax), blue);
-	draw(-apex--(0,-ymax), red + dashed + 0.6);
-	dot(-apex, red);
+	draw(arc, s);
+	dot(apex, dot_s);
+	draw(apex--(0,ymax), s);
+	draw(-apex--(0,-ymax), t);
+	dot(-apex, dot_t);
 	label("$s$", (0,ymax), dir(90));
@@
 \begin{op}[Isotropy] If two diagrams can be continuously deformed into each other (in the topological sense), then they are equivalent.  In other words, the maps are isotropy invariant  \end{op}
-The reasons for the above operation are not obvious; see page 7 of \cite{ref:gr4all} for an explanation.
+\begin{remark*}
+	The justification for the above operation is not obvious; see page 7 of \cite{ref:gr4all} for an explanation.
+\end{remark*}
 \begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$.  \end{op}

### 2013-07-30 paper.tex
Almost done.

@@
 This paper investigates some of the properties of these diagrammatics from a combinatorial perspective.
-In this paper, we consider only the special case where the underlying group $W$ of the Hecke algebra is an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).
+We consider only the special case where the underlying group $W$ of the Hecke algebra is an infinite dihedral group with generators $s$ and $t$ (as opposed to an arbitrary Coxeter group $W$).
 
@@
 A minimal set of definitions used in this paper is given in Section~\ref{sec:prelim}.
-In Section~\ref{sec:probstate}, the problem statement is given in its full technicality.
+In Section~\ref{sec:probstate}, we give the problem statement in its full technicality.
 
@@
 The most important results of this paper are presented in Sections~\ref{sec:res_alt_restrict} and \ref{sec:res_alt_compute}, where we investigate a special ``alternating'' case.
-In particular, we show that the possible resulting structures are extremely limited, and provide a recursion based on these restrictions for that case.
+We show that the possible resulting structures are extremely limited in a certain sense.
+We then exploit these restrictions to provide a partial recursion to compute the compositions of light leaves in the alternating case.
 

### 2013-07-30 appa.tex
fml

@@
 
-Fix an expression $\ul r$ of $s$'s and $t$'s with length $n$.  Then for any binary string $\ul b$ of length $n$ we can construct a diagram based on a series of rules.
+Fix an expression $\ul r$ of length $n$.  Then for any binary string $\ul b$ of length $n$ we can construct a diagram based on a series of rules.
 
@@
 
-	Define a pair of red anchors $u, v$, with $u$ to the left of $v$, to be \emph{quasi-connected} if (i) one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect blue lines, and (ii) there is no red anchor $w$ strictly between $u$ and $v$ for which one can draw a similar arc on the same half-map joining $w$ and $v$.
+	Define a pair of red anchors $u, v$, with $u$ to the left of $v$, to be \emph{quasi-connected} if
+	\begin{inparaenum}[(i)]
+		\ii one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect blue lines, and
+		\ii there is no red anchor $w$ strictly between $u$ and $v$ for which one can draw a similar arc on the same half-map joining $w$ and $v$.
+	\end{inparaenum}
 

### 2013-07-30 paper.tex
fml

@@
 The result became known as the Hecke category.
-% If $K = \RR$, the resulting basis of $\HH$ is understood, and called the Kazhdan-Lusztig basis.  However, if $K$ is a field of some other characteristic $p$, the basis is unknown.
 Soergel \cite{ref:Soe1,ref:Soe2} simplified this construction significantly in 1990 with an algebraic approach, using the aptly named Soergel bimodules.
@@
 \begin{definition}
-	A connected component which (i) is acyclic, and (ii) does not touch the top or bottom boundaries is called a \emph{barbell}.
+	A connected component which
+	\begin{inparaenum}[(i)]
+		\ii is acyclic, and 
+		\ii does not touch the top or bottom boundaries
+	\end{inparaenum} is called a \emph{barbell}.
 \end{definition}
@@
 \begin{equation}
-	s([n]_x\alpha_s + [n-1]_y\alpha_t) = [n]_x\alpha_s + [n+1]_y\alpha_t
+	s([n-1]_x\alpha_s + [n]_y\alpha_t) = [n]_x\alpha_s + [n+1]_y\alpha_t
 	\label{eq:quantum}
@@
 \begin{definition}
-	For any reduced expression $\ul r$, we define the quantum polynomial $Q_{\ul r}$ by:
-	\[
-		Q_{\AA_n} = 
-		\begin{cases}
-			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd} \\
-			[n]_x \alpha_s + [n+1]_y \alpha_t & \text{if $n$ is even}
-		\end{cases}
-	\]
-	when $\ul r = \AA_n$, and otherwise,
-	\[
-		Q_{\AA_n'} =
-		\begin{cases}
-			[n]_x \alpha_s + [n+1]_y \alpha_t & \text{if $n$ is even} \\
-			[n+1]_x \alpha_s + [n]_y \alpha_t & \text{if $n$ is odd}.
-		\end{cases}
-	\]
+	For any reduced expression $\ul r$, we define the quantum polynomial $Q_{\ul r}$ by $Q_{\AA_n} = [n+1]_x \alpha_s + [n]_y \alpha_t$ when $\ul r = \AA_n$, and otherwise, $Q_{\AA_n'} = [n]_x \alpha_s + [n+1]_y \alpha_t$.
 \end{definition}
@@
 \end{definition}
-If we can find two half-maps $A$ and $B$ (with the same top and base) for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.
+If we can find two half-maps $A$ and $B$ for which $AB$ is the identity, then $(BA)^2=BABA=BA$ is an idempotent.
 More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.
@@
 
-However, if we are interested in finding sets of \emph{pairwise orthogonal} idempotents, then this becomes a linear algebra problem in which we require a matrix of all possible products.
+However, if we are interested in finding sets of \emph{pairwise orthogonal} idempotents, then this becomes a linear algebra problem in which we require a matrix of all products.
 The construction of such a set of idempotents is closely related to the decomposition of these bimodules, which in turn gives information about the Soergel bimodules\footnote{Actually, the Soergel bimodules may be defined as the images of idempotents in the endomorphism rings of the Bott-Samelson bimodules.}.
@@
 We do so by using induction on $n$, and applying \eqref{eq:top}.
-By splitting into the case where $\ul b[n] = 1$ and $\ul b[n] = 0$, we get two binomial coefficients; the computation is to verify that by Pascal's identity they sum to the desired coefficient.
+By splitting into the case where $\ul b[n] = 1$ and $\ul b[n] = 0$, we get two binomial coefficients; the computation is to verify that we can then apply Pascal's identity.
 The second step is to reduce the case where $\ell \neq n$ to the previous step using Proposition~\ref{prop:s_top}.
@@
 
-Below we present three results which show that the possible outputs of a map with base $\AA_n$ are structurally very limited.
+Below we present three results which show that the possible outputs of a map with base $\AA_n$ all take certain forms.
 \begin{restatable}[Bubble Lemma]{lemma}{bubble}
@@
 The other two lemmas follow directly from it.
-The details of the proofs are given in Appendix~\ref{sec:lemmata_proof}, on page~\pageref{sec:lemmata_proof}.
+The proofs are given in Appendix~\ref{sec:lemmata_proof}, on page~\pageref{sec:lemmata_proof}.
 
@@
 \begin{remark*}
-	According to Theorem~\ref{thm:alt_struct}, a nonzero map $\MM_{\AA_n}$ has face $1$ and only if its top has the same last character as $\AA_n$.
+	According to Theorem~\ref{thm:alt_struct}, a nonzero map $\MM_{\AA_n}$ has face $1$ if and only if its top has the same last character as $\AA_n$.
 \end{remark*}
@@
 It was originally hoped that, by understanding $\AA_n$ and $\SS_n$, one could derive the general formula (perhaps by viewing strings of $s$'s in $\ul r$ as a single $s$ with a formula for $\SS_n$, and then aggregating all this information with a formula for $\AA_n$).
-Unfortunately, the lemmata of Section~\ref{sec:res_alt_restrict} show that in fact, maps with base $\AA_n$ are quite restricted.
-So, either the results of Section~\ref{sec:res_alt_compute} will have to be generalized significantly (in the context of maps outside those of base $\AA_n$), or an entirely new approach will be required.
+Unfortunately, the lemmata of Section~\ref{sec:res_alt_restrict} show that in fact, maps with base $\AA_n$ have very special properties.
+So, either the results of Section~\ref{sec:res_alt_compute} will have to be generalized significantly (in the context of maps outside those with base $\AA_n$), or an entirely new approach will be required.
 

### 2013-07-30 paper.tex
my feet are cold
Done.  FOREVER.

@@
 
+Two maps $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ with identical tops may be composed by juxtaposing $\MM_{\ul r}(\ul a)$ with a flipped copy of $\MM_{\ul r}(\ul b)$; an example of such a composition is given in Figure~\ref{fig:example_compose}.
+We denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
+If the two half-maps are not compatible (that is, $\Top_{\ul r}(\ul a) \neq \Top_{\ul r}(\ul b)$) then we simply set $\MM_{\ul r}(\ul a, \ul b) = 0$.
+
 \begin{figure}[ht]
@@
 \end{figure}
-
-Two maps $\MM_{\ul r}(\ul a)$ and $\MM_{\ul r}(\ul b)$ with identical tops may be composed by juxtaposing $\MM_{\ul r}(\ul a)$ with a flipped copy of $\MM_{\ul r}(\ul b)$; an example of such a composition is given in Figure~\ref{fig:example_compose}.
-We denote this product by $\MM_{\ul r}(\ul a, \ul b)$.
-If the two half-maps are not compatible (that is, $\Top_{\ul r}(\ul a) \neq \Top_{\ul r}(\ul b)$) then we simply set $\MM_{\ul r}(\ul a, \ul b) = 0$.
 
@@
 More generally, however, if $AB = c$ for some scalar $c \neq 0$, then \[ \left( \frac{BA}{c} \right)\left( \frac{BA}{c} \right) = \frac{BABA}{c^2} = \frac{BA}{c} \] is also an idempotent.
-In other words, any two maps with nonzero product can be used to construct an idempotent.
 
@@
 Furthermore, I would like to thank my head mentor Dr. Tanya Khovanova, MIT, for providing individual discussion with me, and the MIT Math Department for making my project possible.
-I also wish to thank my tutor Mr. Antoni Rangachev, Northeastern University, for his invaluable advice in preparing both this paper and my final presentation.
+I also wish to thank my tutor Mr.
+Antoni Rangachev, Northeastern University, for his invaluable advice in preparing both this paper and my final presentation, as well as Felipe Hern\'andez and Charlie Pasternak for their revisions.
 

### 2013-07-30 appa.tex
QQ papersubmit

@@
 		\text{Map} & \text{Modules} & \text{Description} \\[1em]
-		\barbell{half_top} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
-		\barbell{half_bot} & R \to R \stimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
-		\barbell{tri_down} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
-		\barbell{tri_up} & R \stimes R \stimes R \to R \stimes R & 1 \mid g \mid 1 \mapsto \partial_s(g) \mid 1 \\[1em]
-		\barbell{id} & R \stimes R \to R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \\[1em]
+		\barbell{\includegraphics{barbell/half_top.pdf}} & R \stimes R \to R & 1 \mid 1 \mapsto 1 \\[1em]
+		\barbell{\includegraphics{barbell/half_bot.pdf}} & R \to R \stimes R & 1 \mapsto \half \left( 1 \mid \alpha_s + \alpha_s \mid 1 \right) \\[1em]
+		\barbell{\includegraphics{barbell/tri_down.pdf}} & R \stimes R \to R \stimes R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \mid 1 \\[1em]
+		\barbell{\includegraphics{barbell/tri_up.pdf}} & R \stimes R \stimes R \to R \stimes R & 1 \mid g \mid 1 \mapsto \partial_s(g) \mid 1 \\[1em]
+		\barbell{\includegraphics{barbell/id.pdf}} & R \stimes R \to R \stimes R & 1 \mid 1 \mapsto 1 \mid 1 \\[1em]
 	\end{array}
@@
 
-Henceforth, we will make the convenient abbreviation of $\barbell{tri_up_contract_before}$ as $\barbell{tri_up_contract_after}$.
+Henceforth, we will make the convenient abbreviation of $\barbell{\includegraphics{barbell/tri_up_contract_before.pdf}}$ as $\barbell{\includegraphics{barbell/tri_up_contract_after.pdf}}$.
 It will also be understood that edges need not be straight lines, but any topologically equivalent deformation shall represent the same graph.
@@
 \end{remark*}
-\begin{op}[Associativity] We have $\barbell{assoc_horiz} = \barbell{assoc_vert}$.  \end{op}
-\begin{op}[Contraction] We have $\barbell{contract_left} = \barbell{contract_right} = \barbell{alpha_blue}$.  \end{op}
-\begin{op}[The Needle] We have $\barbell{needle} = 0$.  \end{op}
-\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{zero}$ is zero as well.
+\begin{op}[Associativity] We have $\barbell{\includegraphics{barbell/assoc_horiz.pdf}} = \barbell{\includegraphics{barbell/assoc_vert.pdf}}$.  \end{op}
+\begin{op}[Contraction] We have $\barbell{\includegraphics{barbell/contract_left.pdf}} = \barbell{\includegraphics{barbell/contract_right.pdf}} = \barbell{\includegraphics{barbell/alpha_blue.pdf}}$.
+\end{op}
+\begin{op}[The Needle] We have $\barbell{\includegraphics{barbell/needle.pdf}} = 0$.  \end{op}
+\begin{remark*} Using contraction and the above, one can show that the diagram $\barbell{\includegraphics{barbell/zero.pdf}}$ is zero as well.
 In fact, in general, \emph{any} map which contains a ``closed'' and empty region is the zero map.
@@
 	\begin{enumerate}[(a)]
-		\ii $\barbell{barbell_blue}\barbell{alpha_blue} + \barbell{alpha_blue} \barbell{barbell_blue} = 2 \barbell{break_blue}$, and the similar equation for red.
-		\ii $\barbell{alpha_red}\barbell{barbell_blue} = -x\barbell{break_red} + \barbell{barbell_blue}\barbell{alpha_red} + x \barbell{barbell_red}\barbell{alpha_red}$.
-		\ii $\barbell{alpha_blue}\barbell{barbell_red} = -y\barbell{break_blue} + \barbell{barbell_red}\barbell{alpha_blue} + y \barbell{barbell_blue}\barbell{alpha_blue}$.
+		\ii $\barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}} + \barbell{\includegraphics{barbell/alpha_blue.pdf}} \barbell{\includegraphics{barbell/barbell_blue.pdf}} = 2 \barbell{\includegraphics{barbell/break_blue.pdf}}$, and the similar equation for red.
+		\ii $\barbell{\includegraphics{barbell/alpha_red.pdf}}\barbell{\includegraphics{barbell/barbell_blue.pdf}} = -x\barbell{\includegraphics{barbell/break_red.pdf}} + \barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/alpha_red.pdf}} + x \barbell{\includegraphics{barbell/barbell_red.pdf}}\barbell{\includegraphics{barbell/alpha_red.pdf}}$.
+		\ii $\barbell{\includegraphics{barbell/alpha_blue.pdf}}\barbell{\includegraphics{barbell/barbell_red.pdf}} = -y\barbell{\includegraphics{barbell/break_blue.pdf}} + \barbell{\includegraphics{barbell/barbell_red.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}} + y \barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}}$.
 	\end{enumerate}

### 2013-07-30 paper.tex
QQ papersubmit

@@
 \end{definition}
-Notice that, by combining homotopy and contraction (see Appendix~\ref{sec:prelim_genrel}), every blue barbell is simply $\barbell{barbell_blue}$.
-Similarly, every red barbell is simply $\barbell{barbell_red}$.
+Notice that, by combining homotopy and contraction (see Appendix~\ref{sec:prelim_genrel}), every blue barbell is simply $\barbell{\includegraphics{barbell/barbell_blue.pdf}}$.
+Similarly, every red barbell is simply $\barbell{\includegraphics{barbell/barbell_red.pdf}}$.
 
@@
 	\ii For any $f \in R$, the map $x \mapsto fx$ (i.e. multiplication on the left) will be abbreviated as $f$ from this point forward.  
-	\par In particular, the map $\barbell{barbell_blue}$ is $\alpha_s$.
+	\par In particular, the map $\barbell{\includegraphics{barbell/barbell_blue.pdf}}$ is $\alpha_s$.
 This follows from a straightforward computation.
-Furthermore, one can check that, for example, $\barbell{barbell_blue}\barbell{barbell_blue}\barbell{barbell_red}\barbell{alpha_blue} = \alpha_s^2 \alpha_t$.
-	Note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{alpha_blue}\barbell{barbell_blue} \neq \alpha_s$.
+Furthermore, one can check that, for example, $\barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/barbell_blue.pdf}}\barbell{\includegraphics{barbell/barbell_red.pdf}}\barbell{\includegraphics{barbell/alpha_blue.pdf}} = \alpha_s^2 \alpha_t$.
+	Note that $x \mapsto xf$ does not get a similar abbreviation.  So, $\barbell{\includegraphics{barbell/alpha_blue.pdf}}\barbell{\includegraphics{barbell/barbell_blue.pdf}} \neq \alpha_s$.
 	\ii We work \emph{modulo lower terms}.
 That is, any map which contains a connected component that touches any boundary only once (total) is considered zero.
-So, for example, we have $\barbell{break_blue} = 0$.
+So, for example, we have $\barbell{\includegraphics{barbell/break_blue.pdf}} = 0$.
 \end{enumerate}
@@
 \begin{equation}
-	\barbell{alpha_blue} f = \partial_s(f) \barbell{break_blue} + s(f) \barbell{alpha_blue}
+	\barbell{\includegraphics{barbell/alpha_blue.pdf}} f = \partial_s(f) \barbell{\includegraphics{barbell/break_blue.pdf}} + s(f) \barbell{\includegraphics{barbell/alpha_blue.pdf}}
 	\label{eq:barbell_break}
